### 2022-04-01 paper.tex
changes + paper start

\documentclass[11pt]{article}
\usepackage[margin  = 1in]{geometry}
\usepackage{hyperref}
\bibliographystyle{ieeetr}
\usepackage{amsmath}

\begin{document}

\title{Deep Learning Methods for Optimizing Terahertz Leaky Wave Antenna Design}
\author{J. Neronha, H. Guerboukha, and D. Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
\date{}

\maketitle

\section*{Introduction}

The predictive power of neural networks and machine learning techniques more generally have been applied to a vast array problems ever since the neural network was proposed as a computational model for the brain in the mid-twentieth century. \cite{McCulloch:1943vq} This, of course, includes communications technology -- neural networks have been used extensively in the field because of their unique ability to approximate accurate solutions to nonlinear problems that are commonplace in antenna design. Machine learning models are particularly useful in situations where an analytical solution cannot be obtained and/or numerical simulations are expensive \cite{Kim, Massa}, for example when solving the ``direct" problem of approximating an antenna's output \cite{8608745} or modeling a metasurface \cite{Nadell:19}, which could take a finite-element model hours or longer to solve, limiting real-time simulation and design. The ``inverse" problem considers the opposite, for example reconstructing an image from scattered light \cite{Sun:18}. \\

\noindent We are particularly interested in the inverse problem of terahertz leaky-wave antenna (LWA) design because of its high applicability to the field of communications -- given some arbitrarily desired far-field pattern, how can we quickly design, fabricate, and test an antenna that meets our needs? LWAs are simple metallic waveguides that have proven very effective in the terahertz range and are particularly interesting because they emit radiation at a frequency-dependent angle with a one-to-one relationship between frequency and angle, which is quite valuable given the narrow character of beams in the terahertz range. \cite{doi:10.1063/5.0033126} They have been used in a number of diverse applications including link discovery \cite{Ghasempour:2020tz}, multiplexing and demultiplexing \cite{Karl:2015uh, Ma:2017vo}, and for radar and object detection purposes \cite{Amarasinghe:20}. Leaky-wave antennas also stand out for our purposes of rapid design and experimentation because of the ease of fabricating them using novel hot-stamping techniques \cite{Guerboukha:21}. \\

\noindent This inverse problem has been explored in the terahertz range using deep neural networks in the context of designing structures to obtain an optimized geometry that produces the desired signal, particularly in relation to metasurface design \cite{Deng:21, 9602997}. The inverse Leaky-wave antenna problem has also been explored, but using a genetic algorithm and outside of the terahertz range at much higher frequencies \cite{Jafar-Zanjani:2018vy}. As a result, in this paper, we propose a model to predict the ideal LWA geometry that will generate desired far-field radiation in the terahertz range.

\section*{Methodology}

We train a model to predict a slot geometry for a desired far-field signal. In particular, we consider a one-dimensional discretized slot where each component 0.5 micron slot can either be transparent or metallic, similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}. This design essentially creates a non-uniform periodic waveguide whose peaks can be predicted by Floquet theory. In a leaky wave guide with plate separation $h$, the dispersion constant $\beta$ for a given period $\Lambda$ and Floquet mode $p$ for a wave vector $k_0$ is given by:

\[\beta=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1} \label{eq:special}\]

\noindent Oftentimes, the primary objective design of antenna design is to generate peaks of specific magnitudes at specific locations. We use Eq. 1 to  obtain the location of all possible Floquet peaks for periodic leaky wave antennas, which form the set of possible peaks for which the model can design a geometry. This is important because it ensures that users of the model cannot attempt to design a slot that will place a peak at an angle that is impossible given the dispersion relation for the waveguide. For our LWA with a plate separation of 1 mm operating at a frequency of 200 GHz, we plot the possible peaks generated by Floquet theory in Figure 1 below. \\

\noindent We build a model of a leaky-wave antenna in COMSOL Multiphysics with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length. 18 sub-slots (exactly half) of the slots are randomly chosen as to be transparent (i.e. a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation. We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its native API.

\section*{Results and Discussion}

\section*{Conclusion}

\bibliographystyle{plain}
\bibliography{references.bib}
\end{document}

### 2022-04-01 1d/peaks_to_slot/build_model.py

@@ -79,6 +79,8 @@ def main():
     slots, peaks = import_data(args.t)
 
     slot_train, slot_test, peaks_train, peaks_test = train_test_split(slots, peaks, test_size=0.2)
+    print(peaks_train.shape)
+    print(peaks_test.shape)
 
     Model = LWAPredictionModel()
 
@@ -98,6 +100,7 @@ def main():
         random = np.random.randint(0,slot_test.shape[0])
 
         efarx = Model.call(tf.expand_dims(peaks_test[random],0))
+        print(tf.expand_dims(peaks_test[random],0).shape)
         efarx = tf.squeeze(efarx)
 
         truedesign = tf.expand_dims(slot_test[random],axis = 1)
@@ -115,6 +118,23 @@ def main():
 
     with open('1d/peaks_to_slot/results/generated_slots.pkl', 'wb') as f:
         pickle.dump(peak_sim, f)
+
+    peaks_of_interest = np.array([20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20
+
+    ])
+    print(tf.expand_dims(peaks_of_interest,0))
+    results = Model.call(tf.expand_dims(peaks_of_interest,0))
+
+
+    with open('1d/peaks_to_slot/results/testing_slots.pkl', 'wb') as f:
+        pickle.dump([peaks_of_interest, results], f)
+    Model.compute_output_shape(input_shape=(35,1))
+    # Model.save_weights('1d/peaks_to_slot/results/model_weights')
 
     return Model
 

### 2022-04-01 1d/peaks_to_slot/results/trained_analysis.py

@@ -1,0 +1,16 @@
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+
+trained_model = tf.keras.models.load_model('1d/peaks_to_slot/results/model')
+trained_model.compile()
+
+peaks_of_interest = np.array([20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20,
+                                20,20,20,20,20,20
+])
+
+results = trained_model.call(tf.expand_dims(peaks_of_interest,0))

### 2022-04-05 paper/paper.tex
constnat power

--- 2022-04-01 paper.tex
@@
 We use Eq.
-1 to  obtain the location of all possible Floquet peaks for periodic leaky wave antennas, which form the set of possible peaks for which the model can design a geometry.
+1 to  obtain the location of all possible Floquet peaks for periodic leaky wave antennas, which form the set of possible peaks for which the model can design a geometry and only keep the solutions where $\beta > |k_0|$ (i.e.
+where radiation leaks from the antenna -- forward scattering if $k_0$ is positive, and backwards scattering if $k_0$ is negative).
 This is important because it ensures that users of the model cannot attempt to design a slot that will place a peak at an angle that is impossible given the dispersion relation for the waveguide.
@@
 We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its native API.
+Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs.
+\\
+
+\noindent The COMSOL simulation data is used as the data source for our deep neural network.
+The network, which is built with TensorFlow, has six dense layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
+The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
+The model architecture is visualized in Figure 2.
 

### 2022-04-05 1d/peaks_to_slot/constant_power/analysis.py

@@ -1,0 +1,185 @@
+import numpy as np
+import pandas as pd
+import pickle
+import tensorflow as tf
+import matplotlib.pyplot as plt
+
+with open('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power/results/generated_slots.pkl', 'rb') as file:
+    data = pickle.load(file)
+real_peaks = [x[0] for x in data]
+true = [x[1] for x in data]
+prediction = [x[2] for x in data]
+
+floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
+floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+floquet_back_fake = [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
+
+def import_data():
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+
+    with open('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/comsol_results/1d/1648515434.csv', 'rb') as file:
+        results = np.loadtxt(file, delimiter=",", dtype=float)
+        num_sims = int(results.shape[0] / 361)
+        points = [361 * x for x in np.arange(num_sims + 1)]
+        sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+        peaks = sorted_x[:,floquet_back + floquet_forward]
+
+            # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
+
+            # max = peaks[past_thresh].max(axis=1)
+            # print(max.shape)
+            # normalized = np.divide(peaks[past_thresh].T,np.max(peaks[past_thresh],axis=1)).T
+            # normalized = (peaks[past_thresh].T / peaks[past_thresh].max(axis=1)).T# TEMP:
+            # peaks_list.append(normalized)
+            # peaks_list.append(normalized)
+        peaks_list.append(peaks)
[…]

### 2022-04-05 1d/peaks_to_slot/constant_power/build_model.py

@@ -1,0 +1,140 @@
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+from preprocess import import_data, get_next_batch
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+import argparse
+import pickle
+
+parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
+
+def train(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        with tf.GradientTape() as tape:
+            efarx = model.call(peaks_batch)
+            efarx_loss = model.loss_function(efarx, slot_batch) #slots serves as the mask here
+            # print(efarx_loss)
+
+        gradients = tape.gradient(efarx_loss, model.trainable_variables)
+        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+
+    print('Efarx training loss: ', tf.reduce_mean(loss_list))
+    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+
+def test(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+    assump_acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        efarx = model.call(peaks_batch)
+        efarx_loss = model.loss_function(efarx, slot_batch)
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+        assump_acc_list.append(model.assump_accuracy(efarx,slot_batch))
+
+
[…]

### 2022-04-05 1d/peaks_to_slot/constant_power/peaks_to_slots_model.py

@@ -1,0 +1,101 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1DTranspose
+
+
+class LWAPredictionModel(tf.keras.Model):
+    def __init__(self, lr = 5e-5):
+        super(LWAPredictionModel, self).__init__()
+
+        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
+        self.batch_size = 64
+        self.epochs = 40
+
+        self.dense_layers = tf.keras.Sequential()
+        # self.dense_layers.add(Dense(1000, activation = 'relu'))
+        # self.dense_layers.add(Dense(800, activation = 'relu'))
+        self.dense_layers.add(Dense(1000))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        self.dense_layers.add(Dense(1000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(1000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(1000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(1000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(1000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        # self.dense_layers.add(LeakyReLU(0.2))
+        # self.dense_layers.add(Dense(2000))
+        # # self.dense_layers.add(ReLU())
+        # self.dense_layers.add(LeakyReLU(0.2))
+        # self.dense_layers.add(Dense(2000))
[…]

### 2022-04-05 1d/peaks_to_slot/constant_power/test.py

@@ -1,0 +1,3 @@
+import os
+
+list(set([x.split('.')[0] for x in os.listdir('comsol_results/1dconstantslots')]))

### 2022-04-05 1d/peaks_to_slot/results/trained_analysis.py

@@ -1,16 +1,55 @@
 import numpy as np
 import tensorflow as tf
+import sys
+sys.path.append("1d/peaks_to_slot")
 from peaks_to_slots_model import LWAPredictionModel
+import matplotlib.pyplot as plt
 
-trained_model = tf.keras.models.load_model('1d/peaks_to_slot/results/model')
-trained_model.compile()
+Model = LWAPredictionModel()
+Model.load_weights('1d/peaks_to_slot/results/model_weights')
 
+Model.compile()
+
+Model.summary()
 peaks_of_interest = np.array([20,20,20,20,20,20,
                                 20,20,20,20,20,20,
                                 20,20,20,20,20,20,
                                 20,20,20,20,20,20,
                                 20,20,20,20,20,20,
-                                20,20,20,20,20,20
+                                20,20,20,20,20
 ])
 
-results = trained_model.call(tf.expand_dims(peaks_of_interest,0))
+x = tf.convert_to_tensor(peaks_of_interest)
+tf.expand_dims(peaks_of_interest,0).shape
+results = Model.call(tf.expand_dims(x,0))
+
+plt.imshow(tf.transpose(results), cmap='YlGnBu')
+
+len(peaks_of_interest)
+
+def plot_rounded(data, total_slots):
+    this_data = np.array(data[0])
+    pred = np.array(data[0])
+
+    print(pred)
+
+    top_slots = list(np.argsort(pred)[36 - int(total_slots):36])
+    min = pred[top_slots].min()
+
+    pred[pred >= min] = 1
+    pred[pred < min] = 0
+
+    naive = tf.round(this_data)
+
+    print(this_data)
+
+    fig = plt.figure()
+    ax = fig.subplots(1,4, gridspec_kw={'width_ratios': [3, 1, 1, 1]})
+    ax[0].scatter(np.arange(len(peaks_of_interest)),peaks_of_interest)
+    ax[1].imshow(tf.expand_dims(this_data,1),cmap = 'GnBu')
+    ax[2].imshow(tf.expand_dims(pred,1),cmap = 'GnBu')
+    ax[3].imshow(tf.expand_dims(naive,1),cmap = 'GnBu')
+
+    return naive
+
+plot_rounded(results,18)

### 2022-04-26 paper/paper.tex
basic grey model

--- 2022-04-01 paper.tex
@@
 \usepackage{amsmath} 
+\usepackage{graphicx}
+\usepackage{float}
+\usepackage{subcaption}
 
@@
 
-The predictive power of neural networks and machine learning techniques more generally have been applied to a vast array problems ever since the neural network was proposed as a computational model for the brain in the mid-twentieth century.
+The predictive power of neural networks and machine learning techniques more generally have been applied to a vast array problems ever since the neural network was proposed as a computational technique loosely modeling the brain in the mid-twentieth century.
 \cite{McCulloch:1943vq} This, of course, includes communications technology -- neural networks have been used extensively in the field because of their unique ability to approximate accurate solutions to nonlinear problems that are commonplace in antenna design.
@@
 We train a model to predict a slot geometry for a desired far-field signal.
-In particular, we consider a one-dimensional discretized slot where each component 0.5 micron slot can either be transparent or metallic, similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}.
-This design essentially creates a non-uniform periodic waveguide whose peaks can be predicted by Floquet theory.
+In particular, we consider a one-dimensional discretized slot split into thirty-six 0.5 micron sub-slots that can either be transparent or metallic, similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}.
+This design essentially creates a non-uniform periodic waveguide that has peaks which can be predicted by Floquet theory.
 In a leaky wave guide with plate separation $h$, the dispersion constant $\beta$ for a given period $\Lambda$ and Floquet mode $p$ for a wave vector $k_0$ is given by:
@@
 
-\noindent Oftentimes, the primary objective design of antenna design is to generate peaks of specific magnitudes at specific locations.
-We use Eq.
-1 to  obtain the location of all possible Floquet peaks for periodic leaky wave antennas, which form the set of possible peaks for which the model can design a geometry.
-This is important because it ensures that users of the model cannot attempt to design a slot that will place a peak at an angle that is impossible given the dispersion relation for the waveguide.
-For our LWA with a plate separation of 1 mm operating at a frequency of 200 GHz, we plot the possible peaks generated by Floquet theory in Figure 1 below.
+\noindent where $k_0$ is the wave number and $h$ is the height of the slot.
+One primary objective design of antenna design is to generate peaks of specific magnitudes at specific locations.
+Thus, we wish to design a slot that will generate the desired amplitudes at the peaks from each possible Floquet mode.
+Our randomly generated slots form linear combinations of periodicities that greatly expands the potential peak profiles compared to a slot with a simple constant periodicity and makes the problem significantly more challenging to solve analytically, introducing the need for a model like ours.
+We wish to compute all possible phase constants for each possible periodicity across all Floquet modes; if they are valid (i.e.
+$\-1 < \frac{\beta}{k_0} = n_{eff} < 1$), we can generate the predicted scattering angle by $\theta = \cos^{-1}(n_{eff})$.
+In Figure 1 below, we compute all possible peak angles for an arbitrary discretized slot predicted by Floquet modes and overlay those peaks on a sample far-field signal generated numerically.
+We will extract these peaks from the simulation data and use them as the input training data along with the slot used to generate it in order to predict a slot design given some peak profile in the neural network model.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=6in]{figures/fig4_labeled2.eps}
+	\caption{The left panel shows the possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering (< 90$\deg$) and the negative modes in back-scattering.
+The right panel shows these predicted Floquet modes overlaid on a sample peak profile generated in COMSOL.}
+\end{figure}
+
+\noindent To generate our training data, we build a model of a leaky-wave antenna in COMSOL Multiphysics with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length.
+18 sub-slots (exactly half) of the slots are randomly chosen as to be transparent (i.e.
+a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation.
+We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its API.
+Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs; using only a few tens of thousands sets of training data, we can predict an optimal slot design for an arbitrary peak profile.
+The simulation geometry is shown in Figure 2a below \\
+
+\begin{figure}[H]
+	\caption{Simulation geometry (left) and possible peak profiles (right)}
+	\begin{subfigure}[b]{0.45\textwidth}
+		\centering
+		\includegraphics[width = 3.2in]{figures/fig5.eps}
+		\caption{The leaky wave antenna geometry used to generate training data.
+Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; both are randomly generated so that the slots are half and half.}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.55\textwidth}
+		\centering
+		\includegraphics[width=3in]{figures/fig2new.eps}
+
+		\caption{A box plot showing the amplitudes at each peak; peak \#23 is always the highest amplitude because it is the primary emission angle of all LWAs, periodic and not, at 200 GHz.
+A wide array of values are evident.}
+	\end{subfigure}
+
+\end{figure}
+
+\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20.
+Figure 2b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
+The network, which is built with TensorFlow, has six dense layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
+The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
+The model architecture is visualized in Figure 3.
 \\
 
-\noindent We build a model of a leaky-wave antenna in COMSOL Multiphysics with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length.
-18 sub-slots (exactly half) of the slots are randomly chosen as to be transparent (i.e.
-a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation.
-We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its native API.
+\begin{figure}[b]
+	\centering
+	\includegraphics[width=6in]{figures/fig1.eps}
+	\caption{Neural network architecture schematic; peaks are used as the input data and passed through six hidden layers to predict the ideal slot design that will yield the closest possible signal.}
+\end{figure}
+
+\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this idea as our loss function, we would need to compute the far-field signal for each slot we generate as we train the model, which would be extraordinary (and unfeasibly) computationally expensive.
+Thus, instead, we turn to the idea of making the generated slot look as similar to the given training slot for a given peak profile as possible.
+Given that this is essentially a binary classification problem for each sub-slot, we use three weighted binary cross-entropy (BCE) loss functions, which are summed together to form our overall loss function with the following weightings:
+\begin{enumerate}
+  \item BCE between the true and predicted slot (2x)
+  \item BCE between the first derivative of the true and predicted slot using a Prewitt filter (1x)
+  \item BCE between the second derivative of the true and predicted slot using a Laplacian filter (1x)
+\end{enumerate}
 
 \section*{Results and Discussion}
+\subsection*{Binary Predictions}
+For some given peak geometry, the model returns each individual sub-slot's probability of being transparent (i.e.
+a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function.
+In Figure 4 below, for two sample peak profiles, the true slots (left), predicted slot (center) and rounded ML slot (right, i.e.
+making the 16 slots with the highest probabilities transparent and vice versa).
+Both of these predicted slots share many similarities with the true slot but there are also some differences -- the testing accuracy was about 68\% averaged over all of the training samples.
+
+\begin{figure}[H]
+	\centering
+	\subfloat{{\includegraphics[height=2in]{figures/fig3_labeled.eps}}}
+	\subfloat{{\includegraphics[height=2in]{figures/fig3b_labeled.eps}}}
+	\caption{Model predictions for two different peak profiles.
+The left-most slot design is the randomly generated slot used to generate this profile, the center plot shows the sigmoid probabilities of a transparent sub-slot, and the right-most plot shows the top 16 sub-slots from the probabilities.}
+\end{figure}
+
+\noindent However, what determines the usefulness of our model is not the similarity of the slot but the similarity of the signal it generates to the objective.
+In order to consider the accuracy and usefulness of our model, we extract the predicted slot geometries, choose the top 16 slots based on the probabilities, and pass 500 of these new generated slots into our COMSOL model in order to compare the signal from the ML-generated slot to the originally desired peak profile.
+We then compare the peak profiles to the objective signal and calculate using the mean square error (MSE), as shown in the top left panel of Figure 5 below; the shape of the distribution matches that of similar work \cite{Nadell:19}.
+In the other panels of Figure 2, we plot the objective peak profile in black against the peak profile of an ML-generated slot, where the color corresponds to the four colored buckets depicted in the histogram.
+Overall, the agreement is quite excellent, particularly for the first two buckets (green and light blue), which compose about 60\% of testing samples with trends and relative amplitudes of the peaks agreeing very well.
+Even in the lower-tiered buckets, like in the bottom right panel of Figure 2, many of the peak profile trends are well matched -- however, there are some areas where the model does not perform as well, resulting in a higher MSE.
+Overall, though, the agreement is excellent and shows that the model can be used to design an acceptable slot for many potentially desired peak profiles.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics{figures/fig2_labeled.eps}
+	\caption{Results from COMSOL simulations of ML-generated slots. The top left panel shows an MSE histogram while the others compare the ML-slot generated peak profile to the objective.}
+\end{figure}
 

### 2022-04-26 1d/peaks_to_slot/constant_power/analysis.py

@@ -3,6 +3,9 @@ import pandas as pd
 import pickle
 import tensorflow as tf
 import matplotlib.pyplot as plt
+import scipy.signal as signal
+import tensorflow_io as tfio
+import scipy
 
 with open('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power/results/generated_slots.pkl', 'rb') as file:
     data = pickle.load(file)
@@ -13,6 +16,8 @@ prediction = [x[2] for x in data]
 floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
 floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
 floquet_back_fake = [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
+
+floquet_back
 
 def import_data():
     """
@@ -157,8 +162,67 @@ def plot_rounded(which):
     ax[3].imshow(tf.expand_dims(pred,1),cmap = 'GnBu')
     ax[4].imshow(tf.expand_dims(naive,1),cmap = 'GnBu')
 
-plot_rounded(8)
+plot_rounded(9)
 
+data[0][0]
+
+
+
+plt.imshow(np.round(np.expand_dims(data[0][1],axis=1)))
+first =
+plt.imshow(np.round(np.expand_dims(data[0][2],axis=1)))
+data[0][2].shape
+np.correlate(np.squeeze(data[0][1]), data[0][2])
+
+np.correlate(np.squeeze(data[0][1]), np.squeeze(data[0][1]))
+
+np.expand_dims(data[0][2],axis=1)
+
+plt.imshow(np.expand_dims(signal.fftconvolve(np.squeeze(data[0][1]), np.flip(data[0][2])),axis=0))
+plt.colorbar()
+
+tf_data = tf.reshape(data[0][1], [1,1,36,1])
+tf_data.shape
+plt.imshow(tf.reshape(tfio.experimental.filter.laplacian(tf.cast(tf_data,tf.float32), ksize=[1,3]),[36,1]),cmap='YlGnBu')
+plt.colorbar()
+
[…]

### 2022-04-26 1d/peaks_to_slot/constant_power/another_analysis copy.py

@@ -1,0 +1,150 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power')
+import pickle
+import tensorflow as tf
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+from preprocess import import_data, import_val_data
+
+###
+
+# slots, peaks = import_data()
+
+# peaks.shape
+# selected_peaks = peaks[peaks[:,1] <0 ]
+# plt.boxplot(selected_peaks)
+# plt.plot(np.mean(peaks,axis=0))
+
+###
+
+with open('1d/peaks_to_slot/constant_power/results/test_data.pkl','rb') as file:
+    test_data = pickle.load(file)
+    peaks, true, pred = test_data
+
+val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation')
+
+grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/grey_trans')
+
+plt.imshow(pred[0])
+
+len(grey_peaks)
+
+plt.plot(peaks[6])
+plt.plot(val_peaks[6])
+plt.plot(grey_peaks[6])
+plt.legend(['Reference','Binary','Greyscale'])
+
+# correct / (len(val_slots) * 36)
+# correct = 0
+# for i in np.arange(len(val_slots)):
+#     correct += (val_slots[i] == true[i]).sum()
+# val_slots
+
+mse_list_binary = []
+mse_list_grey = []
+bucket_1 = []
+bucket_2 = []
+bucket_3 = []
+bucket_4 = []
+for i in np.arange(500):
+    mse_b = ((peaks[i] - val_peaks[i]) ** 2).mean()
+    mse_list_binary.append(mse_b)
+
+    mse_g = ((peaks[i] - grey_peaks[i]) ** 2).mean()
+    mse_list_grey.append(mse_g)
+    if mse_b < 0.0166:
+        bucket_1.append(i)
+    elif mse_b < 0.03236:
[…]

### 2022-04-26 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -1,0 +1,170 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power')
+import pickle
+import tensorflow as tf
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+from preprocess import import_data, import_val_data
+
+###
+
+slots, peaks = import_data()
+
+peaks.shape
+# selected_peaks = peaks[peaks[:,1] <0 ]
+
+fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
+
+boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
+plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
+plt.xlabel('Peak Count')
+plt.ylabel('Amplitude (normalized)')
+
+cmap = mpl.cm.get_cmap('GnBu')
+
+for index, patch in enumerate(boxplot['boxes']):
+    patch.set_facecolor(cmap(index / 36))
+
+plt.savefig('paper/figures/fig2new.eps')
+
+###
+
+with open('1d/peaks_to_slot/constant_power/results/test_data.pkl','rb') as file:
+    test_data = pickle.load(file)
+    peaks, true, pred = test_data
+
+val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation')
+
+grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/grey_trans')
+
+plt.imshow(pred[0])
+
+len(grey_peaks)
+
+plt.plot(peaks[6])
+plt.plot(val_peaks[6])
+plt.plot(grey_peaks[6])
+plt.legend(['Reference','Binary','Greyscale'])
+
+# correct / (len(val_slots) * 36)
+# correct = 0
+# for i in np.arange(len(val_slots)):
+#     correct += (val_slots[i] == true[i]).sum()
+# val_slots
+
+mse_list_binary = []
+mse_list_grey = []
+mse_list_control = []
[…]

### 2022-04-26 1d/peaks_to_slot/constant_power/floquet_analysis.py

@@ -1,0 +1,95 @@
+import numpy as np
+import pandas as pd
+import pickle
+import tensorflow as tf
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import scipy.signal as signal
+import tensorflow_io as tfio
+import scipy
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 14
+plt.rcParams['axes.linewidth'] = 2
+
+def import_data():
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+
+    with open('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/comsol_results/1dconstantslots/1648578904.csv', 'rb') as file:
+        results = np.loadtxt(file, delimiter=",", dtype=float)
+        num_sims = int(results.shape[0] / 361)
+        points = [361 * x for x in np.arange(num_sims + 1)]
+        sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+
+    return sorted_x
+
+dataa = import_data()
+dataa.shape
+dataa[3,271:361].shape
+
+def plot_profiles(num,ax):
+
+    axs[ax].plot(np.arange(91,181),np.flip(dataa[num,271:361]),color = '#0c2c84')
+    axs[ax].plot(np.arange(0,91),np.flip(dataa[num,0:91]), color = '#0c2c84')
+
+    axs[ax].scatter([90 - x for x in floquet_forward], dataa[num,floquet_forward],color = '#7fcdbb')
+    axs[ax].scatter([450 - x for x in floquet_back], dataa[num,floquet_back], color = '#7fcdbb')
+
+plot_profiles(14)
+
+floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+floquet_back
+
+
+floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
+floquet_back
+floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+floquet_back
+[450 - x for x in floquet_back]
+
[…]

### 2022-04-26 1d/peaks_to_slot/constant_power/preprocess.py

@@ -47,6 +47,44 @@ def import_data():
     return np.concatenate(slots_list), np.concatenate(peaks_list)
 
 
+def import_val_data(path):
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+
+    with open(path + '.csv', 'rb') as file:
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet_back + floquet_forward]
+
+            # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
+
+            # max = peaks[past_thresh].max(axis=1)
+            # print(max.shape)
+            # normalized = np.divide(peaks[past_thresh].T,np.max(peaks[past_thresh],axis=1)).T
+            normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
+            # normalized = (peaks / peaks.max(axis=0))
+            peaks_list.append(normalized)
+            # peaks_list.append(normalized)
+            # peaks_list.append(peaks)
+            # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
+    try:
+        with open(path + '.pkl', 'rb') as file:
+                slots = np.array(pickle.load(file))
+                # print(slots.shape)
+                slots_list.append(slots)
+    except:
+        slots_list.append([])
+
+    # return np.concatenate(slots_list), np.concatenate([np.concatenate(peaks_list), np.concatenate(max_list)],axis=1)
+    return np.concatenate(slots_list), np.concatenate(peaks_list)
+
 def get_next_batch(input_array, label_array, start_index, batch_size):
     """
     Accepts an array of inputs and labels along with a starting index and batch

### 2022-04-26 1d/peaks_to_slot/grey/build_model.py

@@ -1,0 +1,156 @@
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+from preprocess import import_data, get_next_batch
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+import argparse
+import pickle
+
+parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
+
+def train(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        with tf.GradientTape() as tape:
+            efarx = model.call(peaks_batch)
+            efarx_loss = model.loss_function(efarx, slot_batch) #slots serves as the mask here
+            # print(efarx_loss)
+
+        gradients = tape.gradient(efarx_loss, model.trainable_variables)
+        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
+
+        loss_list.append(efarx_loss)
+        # acc_list.append(model.accuracy(efarx, slot_batch))
+
+    print('Efarx training loss: ', tf.reduce_mean(loss_list))
+    # print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+
+def test(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+    assump_acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        efarx = model.call(peaks_batch)
+        efarx_loss = model.loss_function(efarx, slot_batch)
+
+        loss_list.append(efarx_loss)
+        # acc_list.append(model.accuracy(efarx, slot_batch))
+        # assump_acc_list.append(model.assump_accuracy(efarx,slot_batch))
+
[…]

### 2022-04-26 1d/peaks_to_slot/grey/peaks_to_slots_model.py

@@ -1,0 +1,96 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1DTranspose
+import tensorflow_io as tfio
+
+
+class LWAPredictionModel(tf.keras.Model):
+    def __init__(self, lr = 5e-5):
+        super(LWAPredictionModel, self).__init__()
+
+        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
+        self.batch_size = 64
+        self.epochs = 10
+
+        self.dense_layers = tf.keras.Sequential()
+        # self.dense_layers.add(Dense(1000, activation = 'relu'))
+        # self.dense_layers.add(Dense(800, activation = 'relu'))
+        self.dense_layers.add(Dense(2000))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(36,activation='ReLU'))
+
+    def call(self, input):
+
+        return self.dense_layers(input)
+
+    # def assump_accuracy(self, prediction, true):
+    #     ba = tf.keras.metrics.BinaryAccuracy()
[…]

### 2022-04-26 1d/peaks_to_slot/grey/preprocess.py

@@ -1,0 +1,99 @@
+import numpy as np
+import tensorflow as tf
+import pickle
+import os
+
+floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
+floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+
+def import_data():
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+
+    timestamp_list = list(set([x.split('.')[0] for x in os.listdir('comsol_results/1dgrey/')]))
+
+    for timestamp in timestamp_list:
+
+        with open('comsol_results/1dgrey/' + timestamp + '.csv', 'rb') as file:
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet_back + floquet_forward]
+
+            # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
+
+            # max = peaks[past_thresh].max(axis=1)
+            # print(max.shape)
+            # normalized = np.divide(peaks[past_thresh].T,np.max(peaks[past_thresh],axis=1)).T
+            normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
+            # normalized = (peaks / peaks.max(axis=0))
+            peaks_list.append(normalized)
+            # peaks_list.append(normalized)
+            # peaks_list.append(peaks)
+            # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
+
+        with open('comsol_results/1dgrey/' + timestamp + '.pkl', 'rb') as file:
+            slots = np.array(pickle.load(file))
+            # print(slots.shape)
+            slots_list.append(slots)
+
+
+
+    # return np.concatenate(slots_list), np.concatenate([np.concatenate(peaks_list), np.concatenate(max_list)],axis=1)
+    return np.concatenate(slots_list), np.concatenate(peaks_list)
+
+
+def import_val_data(path):
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+
[…]

### 2022-04-26 testing.py

@@ -1,0 +1,1 @@
+np.array([0.21,0.11,0.4])

### 2022-04-28 1d/peaks_to_slot/grey/build_model.py
improved grey model

@@ -120,7 +120,7 @@ def main():
         efarx = np.where((efarx > 0.125) & (efarx <= 0.375), 0.25, efarx)
         efarx = np.where((efarx > 0.375) & (efarx <= 0.625), 0.50, efarx)
         efarx = np.where((efarx > 0.625) & (efarx <= 0.875), 0.75, efarx)
-        efarx = np.where((efarx > 0.875) & (efarx <= 1.000), 1.00, efarx)
+        efarx = np.where((efarx > 0.875), 1.00, efarx)
 
         ax[3].imshow(tf.expand_dims(efarx,axis=1))
         save_str = '1d/peaks_to_slot/grey/results/' + str(i) + '.png'

### 2022-04-28 1d/peaks_to_slot/grey/peaks_to_slots_model.py

@@ -10,7 +10,7 @@ class LWAPredictionModel(tf.keras.Model):
         super(LWAPredictionModel, self).__init__()
 
         self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
-        self.batch_size = 64
+        self.batch_size = 128
         self.epochs = 10
 
         self.dense_layers = tf.keras.Sequential()
@@ -40,7 +40,7 @@ class LWAPredictionModel(tf.keras.Model):
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
 
-        self.dense_layers.add(Dense(36,activation='ReLU'))
+        self.dense_layers.add(Dense(36,activation='sigmoid'))
 
     def call(self, input):
 
@@ -69,25 +69,39 @@ class LWAPredictionModel(tf.keras.Model):
 
         # print(prediction)
         # bce = tf.keras.losses.BinaryCrossentropy()
+
+        # print(prediction)
+
         mse =  tf.keras.losses.MeanSquaredError()
+        mse_prewitt =  tf.keras.losses.MeanSquaredError()
+        mse_laplacian =  tf.keras.losses.MeanSquaredError()
         # bce_prewitt = tf.keras.losses.BinaryCrossentropy()
         # bce_laplacian = tf.keras.losses.BinaryCrossentropy()
         # bce_exp2 = tf.keras.losses.BinaryCrossentropy()
 
-        # true_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32))
-        # pred_prewitt = tfio.experimental.filter.prewitt(tf.round(tf.cast(tf.reshape(prediction, [-1,1,36,1]),tf.float32)))
+        # pred_filters = tf.clip_by_values(prediction,0.125,1)
         #
-        # true_laplacian = tfio.experimental.filter.laplacian(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32), ksize = [1,3])
+        true_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32))
+        pred_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(prediction, [-1,1,36,1]),tf.float32))
+        # print(mse_prewitt(true_prewitt, pred_prewitt))
[…]

### 2022-04-28 1d/peaks_to_slot/grey/peaks_to_slots_model.py
Update peaks_to_slots_model.py

@@ -99,7 +99,7 @@ class LWAPredictionModel(tf.keras.Model):
 
         # return bce(true,prediction) + 0.5*bce_exp(true_pooled, pred_pooled) + (0*bce_exp2(true_pooled_2, pred_pooled_2))
         # return 2*bce(true,prediction) + bce_prewitt(true_prewitt, pred_prewitt) + bce_laplacian(true_laplacian, pred_laplacian)
-        return 1*mse(true, prediction) + 0*mse_laplacian(true_laplacian, pred_laplacian) + 1*mse_prewitt(true_prewitt, pred_prewitt)
+        return 2*mse(true, prediction) + 0*mse_laplacian(true_laplacian, pred_laplacian) + 1*mse_prewitt(true_prewitt, pred_prewitt)
         # return mse(true, prediction)
         return mse_prewitt(true_prewitt, pred_prewitt)
 

### 2022-04-28 1d/peaks_to_slot/grey/build_model.py
baseline something works?

@@ -35,10 +35,10 @@ def train(model, slots, peaks):
         model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
 
         loss_list.append(efarx_loss)
-        # acc_list.append(model.accuracy(efarx, slot_batch))
+        acc_list.append(model.accuracy(efarx, slot_batch))
 
     print('Efarx training loss: ', tf.reduce_mean(loss_list))
-    # print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
 
 def test(model, slots, peaks):
     completed = 0
@@ -62,12 +62,12 @@ def test(model, slots, peaks):
         efarx_loss = model.loss_function(efarx, slot_batch)
 
         loss_list.append(efarx_loss)
-        # acc_list.append(model.accuracy(efarx, slot_batch))
+        acc_list.append(model.accuracy(efarx, slot_batch))
         # assump_acc_list.append(model.assump_accuracy(efarx,slot_batch))
 
 
-    # print('Efarx testing loss: ', tf.reduce_mean(loss_list))
-    # print('Efarx testing accuracy:', tf.reduce_mean(acc_list))
+    print('Efarx testing loss: ', tf.reduce_mean(loss_list))
+    print('Efarx testing accuracy:', tf.reduce_mean(acc_list))
     # print('Efarx testing assumption accuracy:', tf.reduce_mean(assump_acc_list))
 
 def main():

### 2022-04-28 1d/peaks_to_slot/grey/peaks_to_slots_model.py

@@ -11,7 +11,7 @@ class LWAPredictionModel(tf.keras.Model):
 
         self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
         self.batch_size = 128
-        self.epochs = 10
+        self.epochs = 50
 
         self.dense_layers = tf.keras.Sequential()
         # self.dense_layers.add(Dense(1000, activation = 'relu'))
@@ -99,12 +99,17 @@ class LWAPredictionModel(tf.keras.Model):
 
         # return bce(true,prediction) + 0.5*bce_exp(true_pooled, pred_pooled) + (0*bce_exp2(true_pooled_2, pred_pooled_2))
         # return 2*bce(true,prediction) + bce_prewitt(true_prewitt, pred_prewitt) + bce_laplacian(true_laplacian, pred_laplacian)
-        return 2*mse(true, prediction) + 0*mse_laplacian(true_laplacian, pred_laplacian) + 1*mse_prewitt(true_prewitt, pred_prewitt)
+        return 2*mse(true, prediction) + 0.5*mse_laplacian(true_laplacian, pred_laplacian) + 1*mse_prewitt(true_prewitt, pred_prewitt)
         # return mse(true, prediction)
         return mse_prewitt(true_prewitt, pred_prewitt)
 
     def accuracy(self, prediction, true):
         ba = tf.keras.metrics.BinaryAccuracy()
-        prediction = tf.round(prediction)
-        true = tf.round(true)
+
+        prediction = np.where((prediction > 0) & (prediction <= 0.125), 0, prediction)
+        prediction = np.where((prediction > 0.125) & (prediction <= 0.375), 0.25, prediction)
+        prediction = np.where((prediction > 0.375) & (prediction <= 0.625), 0.50, prediction)
+        prediction = np.where((prediction > 0.625) & (prediction <= 0.875), 0.75, prediction)
+        prediction = np.where((prediction > 0.875), 1.00, prediction)
+
         return ba(prediction, true)

### 2022-04-28 1d/peaks_to_slot/grey/preprocess.py

@@ -19,6 +19,9 @@ def import_data():
 
     for timestamp in timestamp_list:
 
+        if timestamp == '1651155833':
+            continue
+
         with open('comsol_results/1dgrey/' + timestamp + '.csv', 'rb') as file:
             results = np.loadtxt(file, delimiter=",", dtype=float)
             num_sims = int(results.shape[0] / 361)

### 2022-04-28 1d/peaks_to_slot/grey/peaks_to_slots_model.py
improved?

@@ -1,42 +1,43 @@
 import numpy as np
 import tensorflow as tf
 import tensorflow_probability as tfp
-from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1DTranspose
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
 import tensorflow_io as tfio
 
 
 class LWAPredictionModel(tf.keras.Model):
-    def __init__(self, lr = 5e-5):
+    def __init__(self, lr = 1e-4):
         super(LWAPredictionModel, self).__init__()
 
         self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
         self.batch_size = 128
-        self.epochs = 50
+        self.epochs = 40
 
         self.dense_layers = tf.keras.Sequential()
         # self.dense_layers.add(Dense(1000, activation = 'relu'))
         # self.dense_layers.add(Dense(800, activation = 'relu'))
-        self.dense_layers.add(Dense(2000))
+        # self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Dense(3000))
         # self.dense_layers.add(ReLU())
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
-        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(Dense(3000))
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
         # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(Dense(3000))
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
         # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(Dense(3000))
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
         # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(Dense(3000))
         self.dense_layers.add(LeakyReLU(0.1))
         self.dense_layers.add(Dropout(0.1))
[…]

### 2022-04-29 1d/peaks_to_slot/grey/peaks_to_slots_model.py
first pass trained models for testing

@@ -16,7 +16,8 @@ class LWAPredictionModel(tf.keras.Model):
         self.dense_layers = tf.keras.Sequential()
         # self.dense_layers.add(Dense(1000, activation = 'relu'))
         # self.dense_layers.add(Dense(800, activation = 'relu'))
-        # self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Flatten())
         self.dense_layers.add(Dense(3000))
         # self.dense_layers.add(ReLU())
         self.dense_layers.add(LeakyReLU(0.1))
@@ -44,7 +45,7 @@ class LWAPredictionModel(tf.keras.Model):
         self.dense_layers.add(Dense(36,activation='sigmoid'))
 
     def call(self, input):
-
+        input = tf.expand_dims(input, 2)
         return self.dense_layers(input)
 
     # def assump_accuracy(self, prediction, true):

### 2022-05-02 1d/peaks_to_slot/grey/another_analysis.py
working grey!

@@ -1,0 +1,168 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/grey')
+import pickle
+import tensorflow as tf
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+from preprocess import import_data, import_val_data
+
+###
+
+slots, peaks = import_data()
+
+peaks.shape
+# selected_peaks = peaks[peaks[:,1] <0 ]
+
+fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
+
+boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
+plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
+plt.xlabel('Peak Count')
+plt.ylabel('Amplitude (normalized)')
+
+cmap = mpl.cm.get_cmap('GnBu')
+
+for index, patch in enumerate(boxplot['boxes']):
+    patch.set_facecolor(cmap(index / 36))
+
+plt.savefig('paper/figures/fig2new.eps')
+
+###
+
+with open('1d/peaks_to_slot/grey/results/simpleloss/test_data.pkl','rb') as file:
+    test_data = pickle.load(file)
+    peaks, true, pred = test_data
+
+grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/grey_trans')
+
+plt.imshow(pred[0])
+
+len(grey_peaks)
+
+plt.plot(peaks[6])
+plt.plot(val_peaks[6])
+plt.plot(grey_peaks[6])
+plt.legend(['Reference','Binary','Greyscale'])
+
+# correct / (len(val_slots) * 36)
+# correct = 0
+# for i in np.arange(len(val_slots)):
+#     correct += (val_slots[i] == true[i]).sum()
+# val_slots
+
+mse_list_binary = []
+mse_list_grey = []
+mse_list_control = []
+bucket_1 = []
+bucket_2 = []
+bucket_3 = []
+bucket_4 = []
+for i in np.arange(500):
[…]

### 2022-05-02 1d/peaks_to_slot/constant_power/peaks_to_slots_model.py
new test data

@@ -1,7 +1,7 @@
 import numpy as np
 import tensorflow as tf
 import tensorflow_probability as tfp
-from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1DTranspose
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
 import tensorflow_io as tfio
 
 
@@ -16,6 +16,8 @@ class LWAPredictionModel(tf.keras.Model):
         self.dense_layers = tf.keras.Sequential()
         # self.dense_layers.add(Dense(1000, activation = 'relu'))
         # self.dense_layers.add(Dense(800, activation = 'relu'))
+        self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Flatten())
         self.dense_layers.add(Dense(2000))
         # self.dense_layers.add(ReLU())
         self.dense_layers.add(LeakyReLU(0.1))
@@ -43,7 +45,7 @@ class LWAPredictionModel(tf.keras.Model):
         self.dense_layers.add(Dense(36,activation='sigmoid'))
 
     def call(self, input):
-
+        input = tf.expand_dims(input, 2)
         return self.dense_layers(input)
 
     def assump_accuracy(self, prediction, true):
@@ -69,23 +71,24 @@ class LWAPredictionModel(tf.keras.Model):
 
         # print(prediction)
         bce = tf.keras.losses.BinaryCrossentropy()
-        bce_prewitt = tf.keras.losses.BinaryCrossentropy()
-        bce_laplacian = tf.keras.losses.BinaryCrossentropy()
-        # bce_exp2 = tf.keras.losses.BinaryCrossentropy()
-
-        true_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32))
-        pred_prewitt = tfio.experimental.filter.prewitt(tf.round(tf.cast(tf.reshape(prediction, [-1,1,36,1]),tf.float32)))
-
-        true_laplacian = tfio.experimental.filter.laplacian(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32), ksize = [1,3])
[…]

### 2022-05-03 paper/paper.tex
improved?
analysis

@@
 \usepackage{subcaption}
+\bibliographystyle{ieeetr}
 
@@
 \cite{McCulloch:1943vq} This, of course, includes communications technology -- neural networks have been used extensively in the field because of their unique ability to approximate accurate solutions to nonlinear problems that are commonplace in antenna design.
-Machine learning models are particularly useful in situations where an analytical solution cannot be obtained and/or numerical simulations are expensive \cite{Kim, Massa}, for example when solving the ``direct" problem of approximating an antenna's output \cite{8608745} or modeling a metasurface \cite{Nadell:19}, which could take a finite-element model hours or longer to solve, limiting real-time simulation and design.
-The ``inverse" problem considers the opposite, for example reconstructing an image from scattered light \cite{Sun:18}.
+Machine learning models are particularly useful in situations where an analytical solution cannot be obtained and/or numerical simulations are expensive \cite{Kim, Massa}.
+These types of problems are usually split into two cases, forward and inverse problems.
+The former refers to situations where models attempt to generate the electromagnetic response given some parametric input, while the latter attempts the reverse: predicting those parameters given some signal \cite{9395365}.
 \\
 
+\noindent Examples of direct problems include approximating an antenna's output given a geometry \cite{8608745} or modeling a metasurface \cite{Nadell:19}, which could take a finite-element model hours or longer to solve, limiting real-time simulation and design.
+Inverse problem considers the opposite direction, for example reconstructing an image from scattered light \cite{Sun:18}.
+There have been many applications of neural networks to communications-related problems, for example, in the optimization of massive multiple-input multiple-output (MIMO) systems to improve signal reconstruction quality \cite{8322184} or physical layer design \cite{DBLP:journals/corr/OSheaEC17}.
+\emph{MORE EXAMPLES HERE?} \\
+
 \noindent We are particularly interested in the inverse problem of terahertz leaky-wave antenna (LWA) design because of its high applicability to the field of communications -- given some arbitrarily desired far-field pattern, how can we quickly design, fabricate, and test an antenna that meets our needs?
-LWAs are simple metallic waveguides that have proven very effective in the terahertz range and are particularly interesting because they emit radiation at a frequency-dependent angle with a one-to-one relationship between frequency and angle, which is quite valuable given the narrow character of beams in the terahertz range.
-\cite{doi:10.1063/5.0033126} They have been used in a number of diverse applications including link discovery \cite{Ghasempour:2020tz}, multiplexing and demultiplexing \cite{Karl:2015uh, Ma:2017vo}, and for radar and object detection purposes \cite{Amarasinghe:20}.
-Leaky-wave antennas also stand out for our purposes of rapid design and experimentation because of the ease of fabricating them using novel hot-stamping techniques \cite{Guerboukha:21}.
+Periodic leaky wave-antennas are especially interesting for signal design because of their characteristic emissions at various angles, both forward and backwards scattering, that depend on the periodicity, allowing for a wide variety of potential peak angles \cite{6556051}.
+And while traditional communications systems demand broad angular emission, the terahertz range (i.e.
+$>$ 100 GHz) requires focusing power along narrow directional beams due to substantial power loss as a result of free path losses at higher frequencies \cite{doi:10.1063/1.5014037, Ghasempour:2020tz}, meaning that highly specific peak profile design is crucial.
 \\
 
-\noindent This inverse problem has been explored in the terahertz range using deep neural networks in the context of designing structures to obtain an optimized geometry that produces the desired signal, particularly in relation to metasurface design \cite{Deng:21, 9602997}.
+\noindent LWAs are simple metallic waveguides that have proven very effective in the terahertz range and are particularly interesting because they emit radiation at a frequency-dependent angle with a one-to-one relationship between frequency and angle, which is quite valuable given the narrow character of beams in the terahertz range.
+\cite{doi:10.1063/5.0033126} They have been used in a number of diverse applications including link discovery \cite{Ghasempour:2020tz}, multiplexing and demultiplexing \cite{Karl:2015uh, Ma:2017vo}, and for radar and object detection purposes \cite{Amarasinghe:20, Amarasinghe:21}.
+Leaky-wave antennas also stand out for our purposes of rapid design and experimentation because of the ease of fabricating them using hot-stamping techniques \cite{Guerboukha:21}.
+This inverse problem has been explored in the terahertz range using deep neural networks in the context of designing structures to obtain an optimized geometry that produces the desired signal, particularly in relation to metasurface design \cite{Deng:21, 9602997}.
 The inverse Leaky-wave antenna problem has also been explored, but using a genetic algorithm and outside of the terahertz range at much higher frequencies \cite{Jafar-Zanjani:2018vy}.
-As a result, in this paper, we propose a model to predict the ideal LWA geometry that will generate desired far-field radiation in the terahertz range.
+\\
+
+\noindent As a result, in this paper, we propose a model to predict the ideal LWA geometry that will generate desired far-field radiation in the terahertz range.
+Specifically, we suggest an antenna design where a LWA is broken into sub-slots, each of which can either be metallic, transparent, or somewhere in between (i.e.
+partially transparent).
+Thus, we find that any slot composed of an array of these sub-slots forms a linear superpositioning of periodic modes that can be used to generate highly specific peak profiles.
 
@@
 
-We train a model to predict a slot geometry for a desired far-field signal.
-In particular, we consider a one-dimensional discretized slot split into thirty-six 0.5 micron sub-slots that can either be transparent or metallic, similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}.
-This design essentially creates a non-uniform periodic waveguide that has peaks which can be predicted by Floquet theory.
-In a leaky wave guide with plate separation $h$, the dispersion constant $\beta$ for a given period $\Lambda$ and Floquet mode $p$ for a wave vector $k_0$ is given by:
+We train a model to predict the slot geometry of the LWA for a desired far-field pattern.
+We consider a LWA based on a parallel plate waveguide, the fundamental transverse electric (TE$_1$) mode, and a frequency of 200 GHz.
+Instead of a uniform 1D slot \cite{doi:10.1063/5.0033126}, we discretize the slot into 36 0.5-mm sub-slots that can be transparent, metallic, or somewhere in between (i.e.
+semi-transparent).
+This approach is similar to the approach taken in past explorations of metasurface design \cite{Liu:2022tg, Jafar-Zanjani:2018vy}.
+According to Floquet theory \cite{6556051}, a periodic array of slots excites an infinite number of space harmonics each with its distinct dispersion constant $\beta_p$:
 
@@
 
-\noindent where $k_0$ is the wave number and $h$ is the height of the slot.
-One primary objective design of antenna design is to generate peaks of specific magnitudes at specific locations.
-Thus, we wish to design a slot that will generate the desired amplitudes at the peaks from each possible Floquet mode.
-Our randomly generated slots form linear combinations of periodicities that greatly expands the potential peak profiles compared to a slot with a simple constant periodicity and makes the problem significantly more challenging to solve analytically, introducing the need for a model like ours.
-We wish to compute all possible phase constants for each possible periodicity across all Floquet modes; if they are valid (i.e.
-$\-1 < \frac{\beta}{k_0} = n_{eff} < 1$), we can generate the predicted scattering angle by $\theta = \cos^{-1}(n_{eff})$.
-In Figure 1 below, we compute all possible peak angles for an arbitrary discretized slot predicted by Floquet modes and overlay those peaks on a sample far-field signal generated numerically.
-We will extract these peaks from the simulation data and use them as the input training data along with the slot used to generate it in order to predict a slot design given some peak profile in the neural network model.
+\noindent where $k_0$ is the wave number, $h$ is the height of the waveguide, and $\Lambda$ is the slot periodicity.
+These different modes peak at different angles defined by $\cos(\theta)=\beta_p/k_0$, given that the excited modes can be consider fast-wave (i.e., $|\beta_p|>k_0$).
+Our primary objective is to generate multiple beams with specific magnitudes at specific locations.
+Therefore, instead of a periodic geometry, we consider a non-periodic array of slots.
+By Fourier decomposition, we note that any non-periodic slot design can be viewed as a linear combination of periodic designs $\beta_p$, each peaking at an angle $\cos(\theta)=\beta_p/k_0$.
+The strength (amplitude) of individual peaks can be related to the Fourier coefficients of this decomposition.
+\\
+
+\noindent Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$.
+Indeed, due to the discretization, the possible $\Lambda$ are given by $\Lambda=$.
+Furthermore, due to the fast-wave requirement (i.e., $|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide.
+
+\\ A schematic is shown in Figure 1 below. \\
+
+\begin{figure}
+		\centering
+		\includegraphics[width = 3.2in]{figures/fig5.eps}
+		\caption{The leaky wave antenna geometry.
+Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; in order to maintain constant power, the number of each type of slot is kept equal.}
+\end{figure}
+
+\noindent see, I can keep typing things.
 

### 2022-05-03 paper/paper_comments.tex
analysis

--- 2022-04-26 paper/paper.tex
@@
 \title{Deep Learning Methods for Optimizing Terahertz Leaky Wave Antenna Design}
-\author{J. Neronha, H. Guerboukha, and D. Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
+\author{J. Neronha, H. Guerboukha, and D. M. Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
 \date{}
@@
 
-We train a model to predict a slot geometry for a desired far-field signal.
+We train a model to predict the slot geometry of the LWA for a desired far-field pattern.
+We consider a LWA based on a parallel plate waveguide, the fundamental transverse electric (TE$_1$) mode, and a frequency of 200 GHz.
+Instead of a uniform 1D slot (cite some of our previous papers here), we discretize the slot into 36 0.5-mm sub-slots that can either be transparent or metallic.
+This approach is similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}.
+According to Floquet theory, a periodic array of slots excites an infinite number of space harmonics each with its distinct dispersion constant $\beta_p$:
+\[\beta=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1} \label{eq:special}\]
+
+\noindent where $k_0$ is the wave number, $h$ is the height of the waveguide, and $\Lambda$ is the slot periodicity.
+These different modes peak at different angles defined by $\cos(\theta)=\beta_p/k_0$, given that the excited modes can be consider fast-wave (i.e., $|\beta_p|>k_0$).
+
+Our primary objective is to generate multiple beams with specific magnitudes at specific locations.
+Therefore, instead of a periodic geometry, we consider a non-periodic array of slots.
+By Fourier decomposition, we note that any non-periodic slot design can be viewed as a linear combination of periodic designs $\beta_p$, each peaking at an angle $\cos(\theta)=\beta_p/k_0$.
+The strength (amplitude) of individual peaks can be related to the Fourier coefficients of this decomposition.
+
+Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$.
+Indeed, due to the discretization, the possible $\Lambda$ are given by $\Lambda=$.
+Furthermore, due to the fast-wave requirement (i.e., $|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide.
+
+NEXT EXPLAIN FIG. 1A AND 1B SEPARATELY. WHAT ARE YOU PLOTTING?
+
+%Our randomly generated slots form linear combinations of periodicities that greatly expands the potential peak profiles compared to a slot with a simple constant periodicity and makes the problem significantly more challenging to solve analytically, introducing the need for a model like ours.
+We wish to compute all possible phase constants for each possible periodicity across all Floquet modes; if they are valid (i.e.
+$\-1 < \frac{\beta}{k_0} = n_{eff} < 1$), we can generate the predicted scattering angle by $\theta = \cos^{-1}(n_{eff})$.
+In Figure 1 below, we compute all possible peak angles for an arbitrary discretized slot predicted by Floquet modes and overlay those peaks on a sample far-field signal generated numerically.
+We will extract these peaks from the simulation data and use them as the input training data along with the slot used to generate it in order to predict a slot design given some peak profile in the neural network model.
+
+%We train a model to predict a slot geometry for a desired far-field signal.
 In particular, we consider a one-dimensional discretized slot split into thirty-six 0.5 micron sub-slots that can either be transparent or metallic, similar to the approach taken in past explorations of metasurface design \cite{Jafar-Zanjani:2018vy}.
@@
 
-\[\beta=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1} \label{eq:special}\]
+%\[\beta=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1} \label{eq:special}\]
 
-\noindent where $k_0$ is the wave number and $h$ is the height of the slot.
+%\noindent where $k_0$ is the wave number and $h$ is the height of the slot.
 One primary objective design of antenna design is to generate peaks of specific magnitudes at specific locations.

### 2022-05-03 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -39,18 +39,20 @@ with open('1d/peaks_to_slot/constant_power/results/test_data.pkl','rb') as file:
     test_data = pickle.load(file)
     peaks, true, pred = test_data
 
-val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation')
+# val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation_old')
 
-grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/grey_trans')
+val51_slots, val51_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation51')
 
-plt.imshow(pred[0])
+plt.imshow(tf.expand_dims(pred[80] > tf.sort(pred[80])[16],1))
+
+plt.imshow(tf.expand_dims(val51_slots[80],1))
 
 len(grey_peaks)
 
-plt.plot(peaks[6])
-plt.plot(val_peaks[6])
-plt.plot(grey_peaks[6])
-plt.legend(['Reference','Binary','Greyscale'])
+plt.plot(peaks[7])
+# plt.plot(val_peaks[7])
+plt.plot(val51_peaks[7])
+plt.legend(['Reference','Binary','Conv'])
 
 # correct / (len(val_slots) * 36)
 # correct = 0
@@ -59,21 +61,21 @@ plt.legend(['Reference','Binary','Greyscale'])
 # val_slots
 
 mse_list_binary = []
-mse_list_grey = []
+# mse_list_grey = []
 mse_list_control = []
 bucket_1 = []
 bucket_2 = []
 bucket_3 = []
 bucket_4 = []
 for i in np.arange(500):
-    mse_b = ((peaks[i] - val_peaks[i]) ** 2).mean()
+    mse_b = ((peaks[i] - val51_peaks[i]) ** 2).mean()
     mse_list_binary.append(mse_b)
 
-    mse_g = ((peaks[i] - grey_peaks[i]) ** 2).mean()
-    mse_list_grey.append(mse_g)
+    # mse_g = ((peaks[i] - grey_peaks[i]) ** 2).mean()
+    # mse_list_grey.append(mse_g)
 
     try:
-        mse_c = ((peaks[i] - val_peaks[i+3]) ** 2).mean()
[…]

### 2022-05-03 1d/peaks_to_slot/constant_power/floquet_analysis.py

@@ -63,7 +63,7 @@ lambdaa = 3e8/freq
 k0 = 2*np.pi/lambdaa
 h = 1e-3;
 
-Lambda = np.arange(1e-3, 10e-3, 1e-3)
+Lambda = np.arange(1e-3, 19e-3, 1e-3)
 p = np.arange(-80,81,1)
 
 betaz = np.zeros((len(Lambda),len(p)))
@@ -79,11 +79,12 @@ for i in np.arange(len(Lambda)):
             neff_works[k,:] = [neff[i,j], np.degrees(np.arccos(neff[i,j])), Lambda[i], p[j]];
             k=k+1;
 
-size(neff_works,1) % this number is the total number of possible angles
-neff_works[:61,3].min()
+print(k)
+
+neff_works[:59,3].min()
 
 fig, axs = plt.subplots(1,2,tight_layout=True,figsize=(8,3.5))
-axy = axs[0].scatter(np.arange(61),neff_works[:61,1], c = neff_works[:61,3], cmap = 'GnBu', edgecolors = 'black')
+axy = axs[0].scatter(np.arange(229),neff_works[:229,1], c = neff_works[:229,3], cmap = 'GnBu', edgecolors = 'black')
 axs[0].set_xlabel('Peak Count')
 axs[0].set_ylabel('Angle')
 plt.colorbar(axy)
@@ -93,3 +94,8 @@ plot_profiles(0,1)
 axs[1].set_xlabel('Angle')
 axs[1].set_ylabel('Amplitude (dB)')
 plt.savefig('paper/figures/fig4.eps')
+
+neff_works[:229,1].sort()
+len(np.unique(neff_works[:229,1]))
+
+np.unique(neff_works[:229,1])

### 2022-05-07 paper/paper.tex
intro exp

@@
 Furthermore, due to the fast-wave requirement (i.e., $|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide.
+\\
 
-\\ A schematic is shown in Figure 1 below. \\
+ A schematic is shown in Figure 1 below. \\
 
@@
 
-\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20.
+\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
 Figure 2b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
-The network, which is built with TensorFlow, has six dense layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
+The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
 The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.

### 2022-05-07 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -118,6 +118,7 @@ axs[1].set_ylabel('Count')
 
 ####
 
+bucket_1
 
 fig, axs = plt.subplots(2,2,tight_layout=True,figsize=(6,4))
 
@@ -131,8 +132,8 @@ axs[0,0].set_xlabel('Mean Square Error')
 axs[0,0].set_ylabel('Count')
 
 ## bucket_1 example (22.8%)
-axs[0,1].plot(peaks[22], color = 'black')
-axs[0,1].plot(val_peaks[22], color = '#7fcdbb')
+axs[0,1].plot(peaks[72], color = 'black')
+axs[0,1].plot(val51_peaks[72], color = '#7fcdbb')
 axs[0,1].set_xlabel('Peak Count')
 axs[0,1].set_ylabel('Amplitude')
 
@@ -171,22 +172,26 @@ def top_16(slot):
     out = [1 if x >= median else 0 for x in slot]
     return out
 
+bucket_1
+
+np.mean(np.square(peaks[194] - val51_peaks[194]))
+
 fig, ax = plt.subplots(1,4,gridspec_kw={'width_ratios': [6, 1, 1, 1]})
-ax[0].plot(peaks[408])
+ax[0].plot(peaks[194])
+ax[0].plot(val51_peaks[194])
 ax[0].set_xlabel('Peak Count')
 ax[0].set_ylabel('Amplitude')
 # ax[0].plot(val_peaks[0])
-ax[1].imshow(tf.expand_dims(true[408],1),cmap='YlGnBu')
+ax[1].imshow(tf.expand_dims(true[194],1),cmap='YlGnBu')
 ax[1].axes.xaxis.set_visible(False)
 ax[1].axes.yaxis.set_visible(False)
-ax[2].imshow(tf.expand_dims(pred[408],1),cmap='YlGnBu')
+ax[2].imshow(tf.expand_dims(pred[194],1),cmap='YlGnBu')
 ax[2].axes.xaxis.set_visible(False)
 ax[2].axes.yaxis.set_visible(False)
-forcmap = ax[3].imshow(tf.expand_dims(top_16(pred[408]),1),cmap='YlGnBu')
+forcmap = ax[3].imshow(tf.expand_dims(top_16(pred[194]),1),cmap='YlGnBu')
 ax[3].axes.xaxis.set_visible(False)
-ax[3].axes.yaxis.set_visible(False)
[…]

### 2022-05-07 experiments/194.m

@@ -1,0 +1,48 @@
+clear all
+clc
+close all
+
+Files=dir('binarywaveguide194');
+N = length(Files);
+[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 4:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2095:2150),abs(B(2095:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+axis square
+% colormap(brewermap([],'GnBu'))
+
+order=-1;
+c=3e8;
+period = 0.95e-3;
+
+theta_pm_back = linspace(0,150,1400)
+nu_vector=(150:0.1:280);
+nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white');

### 2022-05-07 experiments/base.m

@@ -1,0 +1,39 @@
+clear all
+clc
+close all
+
+Files=dir('baselwa');
+N = length(Files);
+[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 4:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+plot1 = pcolor(1:90,f(2095:2150),abs(B(2095:2150,1:90)));
+set(plot1, 'EdgeColor', 'none');
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+axis square
+% colormap(brewermap([],'GnBu'))

### 2022-05-07 experiments/baseperiodic.m

@@ -1,0 +1,48 @@
+clear all
+clc
+close all
+
+Files=dir('newbaseperiodic');
+N = length(Files);
+[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 4:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+plot1 = pcolor(1:151,f(2095:2150),abs(B(2095:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+axis square
+% colormap(brewermap([],'GnBu'))
+
+order=-1;
+c=3e8;
+period = 0.95e-3;
+
+theta_pm_back = linspace(0,150,1400)
+nu_vector=(150:0.1:280);
+nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white');

### 2022-05-07 experiments/ml.m

@@ -1,0 +1,6 @@
+B = fftshift(fft(A(:,2)));
+t = A(:,1);
+fmax = 0.5/(t(2)-t(1));
+f = linspace(-fmax,fmax,size(A,1))'
+
+semilogy(f,abs(B).^2))

### 2022-05-07 1d/peaks_to_slot/constant_power/preprocess.py
fixing indices in model...

@@ -3,8 +3,7 @@ import tensorflow as tf
 import pickle
 import os
 
-floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
-floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+floquet = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90] + [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
 
 def import_data():
     """
@@ -24,7 +23,7 @@ def import_data():
             num_sims = int(results.shape[0] / 361)
             points = [361 * x for x in np.arange(num_sims + 1)]
             sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
-            peaks = sorted_x[:,floquet_back + floquet_forward]
+            peaks = sorted_x[:,floquet]
 
             # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
 

### 2022-05-07 experiments/194.m

@@ -36,7 +36,7 @@ nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
 hold on 
 plot(theta_pm, nu_pm,'linewidth',2,'color','r')
 axis square
-% colormap(brewermap([],'GnBu'))
+colormap(brewermap([],'GnBu'))
 
 order=-1;
 c=3e8;
@@ -45,4 +45,14 @@ period = 0.95e-3;
 theta_pm_back = linspace(0,150,1400)
 nu_vector=(150:0.1:280);
 nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
-plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white');
+plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
+
+objective194 = readmatrix('objective194.csv');
+expected194 = readmatrix('expected194.csv');
+
+figure
+semilogy(abs(B(2112,:)) / max(abs(B(2112,:))))
+hold on
+semilogy(objective194(1:180,2) / max(objective194(1:180,2)))
+
+semilogy(expected194(1:180,2) / max(expected194(1:180,2)))

### 2022-05-09 1d/peaks_to_slot/constant_power/floquet_analysis.py
more data

@@ -33,18 +33,11 @@ dataa = import_data()
 dataa.shape
 dataa[3,271:361].shape
 
-def plot_profiles(num,ax):
-
-    axs[ax].plot(np.arange(91,181),np.flip(dataa[num,271:361]),color = '#0c2c84')
-    axs[ax].plot(np.arange(0,91),np.flip(dataa[num,0:91]), color = '#0c2c84')
-
-    axs[ax].scatter([90 - x for x in floquet_forward], dataa[num,floquet_forward],color = '#7fcdbb')
-    axs[ax].scatter([450 - x for x in floquet_back], dataa[num,floquet_back], color = '#7fcdbb')
-
-plot_profiles(14)
-
 floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
 floquet_back
+
+floquet = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90] + [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
+
 
 
 floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
@@ -52,6 +45,21 @@ floquet_back
 floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
 floquet_back
 [450 - x for x in floquet_back]
+
+def plot_profiles(num):
+
+    plt.plot(np.arange(91,181),np.flip(dataa[num,271:361]),color = '#0c2c84')
+    plt.plot(np.arange(0,91),np.flip(dataa[num,0:91]), color = '#0c2c84')
+
+    plt.scatter([90 - x for x in floquet_forward], dataa[num,floquet_forward],color = '#7fcdbb')
+    plt.scatter([450 - x for x in floquet_back], dataa[num,floquet_back], color = '#7fcdbb')
+
+plot_profiles(14)
+
+plt.plot(np.arange(0,180),dataa[14,0:180], color = '#0c2c84')
+plt.scatter(floquet,dataa[14,floquet])
+
+plt.plot(dataa[14,0:360])
 
 floquet_back_fake = [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
 

### 2022-05-09 1d/peaks_to_slot/constant_power/preprocess.py

@@ -4,6 +4,8 @@ import pickle
 import os
 
 floquet = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90] + [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]
+floquet2 = [1 + x for x in floquet]
+
 
 def import_data():
     """
@@ -23,7 +25,7 @@ def import_data():
             num_sims = int(results.shape[0] / 361)
             points = [361 * x for x in np.arange(num_sims + 1)]
             sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
-            peaks = sorted_x[:,floquet]
+            peaks = sorted_x[:,floquet2]
 
             # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
 
@@ -60,7 +62,7 @@ def import_val_data(path):
             num_sims = int(results.shape[0] / 361)
             points = [361 * x for x in np.arange(num_sims + 1)]
             sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
-            peaks = sorted_x[:,floquet_back + floquet_forward]
+            peaks = sorted_x[:,floquet]
 
             # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
 

### 2022-05-09 1d/peaks_to_slot/grey/another_analysis.py

@@ -14,7 +14,7 @@ from preprocess import import_data, import_val_data
 
 ###
 
-slots, peaks = import_data()
+slots, peaks, signals = import_data()
 
 peaks.shape
 # selected_peaks = peaks[peaks[:,1] <0 ]
@@ -39,16 +39,29 @@ with open('1d/peaks_to_slot/grey/results/simpleloss/test_data.pkl','rb') as file
     test_data = pickle.load(file)
     peaks, true, pred = test_data
 
-grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/grey_trans')
+grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/grey/results/simpleloss/simplelosstest')
 
-plt.imshow(pred[0])
+grey_slots
 
-len(grey_peaks)
+with open('1d/peaks_to_slot/grey/results/test_data.pkl','rb') as file:
+    test_data = pickle.load(file)
+    diff_real_peaks, diff_true, diff_pred = test_data
 
-plt.plot(peaks[6])
-plt.plot(val_peaks[6])
-plt.plot(grey_peaks[6])
-plt.legend(['Reference','Binary','Greyscale'])
+diff_slots, diff_peaks = import_val_data('1d/peaks_to_slot/grey/results/difflosstest')
+
+def test(i):
+
+    plt.plot(peaks[i])
+    plt.plot(grey_peaks[i+6])
+    plt.plot(diff_peaks[i])
+    plt.legend(['Reference','Simple','Complicated'])
+
+    x = ((peaks[i] - diff_peaks[i]) ** 2).mean()
+    y = ((peaks[i] - grey_peaks[i]) ** 2).mean()
+
+    return(x,y)
+
+test(23)
 
 # correct / (len(val_slots) * 36)
 # correct = 0
@@ -56,38 +69,45 @@ plt.legend(['Reference','Binary','Greyscale'])
 #     correct += (val_slots[i] == true[i]).sum()
 # val_slots
 
-mse_list_binary = []
+bucket_2
+
+np.array(mse_list_grey).mean()
+np.array(mse_list_diff).mean()
+np.array(mse_list_control).mean()
 mse_list_grey = []
+mse_list_diff = []
 mse_list_control = []
 bucket_1 = []
[…]

### 2022-05-09 experiments/194.m

@@ -25,8 +25,10 @@ for k = 4:N
     f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
 end
 figure
-plot1 = pcolor(1:151,f(2095:2150),abs(B(2095:2150,1:151)));
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
 set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
 
 theta_pm = linspace(0,90,1000); 
 order_m = 1; % order of the PPWG mode
@@ -34,18 +36,18 @@ b = 1e-3; % slit height
 neff = 1; % effective refractive index between the plates
 nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
 hold on 
-plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
 axis square
-colormap(brewermap([],'GnBu'))
+colormap(flipud(brewermap([],'GnBu')))
 
 order=-1;
 c=3e8;
 period = 0.95e-3;
-
-theta_pm_back = linspace(0,150,1400)
-nu_vector=(150:0.1:280);
-nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
-plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
+% 
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
+% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+% plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
 
 objective194 = readmatrix('objective194.csv');
 expected194 = readmatrix('expected194.csv');

### 2022-05-09 experiments/a241.m

@@ -1,0 +1,61 @@
+clear all
+clc
+close all
+
+Files=dir('binarywaveguide241');
+N = length(Files);
+[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 4:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+colormap(flipud(brewermap([],'GnBu')))
+
+order=-1;
+c=3e8;
+period = 0.95e-3;
+% 
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
+% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
[…]

### 2022-05-12 1d/peaks_to_slot/constant_power/another_analysis.py
grey testing

@@ -12,6 +12,11 @@ plt.rcParams['axes.linewidth'] = 2
 
 from preprocess import import_data, import_val_data
 
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
 ###
 
 slots, peaks = import_data()
@@ -35,13 +40,13 @@ plt.savefig('paper/figures/fig2new.eps')
 
 ###
 
-with open('1d/peaks_to_slot/constant_power/results/test_data58.pkl','rb') as file:
+with open('1d/peaks_to_slot/constant_power/results/test_data510.pkl','rb') as file:
     test_data = pickle.load(file)
-    peaks, true, pred = test_data
+    peaks, true, pred, waves = test_data
 
 # val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation_old')
 
-val58_slots, val58_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation58')
+val510_slots, val510_peaks, val510_waves = import_val_data('1d/peaks_to_slot/constant_power/results/validation510')
 
 plt.imshow(tf.expand_dims(pred[80] > tf.sort(pred[80])[16],1))
 
@@ -51,7 +56,7 @@ len(grey_peaks)
 
 plt.plot(peaks[9])
 # plt.plot(val_peaks[7])
-plt.plot(val58_peaks[9])
+plt.plot(val59_peaks[9])
 plt.legend(['Reference','Binary','Conv'])
 
 # correct / (len(val_slots) * 36)
@@ -68,14 +73,14 @@ bucket_2 = []
 bucket_3 = []
 bucket_4 = []
 for i in np.arange(500):
-    mse_b = ((peaks[i] - val58_peaks[i]) ** 2).mean()
+    mse_b = ((peaks[i] - val510_peaks[i]) ** 2).mean()
     mse_list_binary.append(mse_b)
 
     # mse_g = ((peaks[i] - grey_peaks[i]) ** 2).mean()
[…]

### 2022-05-12 1d/peaks_to_slot/constant_power/build_model.py

@@ -8,15 +8,6 @@ import argparse
 import pickle
 import random
 
-a = np.array([3,2,5,6])
-b = np.array([1,4,7,6])
-c = np.array([5,6,4,2])
-
-train_test_split(a,b,test_size=0.5,random_state=431432)
-train_test_split(a,c,test_size=0.5,random_state=42132)
-
-
-
 parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
 
 def train(model, slots, peaks):

### 2022-05-12 1d/peaks_to_slot/constant_power/preprocess.py

@@ -64,6 +64,7 @@ def import_val_data(path):
     slots_list = []
     peaks_list = []
     max_list = []
+    wave_list = []
 
     with open(path + '.csv', 'rb') as file:
             results = np.loadtxt(file, delimiter=",", dtype=float)
@@ -80,6 +81,7 @@ def import_val_data(path):
             normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
             # normalized = (peaks / peaks.max(axis=0))
             peaks_list.append(normalized)
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
             # peaks_list.append(normalized)
             # peaks_list.append(peaks)
             # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
@@ -92,7 +94,7 @@ def import_val_data(path):
         slots_list.append([])
 
     # return np.concatenate(slots_list), np.concatenate([np.concatenate(peaks_list), np.concatenate(max_list)],axis=1)
-    return np.concatenate(slots_list), np.concatenate(peaks_list)
+    return np.concatenate(slots_list), np.concatenate(peaks_list), np.concatenate(wave_list)
 
 def get_next_batch(input_array, label_array, start_index, batch_size):
     """

### 2022-05-12 1d/peaks_to_slot/grey/build_model.py

@@ -6,6 +6,7 @@ from sklearn.model_selection import train_test_split
 import matplotlib.pyplot as plt
 import argparse
 import pickle
+import random
 
 parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
 
@@ -72,9 +73,12 @@ def test(model, slots, peaks):
 
 def main():
 
-    slots, peaks = import_data()
+    slots, peaks, waves = import_data()
 
-    slot_train, slot_test, peaks_train, peaks_test = train_test_split(slots, peaks, test_size=0.2)
+    state = random.randint(0,100000)
+
+    slot_train, slot_test, peaks_train, peaks_test = train_test_split(slots, peaks, test_size=0.2, random_state = state)
+    _, _, waves_train, waves_test = train_test_split(slots, waves, test_size=0.2, random_state = state)
     print(peaks_train.shape)
     print(peaks_test.shape)
 
@@ -91,45 +95,45 @@ def main():
     peak_sim = []
 
     output = Model.call(peaks_test)
-    saved_data = [peaks_test, slot_test, output]
+    saved_data = [peaks_test, slot_test, output, waves_test]
 
     with open('1d/peaks_to_slot/grey/results/test_data.pkl', 'wb') as f:
         pickle.dump(saved_data, f)
 
-
-    # for random in [36, 185, 234, 368, 492, 567, 698, 722, 813, 922]:
-    for i in np.arange(10):
-
-        random = np.random.randint(0,slot_test.shape[0])
-
-        efarx = Model.call(tf.expand_dims(peaks_test[random],0))
-        # print(tf.expand_dims(peaks_test[random],0).shape)
-        efarx = tf.squeeze(efarx)
-
-        truedesign = tf.expand_dims(slot_test[random],axis = 1)
-
-        fig = plt.figure()
-        ax = fig.subplots(1,4, gridspec_kw={'width_ratios': [3, 1, 1, 1]})
-        ax[0].plot(peaks_test[random])
-        ax[1].imshow(truedesign)
-        ax[2].imshow(tf.expand_dims(efarx,axis=1))
-
-        efarx = efarx.numpy()
-
-        efarx = np.where((efarx > 0) & (efarx <= 0.125), 0, efarx)
[…]

### 2022-05-12 1d/peaks_to_slot/grey/peaks_to_slots_model.py

@@ -11,7 +11,7 @@ class LWAPredictionModel(tf.keras.Model):
 
         self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
         self.batch_size = 128
-        self.epochs = 40
+        self.epochs = 35
 
         self.dense_layers = tf.keras.Sequential()
         # self.dense_layers.add(Dense(1000, activation = 'relu'))
@@ -75,35 +75,37 @@ class LWAPredictionModel(tf.keras.Model):
         # print(prediction)
 
         mse =  tf.keras.losses.MeanSquaredError()
-        mse_prewitt =  tf.keras.losses.MeanSquaredError()
-        mse_laplacian =  tf.keras.losses.MeanSquaredError()
-        # bce_prewitt = tf.keras.losses.BinaryCrossentropy()
-        # bce_laplacian = tf.keras.losses.BinaryCrossentropy()
-        # bce_exp2 = tf.keras.losses.BinaryCrossentropy()
-
-        # pred_filters = tf.clip_by_values(prediction,0.125,1)
+        # mse_prewitt =  tf.keras.losses.MeanSquaredError()
+        # mse_laplacian =  tf.keras.losses.MeanSquaredError()
+        # # bce_prewitt = tf.keras.losses.BinaryCrossentropy()
+        # # bce_laplacian = tf.keras.losses.BinaryCrossentropy()
+        # # bce_exp2 = tf.keras.losses.BinaryCrossentropy()
         #
-        true_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32))
-        pred_prewitt = tfio.experimental.filter.prewitt(tf.cast(tf.reshape(prediction, [-1,1,36,1]),tf.float32))
-        # print(mse_prewitt(true_prewitt, pred_prewitt))
-        # # pred_prewitt = tfio.experimental.filter.prewitt(tf.round(tf.cast(tf.reshape(prediction, [-1,1,36,1]),tf.float32)))
+        # # pred_filters = tf.clip_by_values(prediction,0.125,1)
         # #
-
-        # print(true_prewitt)
-        # print(pred_prewitt)
-
-        true_laplacian = tfio.experimental.filter.laplacian(tf.cast(tf.reshape(true, [-1,1,36,1]),tf.float32), ksize = [1,3])
[…]

### 2022-05-12 1d/peaks_to_slot/grey/preprocess.py

@@ -3,8 +3,13 @@ import tensorflow as tf
 import pickle
 import os
 
-floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
-floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+# floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
+# floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
 
 def import_data():
     """
@@ -14,6 +19,8 @@ def import_data():
     slots_list = []
     peaks_list = []
     max_list = []
+    wave_list = []
+
 
     timestamp_list = list(set([x.split('.')[0] for x in os.listdir('comsol_results/1dgrey/')]))
 
@@ -27,7 +34,7 @@ def import_data():
             num_sims = int(results.shape[0] / 361)
             points = [361 * x for x in np.arange(num_sims + 1)]
             sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
-            peaks = sorted_x[:,floquet_back + floquet_forward]
+            peaks = sorted_x[:,floquet]
 
             # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
 
@@ -37,6 +44,7 @@ def import_data():
             normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
             # normalized = (peaks / peaks.max(axis=0))
             peaks_list.append(normalized)
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
             # peaks_list.append(normalized)
             # peaks_list.append(peaks)
             # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
@@ -49,7 +57,7 @@ def import_data():
 
 
[…]

### 2022-05-12 experiments/a241.m

@@ -4,7 +4,7 @@ close all
 
 Files=dir('binarywaveguide241');
 N = length(Files);
-[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+[t,w]=textread(strcat('binarywaveguide241/',Files(3).name),'%f%f','headerlines',6);  % read first for size
 T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
 T(:,1)=t;
 W(:,1)=w;
@@ -14,10 +14,10 @@ t = T(:,1);
 fmax = 0.5/(t(2)-t(1));
 f(:,1) = linspace(-fmax,fmax,size(W,1));
 
-for k = 4:N
+for k = 3:N
     name = Files(k).name;
     x = split(name,'.');
-    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide241/',name),'%f%f','headerlines',6);
     
     B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
     t = T(:,str2double(x(1)) + 1);
@@ -39,7 +39,7 @@ hold on
 plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
 axis square
 colormap(flipud(brewermap([],'GnBu')))
-
+legend('Data','n=0')
 order=-1;
 c=3e8;
 period = 0.95e-3;
@@ -53,15 +53,25 @@ objective241 = readmatrix('objective241.csv');
 expected241 = readmatrix('expected241.csv');
 
 figure
-semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
+% semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
 hold on
-semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
-semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
+% semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
+% semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
+
+plot(7:151,mag2db(abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7)))))
[…]

### 2022-05-12 experiments/base.m

@@ -4,7 +4,7 @@ close all
 
 Files=dir('baselwa');
 N = length(Files);
-[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+[t,w]=textread(strcat('baselwa/',Files(3).name),'%f%f','headerlines',6);  % read first for size
 T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
 T(:,1)=t;
 W(:,1)=w;
@@ -14,10 +14,10 @@ t = T(:,1);
 fmax = 0.5/(t(2)-t(1));
 f(:,1) = linspace(-fmax,fmax,size(W,1));
 
-for k = 4:N
+for k = 3:N
     name = Files(k).name;
     x = split(name,'.');
-    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('baselwa/',name),'%f%f','headerlines',6);
     
     B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
     t = T(:,str2double(x(1)) + 1);
@@ -34,6 +34,9 @@ b = 1e-3; % slit height
 neff = 1; % effective refractive index between the plates
 nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
 hold on 
-plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+plot(theta_pm, nu_pm,'linewidth',3,'color','#f7a400')
 axis square
-% colormap(brewermap([],'GnBu'))
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+legend('n=0')
+colormap(flipud(brewermap([],'GnBu')))

### 2022-05-12 experiments/baseperiodic.m

@@ -4,7 +4,7 @@ close all
 
 Files=dir('newbaseperiodic');
 N = length(Files);
-[t,w]=textread(Files(3).name,'%f%f','headerlines',6);  % read first for size
+[t,w]=textread(strcat('newbaseperiodic/',Files(3).name),'%f%f','headerlines',6);  % read first for size
 T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
 T(:,1)=t;
 W(:,1)=w;
@@ -14,10 +14,10 @@ t = T(:,1);
 fmax = 0.5/(t(2)-t(1));
 f(:,1) = linspace(-fmax,fmax,size(W,1));
 
-for k = 4:N
+for k = 3:N
     name = Files(k).name;
     x = split(name,'.');
-    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(name,'%f%f','headerlines',6);
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('newbaseperiodic/',name),'%f%f','headerlines',6);
     
     B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
     t = T(:,str2double(x(1)) + 1);
@@ -25,7 +25,7 @@ for k = 4:N
     f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
 end
 
-plot1 = pcolor(1:151,f(2095:2150),abs(B(2095:2150,1:151)));
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
 set(plot1, 'EdgeColor', 'none');
 
 theta_pm = linspace(0,90,1000); 
@@ -34,15 +34,18 @@ b = 1e-3; % slit height
 neff = 1; % effective refractive index between the plates
 nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
 hold on 
-plot(theta_pm, nu_pm,'linewidth',2,'color','r')
+plot(theta_pm, nu_pm,'linewidth',3,'color','#f7a400')
 axis square
-% colormap(brewermap([],'GnBu'))
+colormap(flipud(brewermap([],'GnBu')))
 
 order=-1;
 c=3e8;
 period = 0.95e-3;
 
[…]

### 2022-05-24 paper/paper.tex
grey testing
new

@@
 
-\title{Deep Learning Methods for Optimizing Terahertz Leaky Wave Antenna Design}
+\title{Optimizing Terahertz Leaky Wave Antennas Using Deep Learning Predicted Periodically  Modulated Slots}
 \author{J. Neronha, H. Guerboukha, and D. Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
@@
 Furthermore, due to the fast-wave requirement (i.e., $|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide.
-\\
+We propose two different schemes for generating a desired signal:
 
- A schematic is shown in Figure 1 below. \\
+\begin{enumerate}
+	\item each sub-slot can be either transparent or metallic (left panel of Figure 1)
+	\item each sub-slot can also take some intermediate value of opacity (right panel of Figure 1)
+\end{enumerate}
+
+\noindent A schematic of both schemes is shown in Figure 1 below.
+Additionally, Figure 2 shows all possible peaks from the various modes and periodicities Floquet theory and these peaks overlaid a sample far-field signal from a similar geometry.
 
@@
 		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
+		\includegraphics[width = 6in]{figures/fig5.eps}
 		\caption{The leaky wave antenna geometry.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; in order to maintain constant power, the number of each type of slot is kept equal.}
+The left panel shows the binary case, where dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries.
+In the right panel, the boundary conditions are no longer discretized and can take on some intermediate value of transparency, as seen by the sub-slots with colors between light and dark.}
 \end{figure}
-
-\noindent see, I can keep typing things.
 
@@
 a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation.
+A similar process is carried out for the grey scheme, except that slots are randomly assigned to buckets of various levels of transparency.
 We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its API.
 Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs; using only a few tens of thousands sets of training data, we can predict an optimal slot design for an arbitrary peak profile.
-The simulation geometry is shown in Figure 2a below \\
+\\
 
-\begin{figure}[H]
-	\caption{Simulation geometry (left) and possible peak profiles (right)}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
-		\caption{The leaky wave antenna geometry used to generate training data.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; both are randomly generated so that the slots are half and half.}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.55\textwidth}
-		\centering
-		\includegraphics[width=3in]{figures/fig2new.eps}
-
-		\caption{A box plot showing the amplitudes at each peak; peak \#23 is always the highest amplitude because it is the primary emission angle of all LWAs, periodic and not, at 200 GHz.
-A wide array of values are evident.}
-	\end{subfigure}
-
-\end{figure}
-
-\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
-Figure 2b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
+\noindent 20,000 instances of COMSOL simulation data is generated as the data source for our deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
+A different network and set of training data is used to generate predictions for each sub-slot scheme.
+Figure 3b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
 The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
@@
 
-\begin{figure}[b]
+\begin{figure}[H]
 	\centering
@@
 
-\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this idea as our loss function, we would need to compute the far-field signal for each slot we generate as we train the model, which would be extraordinary (and unfeasibly) computationally expensive.
+\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this idea as our loss function, we would need to compute the far-field signal for each slot we generate as we train the model, which would be extraordinarily (and unfeasibly) computationally expensive.
 Thus, instead, we turn to the idea of making the generated slot look as similar to the given training slot for a given peak profile as possible.
-Given that this is essentially a binary classification problem for each sub-slot, we use three weighted binary cross-entropy (BCE) loss functions, which are summed together to form our overall loss function with the following weightings:
-\begin{enumerate}
-  \item BCE between the true and predicted slot (2x)
-  \item BCE between the first derivative of the true and predicted slot using a Prewitt filter (1x)
-  \item BCE between the second derivative of the true and predicted slot using a Laplacian filter (1x)
-\end{enumerate}
+Given that this is a binary classification problem for each sub-slot, we use binary cross-entropy (BCE) loss.
+\\
+
+\noindent We also compare the predictions generated by numerical and machine learning techniques to experimental data.
+We produce simple hot-stamped leaky-wave antennas \cite{Guerboukha:21} and use a Picometrix terahertz time-domain spectroscopy to measure the experimental far-field response, scanning both the forward and backwards scattering directions.
 
 \section*{Results and Discussion}
-\subsection*{Binary Predictions}
+\subsection*{Binary Sub-Slot Scheme}
 For some given peak geometry, the model returns each individual sub-slot's probability of being transparent (i.e.
@@
 making the 16 slots with the highest probabilities transparent and vice versa).
-Both of these predicted slots share many similarities with the true slot but there are also some differences -- the testing accuracy was about 68\% averaged over all of the training samples.
+Both of these predicted slots share many similarities with the true slot but there are also some differences -- the testing accuracy was about 70.9\% averaged over all of the training samples.
+
+\noindent However, what determines the usefulness of our model is not the similarity of the slot but the similarity of the signal it generates to the objective.
+In order to consider the accuracy and usefulness of our model, we extract the predicted slot geometries, choose the top 16 slots based on the probabilities, and pass 500 of these new generated slots into our COMSOL model in order to compare the signal from the ML-generated slot to the originally desired peak profile.
+We then compare the peak profiles to the objective signal and calculate using the mean square error (MSE), as shown in the left panel of Figure 4 below; the shape of the distribution matches that of similar work \cite{Nadell:19} and is significantly better than the control, indicating significant predictive value.
+The right panel of Figure 4 shows the wide range of far-field magnitudes at different peaks.
+
+\begin{figure}[H]
+	\includegraphics[width=6.5in]{figures/fig6a.eps}
+		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
+\end{figure}
+
+\noindent We can also plot the objective and ML-predicted waveforms along with the slots that generated them numerically for a couple of cases as in Figure 5 below.
 
@@
 	\centering
-	\subfloat{{\includegraphics[height=2in]{figures/fig3_labeled.eps}}}
-	\subfloat{{\includegraphics[height=2in]{figures/fig3b_labeled.eps}}}
+	\subfloat{{\includegraphics[height=2.1in]{figures/fig7_left_477.eps}}}
+	\subfloat{{\includegraphics[height=2.1in]{figures/fig7_right_108.eps}}}
 	\caption{Model predictions for two different peak profiles.
-The left-most slot design is the randomly generated slot used to generate this profile, the center plot shows the sigmoid probabilities of a transparent sub-slot, and the right-most plot shows the top 16 sub-slots from the probabilities.}
+The left-most slot design is the randomly generated slot used to generate this profile, the center plot shows the sigmoid probabilities of a transparent sub-slot, and the right-most plot shows the top 16 sub-slots from the probabilities.
+The MSEs of the left and right predictions are 0.0155 and 0.0250, respectively.}
 \end{figure}
 
-\noindent However, what determines the usefulness of our model is not the similarity of the slot but the similarity of the signal it generates to the objective.
-In order to consider the accuracy and usefulness of our model, we extract the predicted slot geometries, choose the top 16 slots based on the probabilities, and pass 500 of these new generated slots into our COMSOL model in order to compare the signal from the ML-generated slot to the originally desired peak profile.
-We then compare the peak profiles to the objective signal and calculate using the mean square error (MSE), as shown in the top left panel of Figure 5 below; the shape of the distribution matches that of similar work \cite{Nadell:19}.
-In the other panels of Figure 2, we plot the objective peak profile in black against the peak profile of an ML-generated slot, where the color corresponds to the four colored buckets depicted in the histogram.
-Overall, the agreement is quite excellent, particularly for the first two buckets (green and light blue), which compose about 60\% of testing samples with trends and relative amplitudes of the peaks agreeing very well.
-Even in the lower-tiered buckets, like in the bottom right panel of Figure 2, many of the peak profile trends are well matched -- however, there are some areas where the model does not perform as well, resulting in a higher MSE.
-Overall, though, the agreement is excellent and shows that the model can be used to design an acceptable slot for many potentially desired peak profiles.
+\noindent Overall, these examples showcase the ability of the model to produce reasonable slots that approximate the desired far-field signal.
+These two cases showcase the best performance of the model, but even with substantially higher values of mean-square error, the overall peak behavior is often well-preserved, albeit with less exact results and more missed peaks.
+\\
+
+\noindent We also wish to examine if our numerical predictions are present experimentally.
+First, using a terahertz time-domain spectroscopy (TDS), we measure and plot angle versus frequency for two different slots, one with a uniform periodic slot and one with our unique periodically-modulated slots as in Figure 6 below.
 
@@
 	\centering
-	\includegraphics{figures/fig2_labeled.eps}
-	\caption{Results from COMSOL simulations of ML-generated slots. The top left panel shows an MSE histogram while the others compare the ML-slot generated peak profile to the objective.}
+	\includegraphics{figures/exp-fig1.eps}
+	\caption{Experimental time-domain spectroscopy (TDS) measurements for two different slot designs, the left with only one periodicity and the right with a linear combination of periodicities.}
 \end{figure}
+
+\noindent Generally speaking, we observe what we expect from Floquet theory.
+For the simple periodic slot, we see the main, non-periodic mode in addition to the one fast-wave Floquet mode.
+However, at right, we see many Floquet modes at play due to the periodicially-modulated nature of the slot; these two plots pose a sharp contrast to one another and show how our method is capable of producing a multitude of possible slot designs.
+From the TDS data, we can extract the far-field signal at 200 GHz and plot against the simulation data (note this is different data than Figure 5).
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=7in]{figures/fig8.eps}
+	\caption{Polar plots of experimental versus simulation data for both the objective and predicted slot; overall, the plots indicate excellent agreement, particularly at the peaks of highest magnitude.}
+\end{figure}
+
+\noindent We draw two primary conclusions from Figure 7, which are generated from the model's predictions for low values of MSE.
+First, the slot predicted by the model predicts a far-field signal quite similar to the objective function.
+Secondly, the experimental data generally agrees with the simulation data, particularly near the largest peaks, there are certainly differences between the numerical and experimental values.
+One possible cause is due to the relatively simple setup we are using to measure experimental data and the resulting geometrical difficulties of picking up back-scattering.
+However, the experimental measurements certainly serve as a proof of concept for further exploration.
+
+\subsection*{Grey Sub-Slot Scheme}
+
+\noindent This second scheme significantly expands the scope of the problem because each sub-slot can take one of five values instead of just two: fully metallic, 25\% transparent, 50\% transparent, 75\% transparent, and 100\% transparent.
+We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer.
+This significantly increases the number of degrees of freedom within the model, as we see in the right panel of Figure 8 below; the range of values at each peak is broader than is seen than in Figure 4.
+
+\begin{figure}[H]
+	\includegraphics[width=6.5in]{figures/histboxgrey.eps}
+		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
+\end{figure}
+
+\noindent The left panel of Figure 8 shows the mean square error histogram for the 500 sets of testing data for which we numerically solved for the predicted slot's far-field pattern in order to compare its similarity to the objective.
+While the model performs similarly to the binary case (except for a slightly longer tail here), the control MSE histogram broadens and moves to the right.
+This means that our model performs better relative to the control with the greyscale scheme compared to the binary scheme, which is not unexpected given the increased degrees of freedom at play and the strength of neural network models at uncovering complex non-linear relationships.
+\\
+
+\noindent Like before in Figure 5, we can plot some of the model-generated slots and the resulting far-field patterns in order to get an idea of what sort of slots the model is producing, which we plot in Figure 9 below.
+Overall, we see close agreement between the objective and ML-predicted slots, particularly at the largest peaks and the overall profile of the wave.
+
+\begin{figure}[H]
+	\centering
+	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
+	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
+	\caption{Model predictions for two different peak profiles using the greyscale scheme.
+The left slot design is the randomly generated greyscale slot used to generate the objective, the center plot shows the ideal transparency of each sub-slot, and the right plot shows those rounded into the buckets used in the simulation.
+The MSEs of the left and right predictions are 0.0127 and 0.0113.}
+\end{figure}
+
+\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data.
+However, this is slightly more complicated experimental method -- we need to actually experimentally generate semi-transparent slots.
+We do this by using the aforementioned hot-stamping technique but instead of using black ink for metallic slots and the absence of ink for transparent slots, we calibrate our TDS system using ``grey'' slots, the idea being that changing the ink color within the greyscale spectrum will directly correlate with the amount of metal deposited on the surface of the antenna.
+We first calibrate shades of grey with transmission values, then using the shades of grey that conform to 25\%, 50\%, and 75\% transparency, we produce our LWAs using the exact same methodology as in the binary case.
 

### 2022-05-24 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -5,7 +5,7 @@ import numpy as np
 sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power')
 import pickle
 import tensorflow as tf
-
+plt.hist()
 mpl.rcParams['font.family'] = 'Arial'
 plt.rcParams['font.size'] = 12
 plt.rcParams['axes.linewidth'] = 2
@@ -44,6 +44,8 @@ with open('1d/peaks_to_slot/constant_power/results/test_data510.pkl','rb') as fi
     test_data = pickle.load(file)
     peaks, true, pred, waves = test_data
 
+true
+top_16(pred)
 # val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation_old')
 
 val510_slots, val510_peaks, val510_waves = import_val_data('1d/peaks_to_slot/constant_power/results/validation510')
@@ -59,11 +61,11 @@ plt.plot(peaks[9])
 plt.plot(val59_peaks[9])
 plt.legend(['Reference','Binary','Conv'])
 
-# correct / (len(val_slots) * 36)
-# correct = 0
-# for i in np.arange(len(val_slots)):
-#     correct += (val_slots[i] == true[i]).sum()
-# val_slots
+correct / (len(val510_slots) * 36)
+correct = 0
+for i in np.arange(len(val510_slots)):
+    correct += (val510_slots[i] == true[i]).sum()
+
 
 mse_list_binary = []
 # mse_list_grey = []
@@ -94,31 +96,36 @@ for i in np.arange(500):
     else:
         bucket_4.append(i)
 
-old_bins = np.array([0.00086428, 0.00873865, 0.01661302, 0.02448739, 0.03236176,
-       0.04023613, 0.0481105 , 0.05598487, 0.06385924, 0.07173361,
-       0.07960798, 0.08748235, 0.09535672, 0.10323109, 0.11110546,
-       0.11897984, 0.12685421, 0.13472858, 0.14260295, 0.15047732,
-       0.15835169])
+# old_bins = np.array([0.00086428, 0.00873865, 0.01661302, 0.02448739, 0.03236176,
[…]

### 2022-05-24 1d/peaks_to_slot/grey/another_analysis.py

@@ -5,6 +5,7 @@ import numpy as np
 sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/grey')
 import pickle
 import tensorflow as tf
+from tensorflow import losses
 
 mpl.rcParams['font.family'] = 'Arial'
 plt.rcParams['font.size'] = 12
@@ -31,15 +32,20 @@ cmap = mpl.cm.get_cmap('GnBu')
 for index, patch in enumerate(boxplot['boxes']):
     patch.set_facecolor(cmap(index / 36))
 
-plt.savefig('paper/figures/fig2new.eps')
+plt.savefig('paper/figures/boxgrey.eps')
 
 ###
-
-with open('1d/peaks_to_slot/grey/results/simpleloss/test_data.pkl','rb') as file:
+with open('1d/peaks_to_slot/grey/results/test_data_simp.pkl','rb') as file:
     test_data = pickle.load(file)
-    peaks, true, pred = test_data
+    peaks, true, pred, waves = test_data
 
-grey_slots, grey_peaks = import_val_data('1d/peaks_to_slot/grey/results/simpleloss/simplelosstest')
+    predb = np.where((pred > 0) & (pred <= 0.125), 0, pred)
+    predb = np.where((predb > 0.125) & (predb <= 0.375), 0.25, predb)
+    predb = np.where((predb > 0.375) & (predb <= 0.625), 0.50, predb)
+    predb = np.where((predb > 0.625) & (predb <= 0.875), 0.75, predb)
+    predb = np.where((predb > 0.875), 1.00, predb)
+
+grey_slots, grey_peaks, grey_wves = import_val_data('1d/peaks_to_slot/grey/results/simplelosstest')
 
 grey_slots
 
@@ -71,9 +77,9 @@ test(23)
 
 bucket_2
 
-np.array(mse_list_grey).mean()
-np.array(mse_list_diff).mean()
-np.array(mse_list_control).mean()
+# np.array(mse_list_grey).mean()
+# # np.array(mse_list_diff).mean()
+# np.array(mse_list_control).mean()
 mse_list_grey = []
 mse_list_diff = []
 mse_list_control = []
[…]

### 2022-05-24 experiments/Polar_dB/Polar_dB/Polar_dB.m

@@ -1,0 +1,60 @@
+function []=Polar_dB(theta,data,range,Ntick,Line,option)
+%   function [] = Polar_dB(theta,data,range,Ntick,Line,option)
+%   Polar_dB plots the data in dB 'data' vs 'theta' is polar fashion. 
+%
+%  	theta 	: in radian
+%   data   	: in dB
+%   range   : e.g. [ min max ], default [-40 0] 
+%   Ntick   : No. of radial ticks, default 5
+% 	Line    : Line properties e.g. '--b', defaul 'k'
+% 	option  : 1) Full circle 2) Half circle display, defaul 1 
+%%
+switch nargin
+    case 2
+        range 			=	[-40 round(max(data))]; % default
+        Ntick 			= 	5;
+		Line 			= 	'k';
+		option 			= 	1;
+	case 3
+        Ntick 			= 	5;
+		Line 			= 	'k';
+		option 			= 	1;
+	case 4
+		Line 			= 	'k';
+		option 			= 	1;
+    case 5
+		option 			= 	1;
+end
+data(isnan(data))       =   min(range);
+data(data < min(range))	=   min(range);
+polarplot(theta,data,Line,'LineWidth',1)
+rlim(range)
+%% 
+if option == 1
+thetaticks(0:15:345)
+thetaticklabels({'0^\circ',' ','30^\circ',' ','60^\circ',' ','90^\circ',' ','120^\circ',' ','150^\circ',' ','180^\circ',' ','-150^\circ',' ','-120^\circ',' ','-90^\circ',' ','-60^\circ',' ','-30^\circ'})
+end
+%% 
+if option == 2
+thetalim([0 180])
+thetaticks(0:15:180)
+thetaticklabels({'-90^\circ',' ','-60^\circ',' ','-30^\circ',' ','0^\circ',' ','30^\circ',' ','60^\circ',' ','90^\circ'})
+end
+%%
+range_                  =   linspace(min(range),max(range),Ntick); 
+rticks(range_)
+Labels                  =   cell(1,Ntick);
+for i=1:Ntick
+    if i==Ntick
+        Labels{1,i}  	=   strcat(num2str(round(range_(i),2)),' dB');
+    else
+        Labels{1,i}    	=   num2str(round(range_(i),2));
+    end
+end
+rticklabels(Labels)
+%%
+pax = gca;
+pax.RAxisLocation   =   0;
+pax.ThetaDir = 'counterclockwise';
+pax.ThetaZeroLocation = 'right';
+end

### 2022-05-24 experiments/Polar_dB/Polar_dB/test.m

@@ -1,0 +1,20 @@
+close all; clear; clc;
+Ns          =   6e2;
+theta2      =   linspace(-pi,pi,Ns);
+data2     	=   6*cos(theta2).*cos(3*theta2).*cos(4*theta2);
+data2       =   10*log10(abs(data2));
+figure
+Polar_dB(theta2,data2,[-40 10],5,'k',1)
+title('Polar plot in dB','FontName','times new roman')
+theta1      =   linspace(-pi,0,Ns);
+data1       =   2*cos(theta1).*cos(4*theta1).*cos(10*theta1);
+data1     	=   10*log10(abs(data1));
+theta2      =   linspace(0,pi,Ns);
+data2     	=   6*cos(theta2).*cos(3*theta2).*cos(4*theta2);
+data2       =   10*log10(abs(data2));
+figure
+Polar_dB(theta1,data1,[-40 8],5,'b',2)
+hold on
+Polar_dB(theta2,data2,[-40 8],5,'-.r',2)
+hold off
+title('Polar plot in dB','FontName','times new roman')

### 2022-05-24 experiments/a241.m

@@ -52,26 +52,48 @@ period = 0.95e-3;
 objective241 = readmatrix('objective241.csv');
 expected241 = readmatrix('expected241.csv');
 
-figure
-% semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
-hold on
-% semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
-% semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
-
-plot(7:151,mag2db(abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7)))))
-plot(mag2db(objective241(1:151,2) / max(objective241(1:151,2))))
-plot(mag2db(expected241(1:151,2) / max(expected241(7:151,2))))
-
-legend('Experimental','Objective','Expected')
-
-% floquet = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90,95,99,101,103,106,109,114,117,120,122,126,128,130,132,146];
+% figure
+% % semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
+% hold on
+% % semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
+% % semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
 % 
-% for i=1:length(floquet)
-%     xline(floquet(i))
-% end
+% plot(7:151,mag2db(abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7)))))
+% plot(mag2db(objective241(1:151,2) / max(objective241(1:151,2))))
+% plot(mag2db(expected241(1:151,2) / max(expected241(7:151,2))))
+% 
+% legend('Experimental','Objective','Expected')
+% 
+% % floquet = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90,95,99,101,103,106,109,114,117,120,122,126,128,130,132,146];
+% % 
+% % for i=1:length(floquet)
+% %     xline(floquet(i))
+% % end
+% figure
 
+
+% 
+% Polar_dB(deg2rad(7:151),mag2db(abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7)))),[-40 0], 5,'k',2)
+% hold on
[…]

### 2022-05-24 experiments/a241new.m

@@ -1,0 +1,99 @@
+% clear all
+% clc
+% close all
+
+Files=dir('binarywaveguide241new');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide241new/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide241new/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+colormap(flipud(brewermap([],'GnBu')))
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+
+theta_pm_back = linspace(0,150,1400)
+nu_vector=(150:0.1:280);
[…]

### 2022-05-24 experiments/a477.m

@@ -1,0 +1,99 @@
+clear all
+clc
+close all
+
+Files=dir('binarywaveguide477');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide477/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+colormap(flipud(brewermap([],'GnBu')))
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+% 
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
[…]

### 2022-05-24 experiments/a477may24.m

@@ -1,0 +1,165 @@
+ clear all
+clc
+close all
+
+Files=dir('binarywaveguide477-remadeplastic/');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide477-remadeplastic/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-remadeplastic/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
+% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+% plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
+
+objective241 = readmatrix('objective477.csv');
+expected241 = readmatrix('expected477.csv');
+
+% figure
+% % semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
+% hold on
+% % semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
+% % semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
+% 
+% plot(7:151,mag2db(abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7)))))
[…]

### 2022-05-24 experiments/a477new.m

@@ -1,0 +1,124 @@
+clear all
+clc
+close all
+
+Files=dir('binarywaveguide477-cutback');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide477-cutback/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-cutback/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+colormap(flipud(brewermap([],'GnBu')))
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+% 
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
[…]

### 2022-05-24 experiments/a477re.m

@@ -1,0 +1,124 @@
+ clear all
+clc
+close all
+
+Files=dir('binarywaveguide477-realigned');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide477-realigned/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-realigned/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+colormap(flipud(brewermap([],'GnBu')))
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+% 
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
[…]

### 2022-05-24 experiments/a477may24_fixedplastic.m
this end

@@ -2,15 +2,9 @@
 clc
 close all
 
-<<<<<<< Updated upstream
-Files=dir('binarywaveguide477/');
-N = length(Files);
-[t,w]=textread(strcat('binarywaveguide477/',Files(3).name),'%f%f','headerlines',6);  % read first for size
-=======
 Files=dir('binarywaveguide477-furtherplastic/');
 N = length(Files);
 [t,w]=textread(strcat('binarywaveguide477-furtherplastic/',Files(3).name),'%f%f','headerlines',6);  % read first for size
->>>>>>> Stashed changes
 T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
 T(:,1)=t;
 W(:,1)=w;
@@ -24,11 +18,7 @@ f(:,1) = linspace(-fmax,fmax,size(W,1));
 for k = 3:N
     name = Files(k).name;
     x = split(name,'.');
-<<<<<<< Updated upstream
-    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477/',name),'%f%f','headerlines',6);
-=======
     [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-furtherplastic/',name),'%f%f','headerlines',6);
->>>>>>> Stashed changes
     
     B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
     t = T(:,str2double(x(1)) + 1);
@@ -41,9 +31,8 @@ end
 % nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
 % plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
 
-base = readmatrix('expected477_base.csv');
-pec_back = readmatrix('expected477_PEC_back.csv');
-pec_some = readmatrix('expected477_PEC_test.csv');
+objective241 = readmatrix('objective477.csv');
[…]

### 2022-06-15 1d/peaks_to_slot/constant_power/another_analysis.py
pre trip updates

@@ -9,6 +9,9 @@ plt.hist()
 mpl.rcParams['font.family'] = 'Arial'
 plt.rcParams['font.size'] = 12
 plt.rcParams['axes.linewidth'] = 2
+from tensorflow import losses
+
+tensorflow.losses.mse([1],[3])
 
 from preprocess import import_data, import_val_data
 
@@ -19,7 +22,7 @@ floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  
 
 ###
 
-slots, peaks = import_data()
+slots, peaks, _ = import_data()
 
 peaks.shape
 # selected_peaks = peaks[peaks[:,1] <0 ]
@@ -30,13 +33,14 @@ boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
 plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
 plt.xlabel('Peak Count')
 plt.ylabel('Amplitude (normalized)')
+plt.ylim([-0.4,1])
 
 cmap = mpl.cm.get_cmap('GnBu')
 
 for index, patch in enumerate(boxplot['boxes']):
     patch.set_facecolor(cmap(index / 36))
 
-plt.savefig('paper/figures/fig2new.eps')
+plt.savefig('paper/figures/boxbinary.eps')
 
 ###
 
@@ -75,14 +79,15 @@ bucket_2 = []
 bucket_3 = []
 bucket_4 = []
 for i in np.arange(500):
-    mse_b = ((peaks[i] - val510_peaks[i]) ** 2).mean()
+    # mse_b = ((peaks[i] - val510_peaks[i]) ** 2).mean()
+    mse_b = losses.mse(waves[i][0:181], val510_waves[i][0:181])
     mse_list_binary.append(mse_b)
 
     # mse_g = ((peaks[i] - grey_peaks[i]) ** 2).mean()
     # mse_list_grey.append(mse_g)
 
     try:
-        mse_c = ((peaks[i] - val510_peaks[i+3]) ** 2).mean()
+        mse_c = losses.mse(waves[i+1][0:181], val510_waves[i][0:181])
         mse_list_control.append(mse_c)
     except:
         pass
@@ -101,10 +106,12 @@ for i in np.arange(500):
 #        0.07960798, 0.08748235, 0.09535672, 0.10323109, 0.11110546,
[…]

### 2022-06-15 1d/peaks_to_slot/grey/another_analysis.py

@@ -162,11 +162,14 @@ def plot_instance_beta(val):
     ax[3].plot(waves[val][0:181],color='#0c2c84')
     ax[3].plot(grey_wves[val][0:181],color='#7fcdbb')
 
-    print('MSE = ' + str(losses.mse(peaks[val], grey_peaks[val])),5)
-bucket_1
+    print('MSE = ' + str(losses.mse(waves[val][0:181], grey_wves[val][0:181])),5)
+bucket_4
 np.mean(np.square(peaks[127] - grey_peaks[127]))
 mse_list_grey[127]
-plot_instance_beta(71)
+plot_instance_beta(488)
+
+np.savetxt('experiments/expected488grey.csv',grey_wves[488])
+
 plt.savefig('paper/figures/grey71.eps')
 
 bucket_3

### 2022-06-15 1d/peaks_to_slot/grey/build_model.py

@@ -1,3 +1,6 @@
+import sys
+sys.path.append('/Users/joshuaneronha/.conda/envs/mittleman/bin/python')
+sys.path.append('1d/peaks_to_slot/grey')
 import numpy as np
 import tensorflow as tf
 from peaks_to_slots_model import LWAPredictionModel
@@ -97,7 +100,7 @@ def main():
     output = Model.call(peaks_test)
     saved_data = [peaks_test, slot_test, output, waves_test]
 
-    with open('1d/peaks_to_slot/grey/results/test_data.pkl', 'wb') as f:
+    with open('1d/peaks_to_slot/grey/results/test_data530.pkl', 'wb') as f:
         pickle.dump(saved_data, f)
 
     #
@@ -157,4 +160,46 @@ def main():
 
 
 if __name__ == '__main__':
-	main()
+	thismodel = main()
+thismodel
+
+exp_test = 20*np.log10(np.loadtxt('experiments/greytestforml.csv',delimiter=','))
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
+filtered = tf.reshape(exp_testy[[x-2 for x in floquet]],(1,35))
+filtered = filtered / np.max(filtered)
+out = thismodel.call(filtered)
+
+
+plt.imshow(tf.transpose(out),cmap='YlGnBu')
+with open('1d/peaks_to_slot/grey/results/test_data530.pkl','rb') as f:
+    output = pickle.load(f)
+output[0][0]
+plt.imshow(tf.expand_dims(output[2][400],1))
+
+test_array = np.array([0.44546966, 0.48853195, 0.59419797, 0.73774793, 0.81137194,
+       0.83679913, 1.        , 0.62820602, 0.53438953, 0.57906827,
+       0.59198008, 0.59870489, 0.56357657, 0.36732016, 0.62812462,
+       0.76372193, 0.61344691, 0.5473943 , 0.70663523, 0.71242345,
+       0.71085666, 0.31885805, 0.38955326, 0.5811831 , 0.57733111,
+       0.42004987, 0.54043865, 0.34543648, 0.42882175, 0.48020032,
[…]

### 2022-06-15 experiments/threegreytesting.m

@@ -1,0 +1,171 @@
+clear all
+clc
+close all
+
+Files=dir('3grey');
+N = length(Files);
+[t,w]=textread(strcat('3grey/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('3grey/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
+% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+% plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
+
+% objective241 = readmatrix('objective477.csv');
+expected241 = readmatrix('3greytest.csv');
+% expected241cont = readmatrix('width-modulation-control.csv');
+% random = readmatrix('expected432grey.csv');
+
+% figure
+% % semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
+% hold on
+% % semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
+% % semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
+% 
[…]

### 2022-06-15 experiments/untitled11.m

@@ -1,0 +1,171 @@
+clear all
+clc
+close all
+
+Files=dir('3grey');
+N = length(Files);
+[t,w]=textread(strcat('3grey/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('3grey/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+% theta_pm_back = linspace(0,150,1400)
+% nu_vector=(150:0.1:280);
+% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
+% plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
+
+% objective241 = readmatrix('objective477.csv');
+expected241 = readmatrix('3greytest.csv');
+% expected241cont = readmatrix('width-modulation-control.csv');
+% random = readmatrix('expected432grey.csv');
+
+% figure
+% % semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
+% hold on
+% % semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
+% % semilogy(expected241(1:151,2) / max(expected241(7:151,2)))
+% 
[…]

### 2022-06-15 paper/paper.tex
pre trip updates
final changes pre vacation

@@
 		\centering
-		\includegraphics[width = 6in]{figures/fig5.eps}
+		\includegraphics[width = 6in]{figures/fig5pdf}
 		\caption{The leaky wave antenna geometry.
@@
 	\centering
-	\includegraphics[width=6in]{figures/fig4_labeled2.eps}
+	\includegraphics[width=6in]{figures/fig4_labeled2pdf}
 	\caption{The left panel shows the possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering (< 90$\deg$) and the negative modes in back-scattering.
@@
 	\centering
-	\includegraphics[width=6in]{figures/fig1.eps}
+	\includegraphics[width=6in]{figures/fig1pdf}
 	\caption{Neural network architecture schematic; peaks are used as the input data and passed through six hidden layers to predict the ideal slot design that will yield the closest possible signal.}
@@
 \begin{figure}[H]
-	\includegraphics[width=6.5in]{figures/fig6a.eps}
+	\includegraphics[width=6.5in]{figures/fig6apdf}
 		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
@@
 	\centering
-	\subfloat{{\includegraphics[height=2.1in]{figures/fig7_left_477.eps}}}
-	\subfloat{{\includegraphics[height=2.1in]{figures/fig7_right_108.eps}}}
+	\includegraphics[height=2.1in]{figures/fig7pdf}
 	\caption{Model predictions for two different peak profiles.
@@
 	\centering
-	\includegraphics{figures/exp-fig1.eps}
+	\includegraphics{figures/exp-fig1pdf}
 	\caption{Experimental time-domain spectroscopy (TDS) measurements for two different slot designs, the left with only one periodicity and the right with a linear combination of periodicities.}
@@
 	\centering
-	\includegraphics[width=7in]{figures/fig8.eps}
+	\includegraphics[height=2in]{figures/477exppdf}
 	\caption{Polar plots of experimental versus simulation data for both the objective and predicted slot; overall, the plots indicate excellent agreement, particularly at the peaks of highest magnitude.}
@@
 \begin{figure}[H]
-	\includegraphics[width=6.5in]{figures/histboxgrey.eps}
+	\includegraphics[width=6.5in]{figures/histboxgreypdf}
 		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
@@
 
-\begin{figure}[H]
-	\centering
-	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
-	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
-	\caption{Model predictions for two different peak profiles using the greyscale scheme.
+%\begin{figure}[H]
+%	\centering
+%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
+%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
+%	\caption{Model predictions for two different peak profiles using the greyscale scheme.
 The left slot design is the randomly generated greyscale slot used to generate the objective, the center plot shows the ideal transparency of each sub-slot, and the right plot shows those rounded into the buckets used in the simulation.
 The MSEs of the left and right predictions are 0.0127 and 0.0113.}
-\end{figure}
+%\end{figure}
 

### 2022-06-15 paper/papertest/papertest.tex
final changes pre vacation

--- 2022-05-07 paper/paper.tex
@@
 		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
+		\includegraphics[height=1.5in]{figures/fig5pdf}
 		\caption{The leaky wave antenna geometry.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; in order to maintain constant power, the number of each type of slot is kept equal.}
+The left panel shows the binary case, where dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries.
+In the right panel, the boundary conditions are no longer discretized and can take on some intermediate value of transparency, as seen by the sub-slots with colors between light and dark.}
 \end{figure}
-
-\noindent see, I can keep typing things.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=6in]{figures/fig4_labeled2.eps}
-	\caption{The left panel shows the possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering (< 90$\deg$) and the negative modes in back-scattering.
-The right panel shows these predicted Floquet modes overlaid on a sample peak profile generated in COMSOL.}
-\end{figure}
-
-\noindent To generate our training data, we build a model of a leaky-wave antenna in COMSOL Multiphysics with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length.
-18 sub-slots (exactly half) of the slots are randomly chosen as to be transparent (i.e.
-a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation.
-We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its API.
-Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs; using only a few tens of thousands sets of training data, we can predict an optimal slot design for an arbitrary peak profile.
-The simulation geometry is shown in Figure 2a below \\
-
-\begin{figure}[H]
-	\caption{Simulation geometry (left) and possible peak profiles (right)}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
-		\caption{The leaky wave antenna geometry used to generate training data.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; both are randomly generated so that the slots are half and half.}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.55\textwidth}
-		\centering
-		\includegraphics[width=3in]{figures/fig2new.eps}
-
-		\caption{A box plot showing the amplitudes at each peak; peak \#23 is always the highest amplitude because it is the primary emission angle of all LWAs, periodic and not, at 200 GHz.
-A wide array of values are evident.}
-	\end{subfigure}
-
-\end{figure}
-
-\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
-Figure 2b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
-The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
-The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
-The model architecture is visualized in Figure 3.
-\\
-
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=6in]{figures/fig1.eps}
-	\caption{Neural network architecture schematic; peaks are used as the input data and passed through six hidden layers to predict the ideal slot design that will yield the closest possible signal.}
-\end{figure}
-
-\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this idea as our loss function, we would need to compute the far-field signal for each slot we generate as we train the model, which would be extraordinary (and unfeasibly) computationally expensive.
-Thus, instead, we turn to the idea of making the generated slot look as similar to the given training slot for a given peak profile as possible.
-Given that this is essentially a binary classification problem for each sub-slot, we use three weighted binary cross-entropy (BCE) loss functions, which are summed together to form our overall loss function with the following weightings:
-\begin{enumerate}
-  \item BCE between the true and predicted slot (2x)
-  \item BCE between the first derivative of the true and predicted slot using a Prewitt filter (1x)
-  \item BCE between the second derivative of the true and predicted slot using a Laplacian filter (1x)
-\end{enumerate}
-
-\section*{Results and Discussion}
-\subsection*{Binary Predictions}
-For some given peak geometry, the model returns each individual sub-slot's probability of being transparent (i.e.
-a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function.
-In Figure 4 below, for two sample peak profiles, the true slots (left), predicted slot (center) and rounded ML slot (right, i.e.
-making the 16 slots with the highest probabilities transparent and vice versa).
-Both of these predicted slots share many similarities with the true slot but there are also some differences -- the testing accuracy was about 68\% averaged over all of the training samples.
-
-\begin{figure}[H]
-	\centering
-	\subfloat{{\includegraphics[height=2in]{figures/fig3_labeled.eps}}}
-	\subfloat{{\includegraphics[height=2in]{figures/fig3b_labeled.eps}}}
-	\caption{Model predictions for two different peak profiles.
-The left-most slot design is the randomly generated slot used to generate this profile, the center plot shows the sigmoid probabilities of a transparent sub-slot, and the right-most plot shows the top 16 sub-slots from the probabilities.}
-\end{figure}
-
-\noindent However, what determines the usefulness of our model is not the similarity of the slot but the similarity of the signal it generates to the objective.
-In order to consider the accuracy and usefulness of our model, we extract the predicted slot geometries, choose the top 16 slots based on the probabilities, and pass 500 of these new generated slots into our COMSOL model in order to compare the signal from the ML-generated slot to the originally desired peak profile.
-We then compare the peak profiles to the objective signal and calculate using the mean square error (MSE), as shown in the top left panel of Figure 5 below; the shape of the distribution matches that of similar work \cite{Nadell:19}.
-In the other panels of Figure 2, we plot the objective peak profile in black against the peak profile of an ML-generated slot, where the color corresponds to the four colored buckets depicted in the histogram.
-Overall, the agreement is quite excellent, particularly for the first two buckets (green and light blue), which compose about 60\% of testing samples with trends and relative amplitudes of the peaks agreeing very well.
-Even in the lower-tiered buckets, like in the bottom right panel of Figure 2, many of the peak profile trends are well matched -- however, there are some areas where the model does not perform as well, resulting in a higher MSE.
-Overall, though, the agreement is excellent and shows that the model can be used to design an acceptable slot for many potentially desired peak profiles.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics{figures/fig2_labeled.eps}
-	\caption{Results from COMSOL simulations of ML-generated slots. The top left panel shows an MSE histogram while the others compare the ML-slot generated peak profile to the objective.}
-\end{figure}
-
-\section*{Conclusion}
 

### 2022-06-27 paper/paper.tex

--- 2022-05-07 paper/paper.tex
@@
 \usepackage{hyperref}
-\bibliographystyle{ieeetr}
 \usepackage{amsmath} 
@@
 \usepackage{subcaption}
-\bibliographystyle{ieeetr}
+\bibliographystyle{naturemag}
 
@@
 
-\title{Deep Learning Methods for Optimizing Terahertz Leaky Wave Antenna Design}
-\author{J. Neronha, H. Guerboukha, and D. Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
+%\title{Optimization of Terahertz Leaky Wave Antennas Using Neural Network Modeled Periodically Modulated Slots}
+\title{Deep Learning Predictions of Antenna Geometry for Desired Far-Field Signals in Terahertz Leaky Wave Antennas}
+\author{Joshua Neronha, Hichem Guerboukha, and Daniel Mittleman \\ \\ \small School of Engineering, Brown University, Providence, RI 02912}
 \date{}
@@
 Thus, we find that any slot composed of an array of these sub-slots forms a linear superpositioning of periodic modes that can be used to generate highly specific peak profiles.
+We use the hot-stamping technique to rapidly prototype and test antennas in the field and view the predictive model as a natural counterpart to rapid prototyping methods.
 
-\section*{Methodology}
+\section*{Methods}
 
-We train a model to predict the slot geometry of the LWA for a desired far-field pattern.
-We consider a LWA based on a parallel plate waveguide, the fundamental transverse electric (TE$_1$) mode, and a frequency of 200 GHz.
-Instead of a uniform 1D slot \cite{doi:10.1063/5.0033126}, we discretize the slot into 36 0.5-mm sub-slots that can be transparent, metallic, or somewhere in between (i.e.
-semi-transparent).
+There are two components to the methodology of this investigation: the computational methods used to construct the model, and the experimental methods applied to confirm the model's validity.
+
+\subsection*{Computational Methods}
+
+We consider a LWA based on a parallel plate waveguide with plate separation of 1 mm, the fundamental transverse electric (TE$_1$) mode, and a frequency of 200 GHz.
+Instead of a uniform 1D slot \cite{doi:10.1063/5.0033126}, we discretize the slot into 36 0.5-mm sub-slots which can be modulated in their transparency.
 This approach is similar to the approach taken in past explorations of metasurface design \cite{Liu:2022tg, Jafar-Zanjani:2018vy}.
@@
 
-\[\beta=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1} \label{eq:special}\]
+\[\beta_p=\sqrt{k_0^2 - (\frac{\pi}{h})^2} +\frac{2\pi p}{\Lambda} \tag{1}\]
 
-\noindent where $k_0$ is the wave number, $h$ is the height of the waveguide, and $\Lambda$ is the slot periodicity.
-These different modes peak at different angles defined by $\cos(\theta)=\beta_p/k_0$, given that the excited modes can be consider fast-wave (i.e., $|\beta_p|>k_0$).
-Our primary objective is to generate multiple beams with specific magnitudes at specific locations.
-Therefore, instead of a periodic geometry, we consider a non-periodic array of slots.
+\noindent where $k_0$ is the free space wave number, $h$ is the plate separation, and $\Lambda$ is the slot periodicity.
+Each different mode peaks at some given angle $\theta$ defined by $\theta=\cos^{-1}(\beta_p/k_0)$, given that the excited modes can be consider fast-wave (i.e.
+$|\beta_p|>k_0$ ).
+Our primary objective is to generate multiple beams with specific magnitudes at specific locations, which we demonstrate in Figure 2a using numerical simulations of four periodic waveguides with different periodicities.
+Each different period has peaks at different angles.
+Therefore, instead of a periodic geometry, we consider a non-uniformly periodic array of slots in order to exploit multiple periodicities and thus excite multiple modes, producing peaks at multiple angles.
 By Fourier decomposition, we note that any non-periodic slot design can be viewed as a linear combination of periodic designs $\beta_p$, each peaking at an angle $\cos(\theta)=\beta_p/k_0$.
 The strength (amplitude) of individual peaks can be related to the Fourier coefficients of this decomposition.
-\\
+Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$.
+Indeed, due to the discretization, the possible $\Lambda$ for a total slot length $\ell$ and sub-slot length $\xi$ given by:
 
-\noindent Our discretized geometry imposes limits on the possible excited Floquet modes, by constraining the values of $\Lambda$.
-Indeed, due to the discretization, the possible $\Lambda$ are given by $\Lambda=$.
-Furthermore, due to the fast-wave requirement (i.e., $|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide.
-\\
+%this equation, honestly, I essentially came up with myself. I'm not sure if someone else has derived this equation, I couldn't find it anywhere. If you can't please give it a sanity check lol
 
- A schematic is shown in Figure 1 below. \\
+\[(\Lambda_k)^{\frac{\ell}{4\xi}}_{k=1}, \textrm{where } \Lambda_k=2k\xi \tag{2}\]
+
+\noindent Furthermore, due to the fast-wave requirement (i.e.
+$|\beta_p|>k_0$), only a few select modes will be able to leak out of the waveguide, meaning that for a given geometry only some of the  peaks will be present.
+A schematic of the proposed scheme, in which each sub-slot can either be transparent or metallic, is shown in Figure 1a.
+For a given geometry, we can calculate all of the possible Floquet peaks by calculating $\beta_p$ for each possible spatial mode for each possible periodicities in this geometry, ranging from $\Lambda$ = 1mm (i.e.
+1 transparent, then 1 metallic, etc.) to $\Lambda$ = 9mm (i.e.
+18 transparent slots and 18 metallic slots).
+We calculate the angles for only those modes that satisfy the fast-wave requirement for this geometry in order to find all possible Floquet peaks, which we plot in Figure 2b -- note that there are almost sixty possible peaks!
 
@@
 		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
-		\caption{The leaky wave antenna geometry.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; in order to maintain constant power, the number of each type of slot is kept equal.}
+		\includegraphics[width = 6in]{figures/fig5pdf}
+		\caption{Leaky wave antenna geometry.
+The antenna is a simple parallel-plate waveguide with non-uniformly periodic sub-slots.
+a) The binary case, where dark sub-slots represent transparency and light sub-slots represent opaqueness.
+b) The grey case, when in addition to transparent and metallic sub-slots, there are also partially transparent slots.}
 \end{figure}
-
-\noindent see, I can keep typing things.
 
@@
 	\centering
-	\includegraphics[width=6in]{figures/fig4_labeled2.eps}
-	\caption{The left panel shows the possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering (< 90$\deg$) and the negative modes in back-scattering.
-The right panel shows these predicted Floquet modes overlaid on a sample peak profile generated in COMSOL.}
+	\includegraphics[width=6in]{figures/theorypdf}
+	\caption{Floquet theory predictions for geometry.
+a) Numerical simulations for uniformly periodic LWAs with four different values of $\Lambda$; each peaks at different angles, indicating how we use superposition of modes to generate a wide array of possible angles.
+Note that all periods have a maximum around 48 degrees, which is the primary mode for a LWA of these dimensions.
+b) The possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering and the negative modes in back-scattering.
+}
 \end{figure}
 
-\noindent To generate our training data, we build a model of a leaky-wave antenna in COMSOL Multiphysics with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length.
-18 sub-slots (exactly half) of the slots are randomly chosen as to be transparent (i.e.
-a scattering boundary layer) whereas the balance remain metallic and thus do not leak radiation.
-We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling COMSOL via its API.
-Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs; using only a few tens of thousands sets of training data, we can predict an optimal slot design for an arbitrary peak profile.
-The simulation geometry is shown in Figure 2a below \\
+\noindent Figure 2 indicates that modulating the periodicity of the geometry we describe enables far-field peak formation at a wide variety of angles, indicating that is a useful regime in which to design a slot based on some desired far-field signal.
+Solving this inverse problem (i.e.
+calculating the slot for some given far-field profile), however, is difficult; deriving an analytical expression for a complicated regime is difficult if not impossible, and solving numerically would require iteration through multiple antenna designs until arriving at an optimal solution, essentially searching for one needle in a haystack of $2^{32}$ possible antenna geometries.
+This is where the idea of a neural network model enters -- deep learning methods are effective at describing nonlinear relationships of complex systems simply by providing training data from which the model can ``learn''.
+Thus, we build a model that predicts the slot geometry for some input of a desired far-field signal.
+\\
 
-\begin{figure}[H]
-	\caption{Simulation geometry (left) and possible peak profiles (right)}
-	\begin{subfigure}[b]{0.45\textwidth}
-		\centering
-		\includegraphics[width = 3.2in]{figures/fig5.eps}
-		\caption{The leaky wave antenna geometry used to generate training data.
-Dark-colored sub-slots represent transparent areas while light colors indicate metallic boundaries; both are randomly generated so that the slots are half and half.}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.55\textwidth}
-		\centering
-		\includegraphics[width=3in]{figures/fig2new.eps}
+\noindent In order to build a model that can predict a slot for a given far-field pattern, we first must generate training data.
+We build a numerical simulation of a leaky-wave antenna with a slot of length 18 mm divided into 36 sub-slots, each of which is 500 microns in length.
+The sub-slots are evenly divided between categories (i.e.
+metallic or transparent).
+We automate this random geometry generation and simulation using MPh \cite{john_hennig_2022_6312347}, an open-source Python package that enables controlling numerical simulation software using its API.
+Basic combinatorics theory tells us that there are over 9 billion possible slot designs that can be generated, indicating the usefulness of deep neural networks in this prediction task given the sheer number of possible outputs.
+Using only a few tens of thousands sets of training data, we will  predict an optimal slot design for an arbitrary peak profile.
+Each simulation takes approximately one minute to complete, meaning that generating training data is quite slow, but once the model is built it can produce an ideal slot for some far-field pattern in milliseconds, reinforcing its usefulness as a complement to rapid prototyping techniques.
+\\
 
-		\caption{A box plot showing the amplitudes at each peak; peak \#23 is always the highest amplitude because it is the primary emission angle of all LWAs, periodic and not, at 200 GHz.
-A wide array of values are evident.}
-	\end{subfigure}
-
-\end{figure}
-
-\noindent 25,000 instances of COMSOL simulation data is used as the data source for our deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
-Figure 2b above shows the possible values for each peak, giving an approximate range over which we can design peak profiles for this particular geometry.
+\noindent 20,000 instances of COMSOL simulation data were generated as the data source for the deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
 The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
 The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
-The model architecture is visualized in Figure 3.
+The model is visualized in Figure 3.
 \\
 
-\begin{figure}[b]
-	\centering
-	\includegraphics[width=6in]{figures/fig1.eps}
-	\caption{Neural network architecture schematic; peaks are used as the input data and passed through six hidden layers to predict the ideal slot design that will yield the closest possible signal.}
-\end{figure}
-
-\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this idea as our loss function, we would need to compute the far-field signal for each slot we generate as we train the model, which would be extraordinary (and unfeasibly) computationally expensive.
-Thus, instead, we turn to the idea of making the generated slot look as similar to the given training slot for a given peak profile as possible.
-Given that this is essentially a binary classification problem for each sub-slot, we use three weighted binary cross-entropy (BCE) loss functions, which are summed together to form our overall loss function with the following weightings:
-\begin{enumerate}
-  \item BCE between the true and predicted slot (2x)
-  \item BCE between the first derivative of the true and predicted slot using a Prewitt filter (1x)
-  \item BCE between the second derivative of the true and predicted slot using a Laplacian filter (1x)
-\end{enumerate}
-
-\section*{Results and Discussion}
-\subsection*{Binary Predictions}
-For some given peak geometry, the model returns each individual sub-slot's probability of being transparent (i.e.
-a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function.
-In Figure 4 below, for two sample peak profiles, the true slots (left), predicted slot (center) and rounded ML slot (right, i.e.
-making the 16 slots with the highest probabilities transparent and vice versa).
-Both of these predicted slots share many similarities with the true slot but there are also some differences -- the testing accuracy was about 68\% averaged over all of the training samples.
+%also I still need to expand on ML techniques at use here...
 
@@
 	\centering
-	\subfloat{{\includegraphics[height=2in]{figures/fig3_labeled.eps}}}
-	\subfloat{{\includegraphics[height=2in]{figures/fig3b_labeled.eps}}}
+	\includegraphics[width=6in]{figures/fig1pdf}
+	\caption{Neural network architecture schematic.
+The amplitudes at the angle of each possible Floquet mode are used as the input data and passed through one convolutional layer and six hidden layers within a neural network architecture to predict the  slot design that will yield the closest possible signal.
+Full network parameters can be found in the code}
+\end{figure}
+
+\noindent The tricky part of the inverse problem, as we consider here, is finding an appropriate loss function -- the primary objective is to generate a slot that minimizes the difference in signal compared to what is desired, but in order to use this basis as our loss function, we would need to compute the far-field signal for each new slot we generate as we train the model, which would be extraordinarily (and unfeasibly) computationally expensive.
+Thus, instead, we turn to the naive idea of making the generated slot look as similar to the given training slot for a given peak profile as possible, although not ideal (one can easily imagine a situation where a slot design was simply offset by 1 in either direction, from which we would expect a very similar response yet would likely score poorly in accuracy).
+Modified loss functions that introduced a convolutional element in order to emphasize spatial relationships and not exact locations of a sub-slot were tested but performed poorly compared to the naive loss funcrion.
+Given that this is a binary classification problem for each sub-slot, we use binary cross-entropy (BCE) loss.
+\\
+
+\noindent In addition to modulating between transparent and opaque sub-slots, one can imagine many other possible modulation schemes.
+While the exploration of these possibilities warrants a paper of their own, we choose to extend our model here to consider the case of partially transparent sub-slots.
+We generate training data and build a model just as we did with the binary case, with the only difference being that the sub-slots are split between 0\%, 50\%, and 100\% opacity, meaning that there is now an ``in-between" option for sub-slots between metallic and transparent, which we will call the ``grey'' case given the in-between nature of partially transparent sub-slots \\
+
+\subsection*{Experimental Methods}
+
+\noindent We also compare the predictions generated by numerical and machine learning techniques to experimental data.
+We produce simple hot-stamped leaky-wave antennas \cite{Guerboukha:21} and use a terahertz time-domain spectroscopy (TDS) system to measure the experimental far-field response, scanning both the forward and backwards scattering directions by moving the receiver along a rotation stage.
+The antenna designs are hot stamped -- meaning that the designs are printed in black and white using a standard laser printer and then passed through a laminator with a sheet of gold foil placed on top, a process that takes only a few minutes and enables rapid prototyping of LWAs.
+The completed LWA designs are shown in Figure 4a and 4b for both the binary and grey schemas.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=6in]{figures/setuppdf}
+	\caption{a) sample hot-stamped binary antenna; b) sample hot-stamped greyscale antenna; c) experimental setup, where the LWA is mounted on a rotation stage between a transmitter and receiver connected to a terahertz time-domain spectroscopy system}
+\end{figure}
+
+\noindent The hot-stamped surfaces are then attached to a metal plate, followed by a 1mm spacer and another plate of metal in order to form a parallel plate waveguide.
+This rapidly fabricated antenna is then mounted in the center of the rotation stage and aligned with the transmitter, lens, and coupler; the receiver is attached to the rotation stage and is moved to sweep the angular response of the far-field signal.
+
+\section*{Results and Discussion}
+
+\subsection*{Binary Sub-Slot Scheme}
+
+For some given far-field response, the compiled model extracts the Floquet peaks and predicts each individual sub-slot's probability of being transparent (i.e.
+a value close to 0 indicates the sub-slot should be metal, whereas a value close to 1 indicates a transparent sub-slot) using a sigmoid activation function.
+In Figure 5, for two random peak profiles inputted into the model, the objective signal and the slot that created it are shown alongside the slot design that the model predicted and the far-field pattern that slot actually generates.
+Both of these predicted slots look quite similar to the objective slot, although they are not exact matches; of the 4000 simulations used for testing the model's performance, 70.9\% of sub-slots were predicted correctly as transparent or metallic, indicating substantial predictive value over the baseline of 50\%.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[height=2.4in]{figures/binaryexamples}
 	\caption{Model predictions for two different peak profiles.
-The left-most slot design is the randomly generated slot used to generate this profile, the center plot shows the sigmoid probabilities of a transparent sub-slot, and the right-most plot shows the top 16 sub-slots from the probabilities.}
+The left slot design is the randomly generated slot used to generate the objective profile and the right slot design is what the model predicted for the objective far-field signal.
+The numerically-calculated far-field signal generated by the predicted slot is overlaid the objective signal.
+The MSEs of the left and right examples are 0.0155 and 0.0250, respectively.}
 \end{figure}
@@
 \noindent However, what determines the usefulness of our model is not the similarity of the slot but the similarity of the signal it generates to the objective.
-In order to consider the accuracy and usefulness of our model, we extract the predicted slot geometries, choose the top 16 slots based on the probabilities, and pass 500 of these new generated slots into our COMSOL model in order to compare the signal from the ML-generated slot to the originally desired peak profile.
-We then compare the peak profiles to the objective signal and calculate using the mean square error (MSE), as shown in the top left panel of Figure 5 below; the shape of the distribution matches that of similar work \cite{Nadell:19}.
-In the other panels of Figure 2, we plot the objective peak profile in black against the peak profile of an ML-generated slot, where the color corresponds to the four colored buckets depicted in the histogram.
-Overall, the agreement is quite excellent, particularly for the first two buckets (green and light blue), which compose about 60\% of testing samples with trends and relative amplitudes of the peaks agreeing very well.
-Even in the lower-tiered buckets, like in the bottom right panel of Figure 2, many of the peak profile trends are well matched -- however, there are some areas where the model does not perform as well, resulting in a higher MSE.
-Overall, though, the agreement is excellent and shows that the model can be used to design an acceptable slot for many potentially desired peak profiles.
+In order to consider the accuracy and usefulness of our model, we use the following procedure:
+
+\begin{enumerate}
+	\item Using the testing dataset, extract the Floquet peaks from the far-field signal and pass them through the model to obtain slot geometry predictions
+	\item Perform numerical simulation of the predicted slot geometries to obtain their far-field patterns
+	\item For each testing sample, compare the far-field response between the objective from the training set and the far-field response from the model-generated slot from Step 2 and compute MSE
+\end{enumerate}
+
+\noindent This procedure enables us to measure the performance of the model by a more useful metric than how similar the slot geometry is; rather, we can compare the similarity of the objective far-field response with the far-field response of the slot geometry the model predicts is optimal based on the objective input.
+Using the mean square error computed in Step 3, we plot a histogram of MSE in Figure 6a and compare it to a control where we compute the MSE between two random signals.
+The shape of the distribution in Figure 6a matches that of similar work \cite{Nadell:19} and is significantly better than the control (i.e.
+the similarity between two random far-field patterns), indicating substantial predictive value.
+The right panel of Figure 6 shows the wide range of normalized far-field power in dB at each possible peaks.
+The seventh peak, which occurs at 48 degrees, is always the highest because that is the primary mode of an LWA regardless of periodicity.
+
+\begin{figure}[H]
+	\includegraphics[width=6.5in]{figures/fig6apdf}
+		\caption{a) Mean square error (MSE) histogram.
+The horizontal displacement between the two histograms shows that the model predicts significantly more accurate antenna geometries than the control.
+b) Box plot of the possible values at each peak.
+A wide array of values are possible at each peak, indicating that the model may be effective over a wide range of far-field signals.}
+\end{figure}
+
+\noindent Overall, we see that most Floquet peaks have a wide range of possible values, indicating that our model can be used to predict an ideal geometry for a wide range of far-field patterns.
+The two examples in Figure 5 showcase the ability of the model to produce reasonable slots that approximate the desired far-field signal.
+These two cases showcase some of the better performance of the model, and like most models, not all inputs will yield a useful result.
+However, even for objective signals that yield substantially higher values of mean-square error, the overall peak behavior is often well-preserved, albeit with less exact results and more missed peaks, as would be expected from a higher MSE.
+Indeed, the goal of this investigation is to demonstrate the usefulness of neural networks for predicting antenna geometry, not to build a perfectly-tuned model.
+\\
+
+\noindent We also wish to compare our numerical predictions to experimental observations to test if the scheme we discuss is physically plausible for real-world antennas.
+First, using a terahertz time-domain spectroscopy (TDS), we measure and plot angle versus frequency for two different slots, one with a uniform periodic slot and one with our unique periodically-modulated slots as in Figure 6 below.
 
@@
 	\centering
-	\includegraphics{figures/fig2_labeled.eps}
-	\caption{Results from COMSOL simulations of ML-generated slots. The top left panel shows an MSE histogram while the others compare the ML-slot generated peak profile to the objective.}
+	\includegraphics{figures/exp-fig1pdf}
+	\caption{Experimental time-domain spectroscopy (TDS) measurements for two different slot designs, the left with only one periodicity and the right with a linear combination of periodicities.
+In the left panel, we see two discrete modes, whereas in the right panel we see a wide array of lower-power modes, as we would expect from a non-uniformly periodic slot.}
 \end{figure}
 
+\noindent Figure 7 confirms our expectations from Floquet theory.
+For the simple periodic slot, we see the main, non-periodic mode in addition to the one fast-wave Floquet mode.
+However, at right, we see many Floquet modes at play due to the periodicially-modulated nature of the slot; these two plots pose a sharp contrast to one another and show how our method is capable of producing a multitude of possible slot designs.
+From the TDS data in the right panel of Figure 7, we extract the far-field signal at 200 GHz and plot against the simulation data (both the objective signal, which is what we want to attain, and the expected signal, which is what we would expect for the slot the model actually predicted) for that slot in Figure 8 below.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[height=2.4in]{figures/477exppdf2}
+	\caption{Comparison of experimental and numerical results for non-uniform periodic slot.
+The experimental signal is what was measured for the given slot using TDS, the expected is what we expect for the antenna geometry the model predicts, and the objective is the desired signal.}
+\end{figure}
+
+\noindent We draw two primary conclusions from Figure 8, which are generated from the model's predictions for low values of MSE.
+First, the slot predicted by the model predicts a far-field signal quite similar to the objective function.
+Secondly, the experimental data generally agrees with the simulation data, particularly near the largest peaks, there are certainly differences between the numerical and experimental values.
+One possible cause is due to the relatively simple setup we are using to measure experimental data and the resulting geometrical difficulties of picking up back-scattering.
+However, the experimental measurements serve as a satisfactory proof of concept of our model and its usefulness with rapid prototyping techniques like hot stamping when designing antennas.
+
+\subsection*{Grey Sub-Slot Scheme}
+%
+%\noindent This second scheme significantly expands the scope of the problem because each sub-slot can take one of five values instead of just two: fully metallic, 25\% transparent, 50\% transparent, 75\% transparent, and 100\% transparent.
+We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer.
+This significantly increases the number of degrees of freedom within the model, as we see in the right panel of Figure 8 below; the range of values at each peak is broader than is seen than in Figure 4.
+%
+%\begin{figure}[H]
+%	\includegraphics[width=6.5in]{figures/histboxgreypdf}
+%		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
+%\end{figure}
+%
+%\noindent The left panel of Figure 8 shows the mean square error histogram for the 500 sets of testing data for which we numerically solved for the predicted slot's far-field pattern in order to compare its similarity to the objective.
+While the model performs similarly to the binary case (except for a slightly longer tail here), the control MSE histogram broadens and moves to the right.
+This means that our model performs better relative to the control with the greyscale scheme compared to the binary scheme, which is not unexpected given the increased degrees of freedom at play and the strength of neural network models at uncovering complex non-linear relationships.
+\\
+%
+%
+%\noindent Like before in Figure 5, we can plot some of the model-generated slots and the resulting far-field patterns in order to get an idea of what sort of slots the model is producing, which we plot in Figure 9 below.
+Overall, we see close agreement between the objective and ML-predicted slots, particularly at the largest peaks and the overall profile of the wave.
+%
+%%\begin{figure}[H]
+%%	\centering
+%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
+%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
+%%	\caption{Model predictions for two different peak profiles using the greyscale scheme.
+The left slot design is the randomly generated greyscale slot used to generate the objective, the center plot shows the ideal transparency of each sub-slot, and the right plot shows those rounded into the buckets used in the simulation.
+The MSEs of the left and right predictions are 0.0127 and 0.0113.}
+%%\end{figure}
+%
+%\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data.
+However, this is slightly more complicated experimental method -- we need to actually experimentally generate semi-transparent slots.
+We do this by using the aforementioned hot-stamping technique but instead of using black ink for metallic slots and the absence of ink for transparent slots, we calibrate our TDS system using ``grey'' slots, the idea being that changing the ink color within the greyscale spectrum will directly correlate with the amount of metal deposited on the surface of the antenna.
+We first calibrate shades of grey with transmission values, then using the shades of grey that conform to 25\%, 50\%, and 75\% transparency, we produce our LWAs using the exact same methodology as in the binary case.
+
 \section*{Conclusion}
+
+\noindent While rapid prototyping methods like hot stamping are useful for quickly testing antenna design, determining how to build an antenna that will produce some given signal is still a work in progress.
+It is easy to conceive of some far-field signal for some specific purpose (i.e.
+delivering a signal to receivers at some number of different locations but avoiding eavesdroppers at other locations	) and also to build a prototype of the antenna for rapid experimentation, but the ideas presented here begin to bridge the gap between conception and experimentation.
+A user with an idea of some highly specific signal might use such a model to obtain a starting point for an antenna geometry, after which techniques like hot-stamping can be used to tweak the antenna until optimal prototype performance is obtained.
+\\
+
+\noindent There remain many areas of further exploration; we present a baseline model that serves as a proof-of-concept, but it could surely be further improved and optimized by generating more training data and extensively tuning the model hyperparameters.
+Additionally, we explore only one additional method of modulation: making some sub-slots partially transparent.
+It is easy to conceive of other ideas, such as modulating the width of each sub-slot or further increasing the number of intermediate grey steps, all of which serve as significant areas of further research from both modeling and experimental perspectives.
+
+\section*{Data Availability}
+The large amount of training data makes its sharing prohibitively difficult but can be shared upon reasonable request from the authors.
+
+\section*{Code Availability}
+The neural network models, analysis, and simulation models are all shared in the public domain at *INSERT REPOSITORY HERE*
+
+\section*{Author Contributions}
+J.N. and H.G. conceived the underlying ideas; J.N. built the model, conducted the experiments, analyzed the data, and wrote the text with the assistance of H.G; D.M. supervised the investigation.
+
+\section*{Funding}
+Research funds de Quebec and NSF grants?
+
+\section*{Competing Interests}
+The authors declare no competing interests.
 

### 2022-06-27 1d/peaks_to_slot/3grey/another_analysis.py
3 grey model results...

@@ -1,0 +1,343 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/grey')
+import pickle
+import tensorflow as tf
+from tensorflow import losses
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+from preprocess import import_data, import_val_data
+
+###
+
+slots, peaks, signals = import_data()
+
+peaks.shape
+# selected_peaks = peaks[peaks[:,1] <0 ]
+
+fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
+
+boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
+plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
+plt.xlabel('Peak Count')
+plt.ylabel('Amplitude (normalized)')
+
+cmap = mpl.cm.get_cmap('GnBu')
+
+for index, patch in enumerate(boxplot['boxes']):
+    patch.set_facecolor(cmap(index / 36))
+
+plt.savefig('paper/figures/boxgrey.eps')
+
+###
+with open('1d/peaks_to_slot/grey/results/test_data_simp.pkl','rb') as file:
+    test_data = pickle.load(file)
+    peaks, true, pred, waves = test_data
+
+    predb = np.where((pred > 0) & (pred <= 0.125), 0, pred)
+    predb = np.where((predb > 0.125) & (predb <= 0.375), 0.25, predb)
+    predb = np.where((predb > 0.375) & (predb <= 0.625), 0.50, predb)
+    predb = np.where((predb > 0.625) & (predb <= 0.875), 0.75, predb)
+    predb = np.where((predb > 0.875), 1.00, predb)
+
+grey_slots, grey_peaks, grey_wves = import_val_data('1d/peaks_to_slot/grey/results/simplelosstest')
+
+grey_slots
+
+with open('1d/peaks_to_slot/grey/results/test_data.pkl','rb') as file:
[…]

### 2022-06-27 1d/peaks_to_slot/3grey/build_model.py

@@ -1,0 +1,205 @@
+import sys
+sys.path.append('/Users/joshuaneronha/.conda/envs/mittleman/bin/python')
+sys.path.append('1d/peaks_to_slot/3grey')
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+from preprocess import import_data, get_next_batch
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+import argparse
+import pickle
+import random
+
+parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
+
+def train(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        with tf.GradientTape() as tape:
+            efarx = model.call(peaks_batch)
+            efarx_loss = model.loss_function(efarx, slot_batch) #slots serves as the mask here
+            # print(efarx_loss)
+
+        gradients = tape.gradient(efarx_loss, model.trainable_variables)
+        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+
+    print('Efarx training loss: ', tf.reduce_mean(loss_list))
+    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+
+def test(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+    assump_acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        efarx = model.call(peaks_batch)
[…]

### 2022-06-27 1d/peaks_to_slot/3grey/peaks_to_slots_model.py

@@ -1,0 +1,117 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
+import tensorflow_io as tfio
+
+
+class LWAPredictionModel(tf.keras.Model):
+    def __init__(self, lr = 1e-4):
+        super(LWAPredictionModel, self).__init__()
+
+        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
+        self.batch_size = 128
+        self.epochs = 35
+
+        self.dense_layers = tf.keras.Sequential()
+        # self.dense_layers.add(Dense(1000, activation = 'relu'))
+        # self.dense_layers.add(Dense(800, activation = 'relu'))
+        self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Flatten())
+        self.dense_layers.add(Dense(3000))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        # self.dense_layers.add(ReLU())
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(36,activation='sigmoid'))
+
+    def call(self, input):
+        input = tf.expand_dims(input, 2)
+        return self.dense_layers(input)
+
[…]

### 2022-06-27 1d/peaks_to_slot/3grey/preprocess.py

@@ -1,0 +1,112 @@
+import numpy as np
+import tensorflow as tf
+import pickle
+import os
+
+# floquet_forward = [5,15,24,28,31,34,48,60,61,63,65,68,70,73,76,80,84,86,88,90]
+# floquet_back = [270 + (180 - x) for x in [95,99,101,103,106,109,114,117,120,122,126,128,130,132,146]]
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
+def import_data():
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+
+    timestamp_list = list(set([x.split('.')[0] for x in os.listdir('comsol_results/3grey/')]))
+
+    for timestamp in timestamp_list:
+
+        if timestamp == '1655498155':
+            continue
+
+        with open('comsol_results/3grey/' + timestamp + '.csv', 'rb') as file:
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet]
+
+            # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
+
+            # max = peaks[past_thresh].max(axis=1)
+            # print(max.shape)
+            # normalized = np.divide(peaks[past_thresh].T,np.max(peaks[past_thresh],axis=1)).T
+            normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
+            # normalized = (peaks / peaks.max(axis=0))
+            peaks_list.append(normalized)
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
+            # peaks_list.append(normalized)
+            # peaks_list.append(peaks)
+            # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
+
+        with open('comsol_results/3grey/' + timestamp + '.pkl', 'rb') as file:
[…]

### 2022-07-04 paper/paper.tex
pre cleaning up!

@@
 \bibliographystyle{naturemag}
+\usepackage{fancyhdr}
+
+\pagestyle{fancy}
+\fancyhf{}
+\rhead{DRAFT MANUSCRIPT (1 July 2022)}
+\lhead{Neronha et al. (2022)}
 
@@
 Inverse problem considers the opposite direction, for example reconstructing an image from scattered light \cite{Sun:18}.
-There have been many applications of neural networks to communications-related problems, for example, in the optimization of massive multiple-input multiple-output (MIMO) systems to improve signal reconstruction quality \cite{8322184} or physical layer design \cite{DBLP:journals/corr/OSheaEC17}.
-\emph{MORE EXAMPLES HERE?} \\
+There have been many applications of neural networks to communications-related problems, for example, in the optimization of massive multiple-input multiple-output (MIMO) systems to improve signal reconstruction quality \cite{8322184}, physical layer design \cite{DBLP:journals/corr/OSheaEC17}, or predicting channel state information \cite{8395053}.
+Neural networks and deep learning are particularly useful and interesting in communications applications because of their strength in predicting complex, nonlinear, and multivariate relationships that underly electromagnetics \cite{raissi2018deep}.\\
 
@@
 Each different mode peaks at some given angle $\theta$ defined by $\theta=\cos^{-1}(\beta_p/k_0)$, given that the excited modes can be consider fast-wave (i.e.
-$|\beta_p|>k_0$ ).
+$|\beta_p|>k_0$ ) \cite{6556051}.
 Our primary objective is to generate multiple beams with specific magnitudes at specific locations, which we demonstrate in Figure 2a using numerical simulations of four periodic waveguides with different periodicities.
@@
 	\centering
-	\includegraphics[width=6in]{figures/theorypdf}
-	\caption{Floquet theory predictions for geometry.
+	\includegraphics[width=6in]{figures/theorypdfslots}
+	%we still have theorypdf.pdf which was that weird scatter plot... do we like that? maybe not the best way to represent but I can't think of a better way.
+	\caption{Floquet theory predictions for different geometries of uniform periodicities.
 a) Numerical simulations for uniformly periodic LWAs with four different values of $\Lambda$; each peaks at different angles, indicating how we use superposition of modes to generate a wide array of possible angles.
 Note that all periods have a maximum around 48 degrees, which is the primary mode for a LWA of these dimensions.
-b) The possible Floquet modes from any linear combination of modes predicted by Equation 1; as expected, the positive modes occur in forward scattering and the negative modes in back-scattering.
-}
+b) The slots used to generate these uniform periodicities; the light sub-slots indicate metal and the darker sub-slots are transparent.}
 \end{figure}
@@
 calculating the slot for some given far-field profile), however, is difficult; deriving an analytical expression for a complicated regime is difficult if not impossible, and solving numerically would require iteration through multiple antenna designs until arriving at an optimal solution, essentially searching for one needle in a haystack of $2^{32}$ possible antenna geometries.
-This is where the idea of a neural network model enters -- deep learning methods are effective at describing nonlinear relationships of complex systems simply by providing training data from which the model can ``learn''.
+This is where the idea of a neural network model enters -- deep learning methods are effective at describing nonlinear relationships of complex systems simply by providing training data from which the model can ``learn'' \cite{raissi2018deep}.
 Thus, we build a model that predicts the slot geometry for some input of a desired far-field signal.
@@
 \noindent 20,000 instances of COMSOL simulation data were generated as the data source for the deep neural network, with a test-train split of 80-20 \cite{molecules26041111}.
-The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$.
-The model uses the Adam optimizer and has a learning rate of 0.0001 and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
+The network, which is built with TensorFlow \cite{tensorflow2015-whitepaper}, a popular deep-learning library, has one convolutional layer for feature extraction \cite{albawi2017understanding} connected to six sequential fully-connected layers, each of which have 2000 neurons and use a LeakyReLU activation function with $\alpha = 0.1$ \cite{nair2010rectified}.
+The model uses the Adam optimizer \cite{kingma2014adam} and has a learning rate of 0.0001, batch size of 128, and trains the model over 35 epochs \cite{smith2018disciplined} and predicts the output of each individual sub-slot with a sigmoid activation function indicating the probability that a given sub-slot should be transparent.
 The model is visualized in Figure 3.
@@
 	\centering
-	\includegraphics[width=6in]{figures/fig1pdf}
+	\includegraphics[width=5.2in]{figures/fig1pdf}
 	\caption{Neural network architecture schematic.
@@
 Given that this is a binary classification problem for each sub-slot, we use binary cross-entropy (BCE) loss.
-\\
+\cite{10.1145/1102351.1102422} \\
 
@@
 	\centering
-	\includegraphics[width=6in]{figures/setuppdf}
+	\includegraphics[width=6in]{figures/setuppdf2}
 	\caption{a) sample hot-stamped binary antenna; b) sample hot-stamped greyscale antenna; c) experimental setup, where the LWA is mounted on a rotation stage between a transmitter and receiver connected to a terahertz time-domain spectroscopy system}
@@
 In Figure 5, for two random peak profiles inputted into the model, the objective signal and the slot that created it are shown alongside the slot design that the model predicted and the far-field pattern that slot actually generates.
-Both of these predicted slots look quite similar to the objective slot, although they are not exact matches; of the 4000 simulations used for testing the model's performance, 70.9\% of sub-slots were predicted correctly as transparent or metallic, indicating substantial predictive value over the baseline of 50\%.
 
@@
 Using the mean square error computed in Step 3, we plot a histogram of MSE in Figure 6a and compare it to a control where we compute the MSE between two random signals.
-The shape of the distribution in Figure 6a matches that of similar work \cite{Nadell:19} and is significantly better than the control (i.e.
-the similarity between two random far-field patterns), indicating substantial predictive value.
-The right panel of Figure 6 shows the wide range of normalized far-field power in dB at each possible peaks.
-The seventh peak, which occurs at 48 degrees, is always the highest because that is the primary mode of an LWA regardless of periodicity.
-
+The shape of the distribution in Figure 6a matches that of similar work \cite{Nadell:19}.
+We conduct a two-sided Z-test -- the requirements of which are satisfied given that the histogram indicates a normal distribution, there are 30+ samples, and samples are independent -- and confirm the model's predictive value is statistically significant with a p-value of 2.91e-89, which indicates significance at a very low value of $\alpha$.
+The average MSE of the model results is 0.0361, and the subslot prediction accuracy is 70.0\%, which is above the baseline value of fifty percent at which there would be no predictive value.
 \begin{figure}[H]
@@
 		\caption{a) Mean square error (MSE) histogram.
-The horizontal displacement between the two histograms shows that the model predicts significantly more accurate antenna geometries than the control.
+The horizontal displacement between the two histograms shows that the model predicts significantly more accurate antenna geometries than the control and is confirmed by a Z-test.
 b) Box plot of the possible values at each peak.
@@
 
-\noindent Overall, we see that most Floquet peaks have a wide range of possible values, indicating that our model can be used to predict an ideal geometry for a wide range of far-field patterns.
+\noindent Figure 6b shows the wide range of normalized far-field power in dB at each possible peaks.
+The seventh peak, which occurs at 48 degrees, is always the highest because that is the primary mode of an LWA regardless of periodicity.
+Overall, we see that most Floquet peaks have a wide range of possible values, indicating that our model can be used to predict an ideal geometry for a wide range of far-field patterns.
 The two examples in Figure 5 showcase the ability of the model to produce reasonable slots that approximate the desired far-field signal.
@@
 	\centering
-	\includegraphics[height=2.4in]{figures/477exppdf2}
+	\includegraphics[height=2.1in]{figures/477exppdf2}
 	\caption{Comparison of experimental and numerical results for non-uniform periodic slot.
@@
 \subsection*{Grey Sub-Slot Scheme}
+
+\noindent This more advanced schema significantly expands the scope of the problem because each sub-slot can take one of three values instead of just two: 0\% transparent (i.e.
+fully metallic), 50\% transparent, and 100\% transparent.
+We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer.
+This significantly increases the number of degrees of freedom within the model, which we would expect would allow us to generate slots for a wider array of potential signals.
+This is suggested by Figure 9b below; the range of values at each peak is broader in the grey model than for the binary model.
 %
-%\noindent This second scheme significantly expands the scope of the problem because each sub-slot can take one of five values instead of just two: fully metallic, 25\% transparent, 50\% transparent, 75\% transparent, and 100\% transparent.
-We again generate approximately 20,000 samples using numerical simulation where each sub-slot can take on these values using a transition boundary layer.
-This significantly increases the number of degrees of freedom within the model, as we see in the right panel of Figure 8 below; the range of values at each peak is broader than is seen than in Figure 4.
-%
-%\begin{figure}[H]
-%	\includegraphics[width=6.5in]{figures/histboxgreypdf}
-%		\caption{The left panel shows the mean square error histogram and verifies the model's predictive value while the right panel shows the wide array of possible values at each peak.}
-%\end{figure}
-%
-%\noindent The left panel of Figure 8 shows the mean square error histogram for the 500 sets of testing data for which we numerically solved for the predicted slot's far-field pattern in order to compare its similarity to the objective.
-While the model performs similarly to the binary case (except for a slightly longer tail here), the control MSE histogram broadens and moves to the right.
-This means that our model performs better relative to the control with the greyscale scheme compared to the binary scheme, which is not unexpected given the increased degrees of freedom at play and the strength of neural network models at uncovering complex non-linear relationships.
-\\
-%
-%
-%\noindent Like before in Figure 5, we can plot some of the model-generated slots and the resulting far-field patterns in order to get an idea of what sort of slots the model is producing, which we plot in Figure 9 below.
-Overall, we see close agreement between the objective and ML-predicted slots, particularly at the largest peaks and the overall profile of the wave.
-%
-%%\begin{figure}[H]
-%%	\centering
-%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_71.eps}}}
-%%	\subfloat{{\includegraphics[height=2.1in]{figures/grey_example_127.eps}}}
-%%	\caption{Model predictions for two different peak profiles using the greyscale scheme.
-The left slot design is the randomly generated greyscale slot used to generate the objective, the center plot shows the ideal transparency of each sub-slot, and the right plot shows those rounded into the buckets used in the simulation.
-The MSEs of the left and right predictions are 0.0127 and 0.0113.}
-%%\end{figure}
-%
-%\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data.
+\begin{figure}[H]
+	\includegraphics[width=6.5in]{figures/histandboxgreyoverlay}
+		\caption{a) The mean square error histogram for both the grey model performance and a control sample.
+The horizontal offset indicates the model's predictive value and is confirmed by a Z-test.
+b) A box plot of possible normalized power values for both models.
+The grey model allows for a wider array of values, as we expect from the increase degrees of freedom in this model.}
+\end{figure}
+
+\noindent As with the binary case, we plot a histogram of the model results in Figure 9a and again note the horizontal offset between the model and control.
+We again conducted two-sided z-test between two samples with the same justifications and again establish a statistically significant difference with p-value of 1.86e-72, indicating significance at a very low value of $\alpha$ (albeit the p-value here is higher than for the binary model, although both are very lower).
+The average MSE is 0.0434, which is higher than in the binary case, and the sub-slot accuracy is 48.1\%; while higher than the base 33.3\% one would expect given there is a 1/3 chance of correctly guessing, this accuracy is lower than in the binary case.
+This is not unexpected; due to computational constraints, we generate the same number of training samples as the binary case despite the increased degrees of freedom ($3^{36}$ instead of $2^{36}$, a significant increase).
+That means in the grey schema, we have a smaller amount of data in relation to the number of possible outcomes, which may explain the decreased accuracy.
+
+\noindent As before, we are interested in comparing the results of our model and numerical simulations to experimental data.
 However, this is slightly more complicated experimental method -- we need to actually experimentally generate semi-transparent slots.
 We do this by using the aforementioned hot-stamping technique but instead of using black ink for metallic slots and the absence of ink for transparent slots, we calibrate our TDS system using ``grey'' slots, the idea being that changing the ink color within the greyscale spectrum will directly correlate with the amount of metal deposited on the surface of the antenna.
-We first calibrate shades of grey with transmission values, then using the shades of grey that conform to 25\%, 50\%, and 75\% transparency, we produce our LWAs using the exact same methodology as in the binary case.
+We first calibrate shades of grey with transmission values to determine the greyscale value between 0 and 255 that yields approximately 50\% transmission; we find it to be 109.
+We then produce our LWAs using the exact same methodology as in the binary case.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[height=2.4in]{figures/greyexperiment}
+		\caption{(34 in set).
+An example of the grey model's performance and comparison to experimental results.
+The left slot design shows the slot used to produce the objective far-field signal and the right slot design shows the model's prediction.
+The polar plot shows the far-field signals computed numerically for each of these slots, overlaid with the experimental results collected using TDS.
+The numerical predicted and objective far-field signals closely agree with an MSE of 0.0311, despite slots that while sharing similarities are somewhat different, and match the experimental data well.}
+\end{figure}
+
+\noindent An example of the model's predictive performance is shown in Figure 10, along with a comparison to the experimental results for the predicted slot collected using the method described in the previous paragraph with the TDS setup described in Figure 4c.
+We draw a handful of conclusions from Figure 10.
+First, for this example, which has an MSE approximately in the center of the histogram and thus can be considered roughly average performance for the model, the predicted and objective far-field signals generally agree quite well and have very similar shapes, despite having slot patterns that are not exactly the same, as we would expect from Floquet theory -- there are many ways to achieve a linear combination of periodicities.
+Secondly, the experimental results agree fairly closely with the numerical predicted values.
+While there are some differences particularly in the backwards direction, it is important to remember that these results were collected using hot-stamping, an inherently inexact rapid-prototyping technique that is particularly imprecise given that we can only generate an approximately 50\% transparent slot subject to the whims of the laster printer, in addiction to the difficulty of measuring back-reflection at large angles $\geq 140$ degrees.
+Overall, the experiment confirms the validity of producing LWA metasurfaces in this fashion, and we expect the experimental accuracy to be higher using more advanced methods of producting metasurfaces.
 
@@
 
-\noindent There remain many areas of further exploration; we present a baseline model that serves as a proof-of-concept, but it could surely be further improved and optimized by generating more training data and extensively tuning the model hyperparameters.
+\noindent There remain many areas of further exploration; we present a baseline model that serves as a proof-of-concept, but it could surely be further improved and optimized by generating more training data and extensively tuning the model hyper-parameters.
 Additionally, we explore only one additional method of modulation: making some sub-slots partially transparent.
@@
 \section*{Data Availability}
-The large amount of training data makes its sharing prohibitively difficult but can be shared upon reasonable request from the authors.
+The data that support the findings of this study are available from the corresponding author upon reasonable request.
 
@@
 \section*{Funding}
-Research funds de Quebec and NSF grants?
+This work was supported by the U.S. National Science Foundation?
 

### 2022-07-04 1d/peaks_to_slot/3grey/another_analysis.py

@@ -2,59 +2,66 @@ import sys
 import matplotlib.pyplot as plt
 import matplotlib as mpl
 import numpy as np
-sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/grey')
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/3grey')
 import pickle
 import tensorflow as tf
 from tensorflow import losses
+from statsmodels.stats.weightstats import ztest
 
 mpl.rcParams['font.family'] = 'Arial'
 plt.rcParams['font.size'] = 12
 plt.rcParams['axes.linewidth'] = 2
 
-from preprocess import import_data, import_val_data
+from preprocess import import_data, import_val_data, import_data_bin
 
 ###
 
 slots, peaks, signals = import_data()
+slotsbin, peaksbin, signalsbin = import_data()
 
 peaks.shape
 # selected_peaks = peaks[peaks[:,1] <0 ]
 
 fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
 
-boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
+boxplot1 = axs.boxplot(peaks, sym = '', patch_artist = True)
+axs2 = axs.twinx()
+axs2.set_ylim(axs.get_ylim())
 plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
 plt.xlabel('Peak Count')
 plt.ylabel('Amplitude (normalized)')
+boxplot2= axs2.boxplot(peaksbin, sym = '', patch_artist = True)
 
-cmap = mpl.cm.get_cmap('GnBu')
+# cmap = mpl.cm.get_cmap('GnBu')
+#
+for index, patch in enumerate(boxplot1['boxes']):
+    patch.set_facecolor('blue')
 
-for index, patch in enumerate(boxplot['boxes']):
-    patch.set_facecolor(cmap(index / 36))
+for index, patch in enumerate(boxplot2['boxes']):
+    patch.set_facecolor('red')
 
-plt.savefig('paper/figures/boxgrey.eps')
+plt.setp(boxplot1['whiskers'], color='blue')
+plt.setp(boxplot2['whiskers'], color='red')
+
+ plt.savefig('paper/figures/box3grey.svg')
 
 ###
[…]

### 2022-07-04 1d/peaks_to_slot/3grey/preprocess.py

@@ -100,6 +100,48 @@ def import_val_data(path):
     # return np.concatenate(slots_list), np.concatenate([np.concatenate(peaks_list), np.concatenate(max_list)],axis=1)
     return np.concatenate(slots_list), np.concatenate(peaks_list), np.concatenate(wave_list)
 
+def import_data_bin():
+    """
+    Loads in data and transposes it into proper shapes
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+    timestamp_list = list(set([x.split('.')[0] for x in os.listdir('comsol_results/1dconstantslots')]))
+
+    for timestamp in timestamp_list:
+
+        with open('comsol_results/1dconstantslots/' + timestamp + '.csv', 'rb') as file:
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet]
+
+            # past_thresh = [index for index,x in enumerate(peaks) if x.max() > 29]
+
+            # max = peaks[past_thresh].max(axis=1)
+            # print(max.shape)
+            # normalized = np.divide(peaks[past_thresh].T,np.max(peaks[past_thresh],axis=1)).T
+            normalized = (peaks.T / peaks.max(axis=1)).T# TEMP:
+            # normalized = (peaks / peaks.max(axis=0))
+            peaks_list.append(normalized)
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
+            # peaks_list.append(normalized)
+            # peaks_list.append(peaks)
+            # max_list.append(np.concatenate([max,max,max,max,max,max],axis=1))
+
+        with open('comsol_results/1dconstantslots/' + timestamp + '.pkl', 'rb') as file:
+            slots = np.array(pickle.load(file))
+            # print(slots.shape)
+            slots_list.append(slots)
+
+    # return np.concatenate(slots_list), np.concatenate([np.concatenate(peaks_list), np.concatenate(max_list)],axis=1)
+    return np.concatenate(slots_list), np.concatenate(peaks_list), np.concatenate(wave_list)
+
 def get_next_batch(input_array, label_array, start_index, batch_size):
     """
     Accepts an array of inputs and labels along with a starting index and batch

### 2022-07-04 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -5,7 +5,8 @@ import numpy as np
 sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power')
 import pickle
 import tensorflow as tf
-plt.hist()
+from statsmodels.stats.weightstats import ztest
+stats
 mpl.rcParams['font.family'] = 'Arial'
 plt.rcParams['font.size'] = 12
 plt.rcParams['axes.linewidth'] = 2
@@ -35,12 +36,7 @@ plt.xlabel('Peak Count')
 plt.ylabel('Amplitude (normalized)')
 plt.ylim([-0.4,1])
 
-cmap = mpl.cm.get_cmap('GnBu')
-
-for index, patch in enumerate(boxplot['boxes']):
-    patch.set_facecolor(cmap(index / 36))
-
-plt.savefig('paper/figures/boxbinary.eps')
+plt.savefig('paper/figures/boxbinarymono.svg')
 
 ###
 
@@ -70,6 +66,7 @@ correct = 0
 for i in np.arange(len(val510_slots)):
     correct += (val510_slots[i] == true[i]).sum()
 
+val510_slots
 
 mse_list_binary = []
 # mse_list_grey = []
@@ -106,6 +103,17 @@ for i in np.arange(500):
 #        0.07960798, 0.08748235, 0.09535672, 0.10323109, 0.11110546,
 #        0.11897984, 0.12685421, 0.13472858, 0.14260295, 0.15047732,
 #        0.15835169])
+
+ztest(mse_list_binary, mse_list_control,value=0,alternative='two-sided')
+np.mean(mse_list_binary)
+np.mean(mse_list_control)
+ pred = np.array(pred)
+for i in np.arange(len(pred)):
+    pred[i,:] = top_16(pred[i,:])
+
+ba = tf.keras.metrics.BinaryAccuracy()
+ba(true,pred)
+
 bins
 bucket_2
 tf.stack(mse_list_binary).numpy()
@@ -130,7 +138,7 @@ for i,thispatch in enumerate(patches):
 axs.legend(['Model','Random'])
 # plt.ylim([0, 115])
 
-plt.savefig('paper/figures/binary_histogram.svg')
+plt.savefig('paper/figures/binary_histogramnew.svg')
 bins
 # axs[1].set_xlabel('Mean Square Error')
 # axs[1].set_ylabel('Count')
[…]

### 2022-07-04 experiments/threegreytesting.m

@@ -110,9 +110,10 @@ period = 0.95e-3;
 figure
 polarplot(deg2rad(1:151),mag2db(abs(B(2112,1:151)) / max(abs(B(2112,1:151)))),'Color','#f7a400','LineWidth',2)
 hold on
-% polarplot(deg2rad(1:151),mag2db(objective241(1:151,2) / max(objective241(1:151,2))),'Color','r','LineWidth',2)
-
 polarplot(deg2rad(1:151),mag2db(expected241(1:151,2) / max(expected241(1:151,2))),'Color','#1d91c0','LineWidth',2)
+polarplot(deg2rad(1:151),mag2db(objective241(1:151,2) / max(objective241(1:151,2))),'Color','#0c2c84','LineWidth',2)
+
+
 % polarplot(deg2rad(1:151),mag2db(expected241cont(1:151,2) / max(expected241cont(1:151,2))),'Color','g','LineWidth',2)
 % polarplot(deg2rad(1:151),mag2db(random(1:151,1) / max(random(1:151,1))),'Color','g','LineWidth',2)
 % polarplot(deg2rad(1:151),mag2db(objective241(1:151,2) / max(objective241(1:151,2))),'Color','g','LineWidth',2)
@@ -132,7 +133,7 @@ pax.ThetaZeroLocation = 'right';
 rlim([-30 0])
 thetalim([0 180])
 thetaticks(0:30:180)
-legend('Experimental','Simulation','Random','location','southwest')
+legend('Experimental','Expected','Objective','location','southwest')
 set(gcf,'color','w');
 % 
 % figure

### 2022-07-04 statstesting.py

@@ -1,0 +1,11 @@
+from statsmodels.stats.weightstats import ztest as ztest
+
+#enter IQ levels for 20 individuals from each city
+cityA = [82, 84, 85, 89, 91, 91, 92, 94, 99, 99,
+         105, 109, 109, 109, 110, 112, 112, 113, 114, 114]
+
+cityB = [90, 91, 91, 91, 95, 95, 99, 99, 108, 109,
+         109, 114, 115, 116, 117, 117, 128, 129, 130, 133]
+
+#perform two sample z-test
+ztest(cityA, cityB, value=0) 

### 2022-07-05 1d/peaks_to_slot/3grey/another_analysis.py
pre-submission organizing

@@ -1,364 +1,0 @@
-import sys
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import numpy as np
-sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/3grey')
-import pickle
-import tensorflow as tf
-from tensorflow import losses
-from statsmodels.stats.weightstats import ztest
-
-mpl.rcParams['font.family'] = 'Arial'
-plt.rcParams['font.size'] = 12
-plt.rcParams['axes.linewidth'] = 2
-
-from preprocess import import_data, import_val_data, import_data_bin
-
-###
-
-slots, peaks, signals = import_data()
-slotsbin, peaksbin, signalsbin = import_data()
-
-peaks.shape
-# selected_peaks = peaks[peaks[:,1] <0 ]
-
-fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
-
-boxplot1 = axs.boxplot(peaks, sym = '', patch_artist = True)
-axs2 = axs.twinx()
-axs2.set_ylim(axs.get_ylim())
-plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
-plt.xlabel('Peak Count')
-plt.ylabel('Amplitude (normalized)')
-boxplot2= axs2.boxplot(peaksbin, sym = '', patch_artist = True)
-
-# cmap = mpl.cm.get_cmap('GnBu')
-#
-for index, patch in enumerate(boxplot1['boxes']):
-    patch.set_facecolor('blue')
-
-for index, patch in enumerate(boxplot2['boxes']):
-    patch.set_facecolor('red')
-
-plt.setp(boxplot1['whiskers'], color='blue')
-plt.setp(boxplot2['whiskers'], color='red')
-
- plt.savefig('paper/figures/box3grey.svg')
-
-###
-with open('1d/peaks_to_slot/3grey/results/test_data627.pkl','rb') as file:
-    test_data = pickle.load(file)
-    peaks, true, pred, waves = test_data
-
-    predb = np.where((pred > 0) & (pred <= 0.333), 0, pred)
-    predb = np.where((predb > 0.333) & (predb <= 0.666), 0.50, predb)
[…]

### 2022-07-05 1d/peaks_to_slot/constant_power/another_analysis.py

@@ -1,319 +1,0 @@
-import sys
-import matplotlib.pyplot as plt
-import matplotlib as mpl
-import numpy as np
-sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/1d/peaks_to_slot/constant_power')
-import pickle
-import tensorflow as tf
-from statsmodels.stats.weightstats import ztest
-stats
-mpl.rcParams['font.family'] = 'Arial'
-plt.rcParams['font.size'] = 12
-plt.rcParams['axes.linewidth'] = 2
-from tensorflow import losses
-
-tensorflow.losses.mse([1],[3])
-
-from preprocess import import_data, import_val_data
-
-floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
-        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
-       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
-       132., 147.]).astype('int'))
-
-###
-
-slots, peaks, _ = import_data()
-
-peaks.shape
-# selected_peaks = peaks[peaks[:,1] <0 ]
-
-fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
-
-boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
-plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
-plt.xlabel('Peak Count')
-plt.ylabel('Amplitude (normalized)')
-plt.ylim([-0.4,1])
-
-plt.savefig('paper/figures/boxbinarymono.svg')
-
-###
-
-with open('1d/peaks_to_slot/constant_power/results/test_data510.pkl','rb') as file:
-    test_data = pickle.load(file)
-    peaks, true, pred, waves = test_data
-
-true
-top_16(pred)
-# val_slots, val_peaks = import_val_data('1d/peaks_to_slot/constant_power/results/validation_old')
-
-val510_slots, val510_peaks, val510_waves = import_val_data('1d/peaks_to_slot/constant_power/results/validation510')
-
[…]

### 2022-07-05 1d/peaks_to_slot/constant_power/build_model.py

@@ -1,151 +1,0 @@
-import numpy as np
-import tensorflow as tf
-from peaks_to_slots_model import LWAPredictionModel
-from preprocess import import_data, get_next_batch
-from sklearn.model_selection import train_test_split
-import matplotlib.pyplot as plt
-import argparse
-import pickle
-import random
-
-parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
-
-def train(model, slots, peaks):
-    completed = 0
-
-    loss_list = []
-    acc_list = []
-
-    while completed < len(slots):
-
-        our_size = model.batch_size
-
-        if len(slots) - completed < model.batch_size:
-            our_size = len(slots) - completed
-
-        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
-
-        completed += our_size
-
-        with tf.GradientTape() as tape:
-            efarx = model.call(peaks_batch)
-            efarx_loss = model.loss_function(efarx, slot_batch) #slots serves as the mask here
-            # print(efarx_loss)
-
-        gradients = tape.gradient(efarx_loss, model.trainable_variables)
-        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
-
-        loss_list.append(efarx_loss)
-        acc_list.append(model.accuracy(efarx, slot_batch))
-
-    print('Efarx training loss: ', tf.reduce_mean(loss_list))
-    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
-
-def test(model, slots, peaks):
-    completed = 0
-
-    loss_list = []
-    acc_list = []
-    assump_acc_list = []
-
-    while completed < len(slots):
-
-        our_size = model.batch_size
-
-        if len(slots) - completed < model.batch_size:
-            our_size = len(slots) - completed
-
-        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
-
-        completed += our_size
-
-        efarx = model.call(peaks_batch)
-        efarx_loss = model.loss_function(efarx, slot_batch)
-
-        loss_list.append(efarx_loss)
-        acc_list.append(model.accuracy(efarx, slot_batch))
-        assump_acc_list.append(model.assump_accuracy(efarx,slot_batch))
-
-
[…]

### 2022-07-05 1d/peaks_to_slot/constant_power/peaks_to_slots_model.py

@@ -1,97 +1,0 @@
-import numpy as np
-import tensorflow as tf
-import tensorflow_probability as tfp
-from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
-import tensorflow_io as tfio
-
-
-class LWAPredictionModel(tf.keras.Model):
-    def __init__(self, lr = 5e-5):
-        super(LWAPredictionModel, self).__init__()
-
-        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
-        self.batch_size = 64
-        self.epochs = 20
-
-        self.dense_layers = tf.keras.Sequential()
-        # self.dense_layers.add(Dense(1000, activation = 'relu'))
-        # self.dense_layers.add(Dense(800, activation = 'relu'))
-        self.dense_layers.add(Conv1D(128,5))
-        self.dense_layers.add(Flatten())
-        self.dense_layers.add(Dense(2000))
-        # self.dense_layers.add(ReLU())
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-        self.dense_layers.add(Dense(2000))
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-        # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-        # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-        # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-        # self.dense_layers.add(ReLU())
-        self.dense_layers.add(Dense(2000))
-        self.dense_layers.add(LeakyReLU(0.1))
-        self.dense_layers.add(Dropout(0.1))
-
-        self.dense_layers.add(Dense(36,activation='sigmoid'))
-
-    def call(self, input):
-        input = tf.expand_dims(input, 2)
-        return self.dense_layers(input)
-
[…]

### 2022-07-05 1d/peaks_to_slot/constant_power/test.py

@@ -1,3 +1,0 @@
-import os
-
-list(set([x.split('.')[0] for x in os.listdir('comsol_results/1dconstantslots')]))

### 2022-07-05 analysis/3grey/another_analysis.py

@@ -1,0 +1,134 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('ml_model/3grey')
+import pickle
+import tensorflow as tf
+from tensorflow import losses
+from statsmodels.stats.weightstats import ztest
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+from preprocess import import_data, import_val_data, import_data_bin
+
+#creating box plot for the grey and binary cases
+
+slots, peaks, signals = import_data()
+slotsbin, peaksbin, signalsbin = import_data_bin()
+
+fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
+boxplot1 = axs.boxplot(peaks, sym = '', patch_artist = True)
+axs2 = axs.twinx()
+
+axs2.get_yaxis().set_visible(False)
+axs.set_ylim([-0.4,1])
+axs2.set_ylim(axs.get_ylim())
+plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
+plt.xlabel('Peak Count')
+axs.set_ylabel('Amplitude (normalized)')
+boxplot2= axs2.boxplot(peaksbin, sym = '', patch_artist = True)
+
+axs.set_xticks(np.arange(35)[::5])
+axs2.set_xticks(np.arange(35)[::5])
+axs.set_xticklabels(np.arange(35)[::5])
+axs2.set_xticklabels(np.arange(35)[::5])
+plt.tight_layout()
+
+for index, patch in enumerate(boxplot1['boxes']):
+    patch.set_facecolor('#0c2c84')
+    patch.set_alpha(0.5)
+
+for index, patch in enumerate(boxplot2['boxes']):
+    patch.set_facecolor('#fc1303')
+    patch.set_alpha(0.5)
+
+plt.setp(boxplot1['whiskers'], color='#0c2c84')
+plt.setp(boxplot2['whiskers'], color='#fc1303')
+
+plt.legend(['Grey Model','Binary Model'],loc='lower right')
+
+# plt.savefig('paper/figures/box3greyoverlay.svg')
+
+###testing validation data where model generated slots put back into COMSOL
+with open('analysis/3grey/test_data627.pkl','rb') as file:
[…]

### 2022-07-05 analysis/3grey/threegrey_analysis.m

@@ -1,0 +1,69 @@
+clear all
+clc
+close all
+
+Files=dir('gray-june29-2');
+N = length(Files);
+[t,w]=textread(strcat('gray-june29-2/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('gray-june29-2/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+objective241 = readmatrix('objective34.csv');
+expected241 = readmatrix('data34.csv');
+
+%%
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','#F7A400')
+axis square
+
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+
+%% plotting
+figure
+polarplot(deg2rad(1:149),mag2db(abs(B(2112,3:151)) / max(abs(B(2112,3:151)))),'Color','#f7a400','LineWidth',2)
+hold on
[…]

### 2022-07-05 analysis/baseline_periodic_comsol/baseline.py

@@ -1,0 +1,25 @@
+
+import numpy as np
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+
+onemm = 20*np.log10(np.loadtxt('Baseline/lambda1mm.csv',delimiter=','))
+twomm = 20*np.log10(np.loadtxt('Baseline/lambda2mm.csv',delimiter=','))
+fourmm = 20*np.log10(np.loadtxt('Baseline/lambda4mm.csv',delimiter=','))
+eightmm = 20*np.log10(np.loadtxt('Baseline/lambda8mm.csv',delimiter=','))
+
+fig, ax = plt.subplots(figsize=(4,3))
+ax.plot(onemm[:,1],color='#c7e9b4')
+ax.plot(twomm[:,1],color='#7fcdbb')
+ax.plot(fourmm[:,1],color='#1d91c0')
+ax.plot(eightmm[:,1],color='#0c2c84')
+ax.legend(['$\lambda$ = 1mm','$\lambda$ = 2mm','$\lambda$ = 4mm','$\lambda$ = 8mm'])
+plt.xlim([0, 180])
+# plt.savefig('theoreticallambda.pdf')
+# %% codecell
+!pip install tensorflow
+# %% codecell

### 2022-07-05 analysis/binary/a477may24_fixedplastic.m

@@ -1,0 +1,71 @@
+ clear all
+clc
+close all
+
+Files=dir('binarywaveguide477-furtherplastic/');
+N = length(Files);
+[t,w]=textread(strcat('binarywaveguide477-furtherplastic/',Files(3).name),'%f%f','headerlines',6);  % read first for size
+T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
+T(:,1)=t;
+W(:,1)=w;
+
+B(:,1) = fftshift(fft(W(:,1)));
+
+t = T(:,1);
+fmax = 0.5/(t(2)-t(1));
+f(:,1) = linspace(-fmax,fmax,size(W,1));
+
+for k = 3:N
+    name = Files(k).name;
+    x = split(name,'.');
+    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-furtherplastic/',name),'%f%f','headerlines',6);
+    
+    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
+    t = T(:,str2double(x(1)) + 1);
+    fmax = 0.5/(t(2)-t(1));
+    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
+end
+
+objective241 = readmatrix('objective477.csv');
+expected241 = readmatrix('expected477_base.csv');
+%%
+figure
+plot1 = pcolor(1:151,f(2096:2150),abs(B(2096:2150,1:151)));
+set(plot1, 'EdgeColor', 'none');
+ylabel('Frequency (THz)')
+xlabel('Angle (degrees)')
+
+theta_pm = linspace(0,90,1000); 
+order_m = 1; % order of the PPWG mode
+b = 1e-3; % slit height
+neff = 1; % effective refractive index between the plates
+nu_pm = 1e-12*3e8*order_m./(2*b*sqrt(neff^2-cosd(theta_pm).^2));
+hold on 
+plot(theta_pm, nu_pm,'linewidth',2,'color','red')
+axis square
+% colormap(flipud(brewermap([],'GnBu')))
+legend('Data','n=0')
+order=-1;
+c=3e8;
+period = 0.95e-3;
+% 
+%% plotting
+figure
[…]

### 2022-07-05 analysis/binary/another_analysis.py

@@ -1,0 +1,123 @@
+import sys
+import matplotlib.pyplot as plt
+import matplotlib as mpl
+import numpy as np
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML/ml_model/binary')
+sys.path.append('/Users/joshuaneronha/Documents/Brown/Research/LeakyWaveML')
+import pickle
+import tensorflow as tf
+from statsmodels.stats.weightstats import ztest
+mpl.rcParams['font.family'] = 'Arial'
+plt.rcParams['font.size'] = 12
+plt.rcParams['axes.linewidth'] = 2
+from tensorflow import losses
+
+from preprocess import import_data, import_val_data
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
+### Generating the box plots with all data...
+
+slots, peaks, _ = import_data()
+
+fig, axs = plt.subplots(1,1,tight_layout=True,figsize=(6,4))
+
+boxplot = axs.boxplot(peaks, sym = '', patch_artist = True)
+plt.xticks(np.arange(0,36,5),np.arange(0,36,5))
+plt.xlabel('Peak Count')
+plt.ylabel('Amplitude (normalized)')
+plt.ylim([-0.4,1])
+
+# plt.savefig('paper/figures/boxbinarymono.svg')
+
+### Analyzing testing data that we put back through COMSOL...
+
+with open('analysis/binary/test_data510.pkl','rb') as file:
+    test_data = pickle.load(file)
+    peaks, true, pred, waves = test_data
+
+val510_slots, val510_peaks, val510_waves = import_val_data('analysis/binary/validation510')
+
+#compute two MSEs -- one between the objective signal and the signal generated by the model generated slot, and a mse_list_control
+#(i.e. two random slots, which is why there is i+1... acts as an offset)
+
+mse_list_binary = []
+mse_list_control = []
+
+for i in np.arange(500):
[…]

### 2022-07-05 analysis/floquet.m

@@ -1,0 +1,33 @@
+clc;clear all
+freq = 200e9; %frequency 
+lambda = 3e8/freq; %wavelength
+k0 = 2*pi/lambda; % free-space wavevector
+h = 1e-3; % plate separation
+
+% assuming total length is 18 mm and pixel length of .5 mm (if you change this, change also here)
+Lambda = 1e-3:1e-3:9e-3; 
+% this goes from minimum period 10101010, which is a period of 1mm
+% to the maximum period, which is half of the slot is open 11111...0000
+p = -80:1:80; %floquet mode number, we just try a lot of floquet modes until it exists.
+
+k=1;
+for i = 1:length(Lambda) 
+    for j = 1:length(p)
+        betaz(i,j) = (sqrt(k0^2-(pi/h)^2)+2*pi*p(j)/Lambda(i)); % calculate the dispersion constant for every possible Lambda,p combination
+        neff(i,j) = betaz(i,j)/k0; % calculate the corresponding effective index
+        if neff(i,j) > -1 && neff(i,j) < 1 % The mode exists (and leaks) only when it is between 0 and 1
+            neff_works(k,:) = [neff(i,j) acosd(neff(i,j)) Lambda(i) p(j)];% This is the matrix of solution. 
+            % 1st column is the value of neff that works
+            % 2nd column is the peak angle (assuming theta=0 is parallel to the slot)
+            % corresponding Lambda 
+            % corresponding p
+            k=k+1;
+        end
+    end
+end
+size(neff_works,1) % this number is the total number of possible angles
+
+plot(neff_works(:,2),'.') % this plots the possible angles
+
+%these are the floquet peaks
+sort(unique(floor(neff_works(:,2))))

### 2022-07-05 analysis/gray_calibration/greycal.m

@@ -1,0 +1,29 @@
+clear all
+clc
+close all
+
+Files=dir('gc5');
+N = length(Files);
+
+maxes = zeros(8,1);
+
+vals = [0 50 75 100 113 125 140 165];
+
+for k = 1:length(vals)
+    
+    [t,w]=textread(strcat('gc5/',num2str(vals(k)),'.picotd'),'%f%f','headerlines',6);
+    
+    B = fftshift(fft(w));
+    fmax = 0.5/(t(2)-t(1));
+    f = linspace(-fmax,fmax,size(w,1));
+    maxes(k) = abs(B(2112))^2;
+    
+end
+
+maxes = maxes / maxes(1);
+p = polyfit(vals,maxes,5);
+cobf = polyval(p,0:165);
+scatter(vals,maxes)
+yline(0.5)
+hold on
+plot(0:165,cobf)

### 2022-07-05 archive/peak_analysis.py

@@ -1,55 +1,0 @@
-from preprocess import *
-import numpy as np
-import pandas as pd
-from scipy import signal
-import matplotlib.pyplot as plt
-
-slots, results = import_data(['1645299750', '1645318239', '1645336863', '1645355510'])
-
-def findpeaks(which):
-    peaks, props = signal.find_peaks(which, prominence = 5, width=5)
-    return peaks
-
-def plotpeaks(i):
-    peaks = findpeaks(results[i,:])
-    plt.plot(results[i,:])
-    plt.plot(peaks, results[i,:][peaks], "x")
-    print(peaks)
-
-plotpeaks(299)
-
-out_dict = {}
-for i in np.arange(2000):
-    peaks = findpeaks(results[i,:])
-    for j in peaks:
-        if j in out_dict:
-            out_dict[j] += 1
-        else:
-            out_dict[j] = 1
-
-out_dict
-
-out = np.array(list(out_dict.items()))
-
-df = pd.DataFrame(out).sort_values(1, ascending = False)
-
-df
-df[0]
-df[1]
-
-df.head(25)
-
-top_df = df.head(50)
-
-plt.scatter(df[0], df[1])
-
-
-
-results.shape
-signal.find_peaks(results)
-
-x = {42: 3, 45: 8}
-x
-
-42 in x
-x[42] += 1

### 2022-07-05 archive/peak_detection.py

@@ -1,155 +1,0 @@
-from preprocess import *
-import numpy as np
-import tensorflow as tf
-import pickle
-import matplotlib.pyplot as plt
-from scipy import signal
-import tensorflow as tf
-import tensorflow_probability as tfp
-
-with open('ten_examples.pkl','rb') as f:
-    data = pickle.load(f)
-
-data[0][0].shape
-
-sim = data[1][0]
-ml = data[1][1]
-
-plt.plot(np.arange(361),sim,ml)
-
-def findpeaks(which):
-    peaks, props = signal.find_peaks(np.array(which), prominence = 5, width=8)
-
-    print(peaks)
-
-    plt.plot(np.array(which))
-    plt.plot(peaks, np.array(which)[peaks], "x")
-
-findpeaks(sim)
-findpeaks(ml)
-tf.expand_dims(efarx[0],axis=1).shape
-
-shapes, efarx = import_data(['1645299750'])
-
-np.correlate(efarx[0],efarx[0])
-
-def findpeaks(which):
-    peaks, props = signal.find_peaks(efarx[which], prominence = 8, width=8)
-
-    plt.plot(efarx[which])
-    plt.plot(peaks, efarx[which][peaks], "x")
-
-plt.plot(signal.correlate(efarx[0], efarx[0]))
-
-findpeaks(2)
-
-
-peaks
-
-props
-
-mult = np.stack([efarx[0],efarx[0]])
-
-mult.shape
-
-efarx[0].shape
-
-corr_vec = np.vectorize(np.correlate)
-
-[efarx[0],efarx[0]]
-
-np.correlate(efarx[0],efarx[0])
-
-[compute_similarity(x[0],x[1]) for x in [[efarx[0],efarx[0]], [efarx[1],efarx[1]]]]
-
-testvec = np.vectorize(compute_similarity)
-
-
-testvec([efarx[0],efarx[0]],3)
-
-compute_similarity(efarx[0],efarx[0])
-
-np.correlate(efarx[0], efarx[0])
-
-def compute_similarity(ref_rec,input_rec,weightage=[0.33,0.33,0.33]):
-    ## Time domain similarity
-    ref_time = np.correlate(ref_rec,ref_rec)
-    inp_time = np.correlate(ref_rec,input_rec)
-    diff_time = abs(ref_time-inp_time)
-
-    ## Freq domain similarity
[…]

### 2022-07-05 archive/preprocess.py

@@ -1,39 +1,0 @@
-import numpy as np
-# import tensorflow as tf
-import pickle
-
-def import_data(timestamp_list):
-    """
-    Loads in data and transposes it into proper shapes
-    """
-
-    slots_list = []
-    results_list = []
-
-    for timestamp in timestamp_list:
-        with open('comsol_results/1d/' + timestamp + '.pkl', 'rb') as file:
-            slots = np.array(pickle.load(file))
-            # print(slots.shape)
-            slots_list.append(slots)
-
-        with open('comsol_results/1d/' + timestamp + '.csv', 'rb') as file:
-            results = np.loadtxt(file, delimiter=",", dtype=float)
-            num_sims = int(results.shape[0] / 361)
-            points = [361 * x for x in np.arange(num_sims + 1)]
-            # sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
-            sorted_x = np.array([results[i:i + 361,1] for i in points[:-1]])
-            results_list.append(sorted_x)
-
-    # print((np.expand_dims(np.concatenate(slots_list),axis=[2,3]) / 1.0).shape)
-    return np.expand_dims(np.concatenate(slots_list),axis=[2,3]) / 1.0, np.concatenate(results_list) / 1.0
-
-def get_next_batch(input_array, label_array, start_index, batch_size):
-    """
-    Accepts an array of inputs and labels along with a starting index and batch
-    size in order to separate the full array of data into batches.
-    :inputs: a NumPy array of all images with shape (n x 2)
-    :labels: a NumPy array of all labels with shape (n x 1)
-    :start_index: the first index desired in the batch
-    :batch_size: how many total images desired in the batch
-    """
-    return input_array[start_index: (start_index + batch_size), :], label_array[start_index: (start_index + batch_size)]

### 2022-07-05 experiments/a477may24_fixedplastic.m

@@ -1,171 +1,0 @@
- clear all
-clc
-close all
-
-Files=dir('binarywaveguide477-furtherplastic/');
-N = length(Files);
-[t,w]=textread(strcat('binarywaveguide477-furtherplastic/',Files(3).name),'%f%f','headerlines',6);  % read first for size
-T=zeros(length(t),N-2); W=T; f=T; B=T;   % preallocate space for time,waveform vectors
-T(:,1)=t;
-W(:,1)=w;
-
-B(:,1) = fftshift(fft(W(:,1)));
-
-t = T(:,1);
-fmax = 0.5/(t(2)-t(1));
-f(:,1) = linspace(-fmax,fmax,size(W,1));
-
-for k = 3:N
-    name = Files(k).name;
-    x = split(name,'.');
-    [T(:,str2double(x(1)) + 1),W(:,str2double(x(1)) + 1)]=textread(strcat('binarywaveguide477-furtherplastic/',name),'%f%f','headerlines',6);
-    
-    B(:,str2double(x(1)) + 1) = fftshift(fft(W(:,str2double(x(1)) + 1)));
-    t = T(:,str2double(x(1)) + 1);
-    fmax = 0.5/(t(2)-t(1));
-    f(:,str2double(x(1)) + 1) = linspace(-fmax,fmax,size(W,1));
-end
-
-% theta_pm_back = linspace(0,150,1400)
-% nu_vector=(150:0.1:280);
-% nu_backfire = -1e-12*((sqrt(2)*sqrt((8*c^2*b^2*order^2)-(c^2.*period.^2.*cosd(2*theta_pm_back))+(c^2.*period.^2))./(b.*period))-((4*c*order.*cosd(theta_pm_back))./period))./(4*((cosd(theta_pm_back).^2)-1));
-% plot(theta_pm_back(:,1:1400),nu_backfire(:,1:1400),'linewidth',1.5,'color','white')
-
-objective241 = readmatrix('objective477.csv');
-expected241 = readmatrix('expected477_base.csv');
-% grey477 = readmatrix('477grey.csv');
-% random = readmatrix('expected241.csv');
-
-% figure
-% % semilogy(7:151,abs(B(2112,1:end-7)) / max(abs(B(2112,1:end-7))))
-% hold on
-% % semilogy(objective241(1:151,2) / max(objective241(1:151,2)))
[…]

### 2022-07-05 experiments/greycal.m

@@ -1,35 +1,0 @@
-clear all
-clc
-close all
-
-Files=dir('gc5');
-N = length(Files);
-
-% blackness = zeros(8,1);
-maxes = zeros(8,1);
-
-vals = [0 50 75 100 113 125 140 165];
-
-for k = 1:length(vals)
-%     name = Files(k).name;
-%     x = split(name,'.');
-%     blackness(k-2) = str2double(x(1));
-    
-    
-    [t,w]=textread(strcat('gc5/',num2str(vals(k)),'.picotd'),'%f%f','headerlines',6);
-%     maxes(k-2) = max(w.^2);
-    
-    B = fftshift(fft(w));
-    fmax = 0.5/(t(2)-t(1));
-    f = linspace(-fmax,fmax,size(w,1));
-    maxes(k) = abs(B(2112))^2;
-    
-end
-
-maxes = maxes / maxes(1);
-p = polyfit(vals,maxes,5);
-cobf = polyval(p,0:165);
-scatter(vals,maxes)
-yline(0.5)
-hold on
-plot(0:165,cobf)

### 2022-07-05 floquet.m

@@ -1,30 +1,0 @@
-clc;clear all
-freq = 200e9; %frequency 
-lambda = 3e8/freq; %wavelength
-k0 = 2*pi/lambda; % free-space wavevector
-h = 1e-3; % plate separation
-
-% assuming total length is 18 mm and pixel length of .5 mm (if you change this, change also here)
-Lambda = 1e-3:1e-3:9e-3; 
-% this goes from minimum period 10101010, which is a period of 1mm
-% to the maximum period, which is half of the slot is open 11111...0000
-p = -80:1:80; %floquet mode number, we just try a lot of floquet modes until it exists.
-
-k=1;
-for i = 1:length(Lambda) 
-    for j = 1:length(p)
-        betaz(i,j) = (sqrt(k0^2-(pi/h)^2)+2*pi*p(j)/Lambda(i)); % calculate the dispersion constant for every possible Lambda,p combination
-        neff(i,j) = betaz(i,j)/k0; % calculate the corresponding effective index
-        if neff(i,j) > -1 && neff(i,j) < 1 % The mode exists (and leaks) only when it is between 0 and 1
-            neff_works(k,:) = [neff(i,j) acosd(neff(i,j)) Lambda(i) p(j)];% This is the matrix of solution. 
-            % 1st column is the value of neff that works
-            % 2nd column is the peak angle (assuming theta=0 is parallel to the slot)
-            % corresponding Lambda 
-            % corresponding p
-            k=k+1;
-        end
-    end
-end
-size(neff_works,1) % this number is the total number of possible angles
-
-plot(neff_works(:,2),'.') % this plots the possible angles

### 2022-07-05 ml_model/3grey/build_model.py

@@ -1,0 +1,118 @@
+import sys
+sys.path.append('/Users/joshuaneronha/.conda/envs/mittleman/bin/python')
+sys.path.append('ml_model/3grey')
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+from preprocess import import_data, get_next_batch
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+import argparse
+import pickle
+import random
+
+parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
+
+def train(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+
+    #work through all the training data
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        #get the next set of data
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        #call the model, calculate the loss function, and update the gradient
+        with tf.GradientTape() as tape:
+            efarx = model.call(peaks_batch)
+            efarx_loss = model.loss_function(efarx, slot_batch) #slots serves as the mask here
+            # print(efarx_loss)
+
+        gradients = tape.gradient(efarx_loss, model.trainable_variables)
+        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+
+    print('Efarx training loss: ', tf.reduce_mean(loss_list))
+    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+
+def test(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+    assump_acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        efarx = model.call(peaks_batch)
+        efarx_loss = model.loss_function(efarx, slot_batch)
+
+        loss_list.append(efarx_loss)
[…]

### 2022-07-05 ml_model/3grey/peaks_to_slots_model.py

@@ -1,0 +1,64 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
+import tensorflow_io as tfio
+
+
+class LWAPredictionModel(tf.keras.Model):
+    def __init__(self, lr = 1e-4):
+        super(LWAPredictionModel, self).__init__()
+
+        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
+        self.batch_size = 128
+        self.epochs = 35
+
+        self.dense_layers = tf.keras.Sequential()
+
+        self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Flatten())
+        self.dense_layers.add(Dense(3000))
+
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(3000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(36,activation='sigmoid'))
+
+    def call(self, input):
+        input = tf.expand_dims(input, 2)
+        return self.dense_layers(input)
+
+    def loss_function(self, prediction, true):
+
+        mse =  tf.keras.losses.MeanSquaredError()
+
+        return mse(true, prediction)
+
+    def accuracy(self, prediction, true):
+        #round to the nearest slot option and check accuracy
+        ba = tf.keras.metrics.BinaryAccuracy()
+
+        prediction = np.where((prediction > 0) & (prediction <= 0.333), 0, prediction)
[…]

### 2022-07-05 ml_model/3grey/preprocess.py

@@ -1,0 +1,131 @@
+import numpy as np
+import tensorflow as tf
+import pickle
+import os
+
+# list of floquet peaks, sourced from analysis/floquet.m
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
+def import_data():
+    """
+    Loads in simulation data
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+    #get list of all files
+    timestamp_list = list(set([x.split('.')[0] for x in os.listdir('simulation_model/3grey/3greydata/')]))
+
+    for timestamp in timestamp_list:
+
+        if timestamp == '1655498155':
+            #this simulation didn't finish, so skipping it
+            continue
+
+        with open('simulation_model/3grey/3greydata/' + timestamp + '.csv', 'rb') as file:
+            #load in far-field data
+            #pull out only the floquet peaks and reshape
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet]
+
+            #normalize, since power should be constant given same number of slots
+
+            normalized = (peaks.T / peaks.max(axis=1)).T
+            peaks_list.append(normalized)
+
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
+
+        with open('simulation_model/3grey/3greydata/' + timestamp + '.pkl', 'rb') as file:
+            #also load in the slot shapes
+            slots = np.array(pickle.load(file))
+            slots_list.append(slots)
+
+    return np.concatenate(slots_list), np.concatenate(peaks_list), np.concatenate(wave_list)
+
+
+def import_val_data(path):
+    """
+    Basically the same thing as import_data, except it reads in the validation
+    data from the generated slots we put back into Comsol... accepts the path
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+    with open(path + '.csv', 'rb') as file:
[…]

### 2022-07-05 ml_model/binary/build_model.py

@@ -1,0 +1,111 @@
+import numpy as np
+import tensorflow as tf
+from peaks_to_slots_model import LWAPredictionModel
+from preprocess import import_data, get_next_batch
+from sklearn.model_selection import train_test_split
+import matplotlib.pyplot as plt
+import argparse
+import pickle
+import random
+
+parser = argparse.ArgumentParser(description='Build a deep learning model based on COMSOL simulations.')
+
+def train(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+
+    #work through all the training data
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        #get the next set of data
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        #call the model, calculate the loss function, and update the gradient
+        with tf.GradientTape() as tape:
+            efarx = model.call(peaks_batch)
+            efarx_loss = model.loss_function(efarx, slot_batch)
+
+        gradients = tape.gradient(efarx_loss, model.trainable_variables)
+        model.adam_optimizer.apply_gradients(zip(gradients, model.trainable_variables))
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+
+    print('Efarx training loss: ', tf.reduce_mean(loss_list))
+    print('Efarx training accuracy:', tf.reduce_mean(acc_list))
+
+def test(model, slots, peaks):
+    completed = 0
+
+    loss_list = []
+    acc_list = []
+    assump_acc_list = []
+
+    while completed < len(slots):
+
+        our_size = model.batch_size
+
+        if len(slots) - completed < model.batch_size:
+            our_size = len(slots) - completed
+
+        slot_batch, peaks_batch = get_next_batch(slots, peaks, completed, our_size)
+
+        completed += our_size
+
+        efarx = model.call(peaks_batch)
+        efarx_loss = model.loss_function(efarx, slot_batch)
+
+        loss_list.append(efarx_loss)
+        acc_list.append(model.accuracy(efarx, slot_batch))
+        assump_acc_list.append(model.assump_accuracy(efarx,slot_batch))
+
+
+    print('Efarx testing accuracy:', tf.reduce_mean(acc_list))
[…]

### 2022-07-05 ml_model/binary/peaks_to_slots_model.py

@@ -1,0 +1,75 @@
+import numpy as np
+import tensorflow as tf
+import tensorflow_probability as tfp
+from tensorflow.keras.layers import Dense, Dropout, BatchNormalization, ReLU, Flatten, LeakyReLU, Conv1D
+import tensorflow_io as tfio
+
+
+class LWAPredictionModel(tf.keras.Model):
+    def __init__(self, lr = 5e-5):
+        super(LWAPredictionModel, self).__init__()
+
+        self.adam_optimizer = tf.keras.optimizers.Adam(learning_rate=lr)
+        self.batch_size = 64
+        self.epochs = 20
+
+        self.dense_layers = tf.keras.Sequential()
+
+        self.dense_layers.add(Conv1D(128,5))
+        self.dense_layers.add(Flatten())
+        self.dense_layers.add(Dense(2000))
+
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(2000))
+        self.dense_layers.add(LeakyReLU(0.1))
+        self.dense_layers.add(Dropout(0.1))
+
+        self.dense_layers.add(Dense(36,activation='sigmoid'))
+
+    def call(self, input):
+        input = tf.expand_dims(input, 2)
+        return self.dense_layers(input)
+
+    def loss_function(self, prediction, true):
+
+        bce = tf.keras.losses.BinaryCrossentropy()
+
+        return bce(true, prediction)
+
+    def assump_accuracy(self, prediction, true):
+        #accuracy assuming we take the top 16 slots, not just probabilites over 0.5
+        ba = tf.keras.metrics.BinaryAccuracy()
+        total_slots = 36 - tf.reduce_sum(true,axis=1)
+
[…]

### 2022-07-05 ml_model/binary/preprocess.py

@@ -1,0 +1,95 @@
+import numpy as np
+import tensorflow as tf
+import pickle
+import os
+
+# list of floquet peaks, sourced from analysis/floquet.m
+
+floquet = list(np.array([  6.,  16.,  24.,  29.,  32.,  34.,  49.,  60.,  62.,  63.,  66.,
+        69.,  71.,  73.,  77.,  81.,  84.,  86.,  89.,  90.,  95., 100.,
+       101., 104., 106., 110., 114., 118., 120., 123., 126., 129., 131.,
+       132., 147.]).astype('int'))
+
+def import_data():
+    """
+    Loads in simulation data
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+    #get list of all files
+    timestamp_list = list(set([x.split('.')[0] for x in os.listdir('simulation_model/binary_model/1dconstantslots/')]))
+
+    for timestamp in timestamp_list:
+
+        with open('simulation_model/binary_model/1dconstantslots/' + timestamp + '.csv', 'rb') as file:
+            #load in far-field data
+            #pull out only the floquet peaks and reshape
+
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
+            points = [361 * x for x in np.arange(num_sims + 1)]
+            sorted_x = np.array([20*np.log10(results[i:i + 361,1]) for i in points[:-1]])
+            peaks = sorted_x[:,floquet]
+
+            #normalize, since power should be constant given same number of slots
+
+            normalized = (peaks.T / peaks.max(axis=1)).T
+            peaks_list.append(normalized)
+
+            wave_list.append((sorted_x.T / sorted_x.max(axis=1)).T)
+
+        with open('simulation_model/binary_model/1dconstantslots/' + timestamp + '.pkl', 'rb') as file:
+            slots = np.array(pickle.load(file))
+            slots_list.append(slots)
+
+    return np.concatenate(slots_list), np.concatenate(peaks_list), np.concatenate(wave_list)
+
+
+def import_val_data(path):
+    """
+    Basically the same thing as import_data, except it reads in the validation
+    data from the generated slots we put back into Comsol... accepts the path
+    """
+
+    slots_list = []
+    peaks_list = []
+    max_list = []
+    wave_list = []
+
+    with open(path + '.csv', 'rb') as file:
+            results = np.loadtxt(file, delimiter=",", dtype=float)
+            num_sims = int(results.shape[0] / 361)
[…]

### 2022-07-05 statstesting.py

@@ -1,11 +1,0 @@
-from statsmodels.stats.weightstats import ztest as ztest
-
-#enter IQ levels for 20 individuals from each city
-cityA = [82, 84, 85, 89, 91, 91, 92, 94, 99, 99,
-         105, 109, 109, 109, 110, 112, 112, 113, 114, 114]
-
-cityB = [90, 91, 91, 91, 95, 95, 99, 99, 108, 109,
-         109, 114, 115, 116, 117, 117, 128, 129, 130, 133]
-
-#perform two sample z-test
-ztest(cityA, cityB, value=0) 

### 2022-07-05 testing.py

@@ -1,1 +1,0 @@
-np.array([0.21,0.11,0.4])
